---
title: "transformations"
author: "Ellie White"
date: "March 23, 2019"
output: html_document
---

Record of how a model's predictive capapility is different given different data transformation techniques.  

# Contents   
1.0 Data Gathering  
2.0 Data Transformations  
3.0 Function
4.0 Modelling and Resampling  
5.0 LOGO Post Processing  
  5.1 Aggregate Basins
  5.2 Incremental Basins  
  5.3 Cumulative Basins 
6.0 Test and Analyze
7.0 Visual Fit  
8.0 Goodness of Fit  
9.0 Variable Importance Plots  
10.0 Partial Dependence Plots  
11.0 Variable Interactions

```{r, include=FALSE}
library(knitr)
library(formatR)
opts_chunk$set(fig.width = 7.5, fig.height = 7.5, collapse = TRUE, tidy = FALSE)
```

# Citations
```{r citations} 
# cite R 
toBibtex(citation())

# cite R studio
RStudio.Version()

# cite packages
citethese <- c("raster", "sp", "rgdal", "rgeos", "dismo", "geojsonio", "hydroGOF", "RColorBrewer", "fBasics", "lmtest", "reshape2", "statmod")
for(c in seq_along(citethese)){
  print(toBibtex(citation(citethese[c])))
}
remove(c)

# session info in case anything goes wrong
sessionInfo()
```

# Set Seed
```{r setseed}
set.seed(3232019)
```

# 1.0 Data Gathering
```{r data_gathering}
df <- readRDS('inputdata/moddf.rds')
dfc <- readRDS('inputdata/moddfc.rds')

# remove DOMGEOLOGY cause it's causing problems
df <- df[ , !(colnames(df) %in% c("DOMGEOLOGY"))]
dfc <- dfc[ , !(colnames(dfc) %in% c("DOMGEOLOGY"))]

# order by baisn name
df <- df[order(df$CDEC_ID), ]
row.names(df) <- 1:nrow(df)
dfc <- dfc[order(dfc$CDEC_ID), ]
row.names(dfc) <- 1:nrow(dfc)

# check this
dim(df) == dim(dfc)

# get rid of negative flows
# 1st of all WHY THE FUCK ARE THERE NEGATIVE FLOWS IN THE DATA? inverstigate this later.
# 2nd make sure the dates that have negative flows in the original dataset is removed from the cumulative dataset too. Afterall, these cumulative values are calculated from the original dataset and negative flow don't make sense there, so their cumulative doesn't make sense in this dataset either. 
moddf <- df[df$FLOW>=0 & dfc$FLOW>=0, ]
moddfc <- dfc[df$FLOW>=0 & dfc$FLOW>=0 , ]

# check if all the negatives are gone from moddf and moddfc
tbd <- moddf[moddf$FLOW<0, "FLOW"]
tbd <- na.omit(tbd)
length(tbd) == 0

tbd <- moddfc[moddfc$FLOW<0, "FLOW"]
tbd <- na.omit(tbd)
length(tbd) == 0

remove(tbd)

# check this
dim(moddf) == dim(moddfc)
```

```{r data_gathering_extra}
# some helpful dataframes, may come in handy later for post processing
basins_points <- read.csv("inputdata/cdec_fnf_stations_data_minus_sfj_otr_bhn_ftm_sfr_sjm_klo.csv", stringsAsFactors = FALSE)
coordinates(basins_points) <- ~LONGITUDE+LATITUDE
proj4string(basins_points) <- CRS("+proj=longlat +datum=WGS84")

basins <- readRDS("inputdata/basins.rds")
cacounties <- readRDS("inputdata/counties.rds")

ta <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +datum=NAD83 +units=km +ellps=GRS80")
basins_points <- spTransform(basins_points, ta)
basins <- spTransform(basins, ta)
cacounties <- spTransform(cacounties, ta)
  
# wide format data
cdec_fnf_wide <- read.csv('inputdata/cdec_fnf_wide.csv')
cdec_fnf_wide$DATE <- as.Date(cdec_fnf_wide$DATE, format="%Y-%m-%d")
cdec_fnf_wide <- cdec_fnf_wide[order(cdec_fnf_wide$DATE),]

# The full records span 1900-01-01 to 1980-09-01, but most records start at 1982
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>="1982-01-01", ]
```

```{r visuals} 
# colourblind palettes
# ordered:     black      pink        orange     yellow     green       blue      darkorange  lightblue
cbpgrey <-  c("#999999", "#CC79A7",  "#E69F00", "#F0E442", "#009E73", "#0072B2", "#D55E00", "#56B4E9")
cbpblack <- c("#000000", "#CC79A7",  "#E69F00", "#F0E442", "#009E73", "#0072B2", "#D55E00", "#56B4E9")
```

# 2.0 Data Tranformations
```{r data_transformation_lm} 
# for LM
# split into two one original aggregate basins and one the incremental basins
df_lm_agg <- moddf[1:(which(moddf$CDEC_ID=="AMA_INC")[1]-1),]
df_lm_inc <- moddf[which(moddf$CDEC_ID=="AMA_INC")[1]:nrow(moddf),]
df_lm_cagg <- moddfc[1:(which(moddfc$CDEC_ID=="AMA_INC")[1]-1),]
df_lm_cinc <- moddfc[which(moddfc$CDEC_ID=="AMA_INC")[1]:nrow(moddfc),]

# get rid of na values 
df_lm_agg <- na.omit(df_lm_agg)
df_lm_inc <- na.omit(df_lm_inc)
df_lm_cagg <- na.omit(df_lm_cagg)
df_lm_cinc <- na.omit(df_lm_cinc)
```

```{r data_transformations_glm} 
# for GLM
# make another data frame without the 0s, because a gamma distributions in glms can't handle zeros
# We are going to add a small amount to the 0s, in essence it is the same in value but now the glm trasformations work
df[which(df$FLOW==0), "FLOW"] <- 1
dfc[which(dfc$FLOW==0), "FLOW"] <- 1

moddf <- df[df$FLOW>0 & dfc$FLOW>0, ]
moddfc <- dfc[df$FLOW>0 & dfc$FLOW>0, ]

# check if all the negatives are gone from moddf and moddfc
tbd <- moddf[moddf$FLOW<=0, "FLOW"]
tbd <- na.omit(tbd)
length(tbd) == 0

tbd <- moddfc[moddfc$FLOW<=0, "FLOW"]
tbd <- na.omit(tbd)
length(tbd) == 0

# no longer needed
remove(tbd)
remove(df)
remove(dfc)

df_glm_agg <- moddf[1:(which(moddf$CDEC_ID=="AMA_INC")[1]-1),]
df_glm_inc <- moddf[which(moddf$CDEC_ID=="AMA_INC")[1]:nrow(moddf),]
df_glm_cagg <- moddfc[1:(which(moddfc$CDEC_ID=="AMA_INC")[1]-1),]
df_glm_cinc <- moddfc[which(moddfc$CDEC_ID=="AMA_INC")[1]:nrow(moddfc),]

df_glm_agg <- na.omit(df_glm_agg)
df_glm_inc <- na.omit(df_glm_inc)
df_glm_cagg <- na.omit(df_glm_cagg)
df_glm_cinc <- na.omit(df_glm_cinc)

# no longer needed
remove(moddf)
remove(moddfc)
```

# 3.0 Functions
```{r funcstoimport} 
# library(hydroGOF) # this is giving wrong functions, do not load it in make sure the search path is clear
goffuncs <- list.files("libraries/HydroGOFm/R")
for(i in 1:length(goffuncs)){
  source(paste0("libraries/HydroGOFm/R/", goffuncs[i]))
}
remove(goffuncs)

search()
```

# 4.0 Modelling and Resampling
```{r lm_modelling_and_cv} 
# group can be resub, 2L, 5L, 10L, logo, lmgo, lho. Notice how a plain 2, 5, and 10 will not work, you have to declare it an integer
# datatype can be "agg" or "inc"

library(dismo)
lmcv <- function(data, groupingstyle, datatype){
  # for resubstitution, where testing data and training data is the same
  if(groupingstyle=="resub"){
    linearmodel <- lm(FLOW~., data=data[,c(15,18:ncol(data))])
    predictions <- predict(linearmodel, data, type='response')
    results <- cbind(obs=data$FLOW, pred=predictions)
    modgof <- gof(as.data.frame(results)$pred, as.data.frame(results)$obs)
  }
  
  # for k-fold cross validation
  if(is.integer(groupingstyle)){
    group <- kfold(data, groupingstyle)
    linearmodel <- results <- modgof <- list()
    for (k in 1:groupingstyle) {
      trainset <- data[group != k, ]
      testset <- data[group == k, ]
      linearmodel[[k]] <- lm(FLOW~., data=trainset[,c(15,18:ncol(trainset))])
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  # for leave one group (basin) out cross validation
  if(groupingstyle=="logo"){
    linearmodel <- results <- modgof <- list()
    for (k in 1:(length(unique(data$CDEC_ID)))){
      h <- unique(data$CDEC_ID)[k]
      testset <- data[data$CDEC_ID==h,]
      trainset <- data[data$CDEC_ID!=h,]
      linearmodel[[k]] <- lm(FLOW~., data=trainset[,c(15,18:ncol(trainset))])
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
    colnames(modgof) <- unique(data$CDEC_ID)
  }
  
  # for random 5-fold leave multiple groups out cross validation, meaning a random 1/5 of the basins will be left out of training
  if(groupingstyle=="lmgo"){
    nfolds <- 5
    group <- as.data.frame(unique(data$CDEC_ID))
    colnames(group) <- "CDEC_ID"
    group$kftrain <- kfold(nrow(group), nfolds)
    data <- merge(data, group, by="CDEC_ID")
    
    linearmodel <- results <- modgof <- list()
    for (k in 1:nfolds) {
      testset <- data[data$kftrain == k, ]
      trainset <- data[data$kftrain != k, ]
      linearmodel[[k]] <- lm(FLOW~., data=trainset[,c(15,18:ncol(trainset))])
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  # # for leave hierarchies out cross validation
  # if(groupingstyle=="lho"){
  # }
  
  if(groupingstyle=="resub"){
    list(mod=linearmodel, results=results, gof=modgof)
    }
  else if(groupingstyle=="logo"){
    list(mod=linearmodel, results=results, gof=modgof)
    }
  else{
    list(mod=linearmodel, results=results, gof=modgof, kf=group)
    }
}

# lm_agg_resub_results <- lmcv(df_lm_agg, "resub", "agg")
# lm_agg_2fold_results <- lmcv(df_lm_agg, 2L, "agg")
# lm_agg_5fold_results <- lmcv(df_lm_agg, 5L, "agg")
# lm_agg_10fold_results <- lmcv(df_lm_agg, 10L, "agg")
# lm_agg_logo_results <- lmcv(df_lm_agg, "logo", "agg")
# lm_agg_lmgo_results <- lmcv(df_lm_agg, "lmgo", "agg")
# 
# lm_inc_resub_results <- lmcv(df_lm_inc, "resub", "inc")
# lm_inc_2fold_results <- lmcv(df_lm_inc, 2L, "inc")
# lm_inc_5fold_results <- lmcv(df_lm_inc, 5L, "inc")
# lm_inc_10fold_results <- lmcv(df_lm_inc, 10L, "inc")
# # not working with DOMGEOLOGY in it
# lm_inc_logo_results <- lmcv(df_lm_inc, "logo", "inc")
# lm_inc_lmgo_results <- lmcv(df_lm_inc, "lmgo", "inc") # no need to do this
# 
# lm_cagg_resub_results <- lmcv(df_lm_cagg, "resub", "agg")
# lm_cagg_2fold_results <- lmcv(df_lm_cagg, 2L, "agg")
# lm_cagg_5fold_results <- lmcv(df_lm_cagg, 5L, "agg")
# lm_cagg_10fold_results <- lmcv(df_lm_cagg, 10L, "agg")
# lm_cagg_logo_results <- lmcv(df_lm_cagg, "logo", "agg")
# lm_cagg_lmgo_results <- lmcv(df_lm_cagg, "lmgo", "agg")
# 
# lm_cinc_resub_results <- lmcv(df_lm_cinc, "resub", "inc")
# lm_cinc_2fold_results <- lmcv(df_lm_cinc, 2L, "inc")
# lm_cinc_5fold_results <- lmcv(df_lm_cinc, 5L, "inc")
# lm_cinc_10fold_results <- lmcv(df_lm_cinc, 10L, "inc")
# # not working with DOMGEOLOGY in it
# lm_cinc_logo_results <- lmcv(df_lm_cinc, "logo", "inc")
# lm_cinc_lmgo_results <- lmcv(df_lm_inc, "lmgo", "inc") # no need to do this
# 
# saveRDS(lm_agg_logo_results, file="ch2 data transformations/outputdata/rds/lm_agg_logo_results.RDS")
# saveRDS(lm_inc_logo_results, file="ch2 data transformations/outputdata/rds/lm_inc_logo_results.RDS")
# saveRDS(lm_cagg_logo_results, file="ch2 data transformations/outputdata/rds/lm_cagg_logo_results.RDS")
# saveRDS(lm_cinc_logo_results, file="ch2 data transformations/outputdata/rds/lm_cinc_logo_results.RDS")

lm_agg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/lm_agg_logo_results.RDS")
lm_inc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/lm_inc_logo_results.RDS")
lm_cagg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/lm_cagg_logo_results.RDS")
lm_cinc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/lm_cinc_logo_results.RDS")
```

```{r glm_modelling_and_cv} 
glmcv <- function(data, groupingstyle, datatype, ...){ 
  # for resubstitution, where testing data and training data is the same
  if(groupingstyle=="resub"){
    linearmodel <- glm(FLOW~. , data=data[,c(15,18:ncol(data))], maxit=100, ...)
    predictions <- predict(linearmodel, data, type='response')
    results <- cbind(obs=data$FLOW, pred=predictions)
    modgof <- gof(as.data.frame(results)$pred, as.data.frame(results)$obs)
  }
  
  # for k-fold cross validation
  if(is.integer(groupingstyle)){
    group <- kfold(data, groupingstyle)
    linearmodel <- results <- modgof <- list()
    for (k in 1:groupingstyle) {
      trainset <- data[group != k, ]
      testset <- data[group == k, ]
      linearmodel[[k]] <- glm(FLOW~. , data=trainset[,c(15,18:ncol(trainset))], maxit=100, ...)
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  # for leave one group (basin) out cross validation
  if(groupingstyle=="logo"){
    linearmodel <- results <- modgof <- list()
    for (k in 1:(length(unique(data$CDEC_ID)))){
      h <- unique(data$CDEC_ID)[k]
      testset <- data[data$CDEC_ID==h,]
      trainset <- data[data$CDEC_ID!=h,]
      linearmodel[[k]] <- glm(FLOW~. , data=trainset[,c(15,18:ncol(trainset))], ...)
      predictions <- predict(linearmodel[[k]], testset, type='response') # should this be "link" or "response"?
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
    colnames(modgof) <- unique(data$CDEC_ID)
  }
  
  # for random 5-fold leave multiple groups out cross validation, meaning a random 1/5 of the basins will be left out of training
  if(groupingstyle=="lmgo"){
    nfolds <- 5
    group <- as.data.frame(unique(data$CDEC_ID))
    colnames(group) <- "CDEC_ID"
    group$kftrain <- kfold(nrow(group), nfolds)
    data <- merge(data, group, by="CDEC_ID")
    
    linearmodel <- results <- modgof <- list()
    for (k in 1:nfolds) {
      testset <- data[data$kftrain == k, ]
      trainset <- data[data$kftrain != k, ]
      linearmodel[[k]] <- glm(FLOW~. , data=trainset[,c(15,18:ncol(trainset))], maxit=100, ...)
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  # # for leave hierarchies out cross validation
  # if(groupingstyle=="lho"){
  # }
  
  if(groupingstyle=="resub"){
    list(mod=linearmodel, results=results, gof=modgof)
    }
  else if(groupingstyle=="logo"){
    list(mod=linearmodel, results=results, gof=modgof)
    }
  else{
    list(mod=linearmodel, results=results, gof=modgof, kf=group)
    }
}

# gamma 
# glmgammalog_agg_logo_results <- glmcv(df_glm_agg, "logo", "agg", family=Gamma(link="log"), maxit=1000)
# glmgammalog_inc_logo_results <- glmcv(df_glm_inc, "logo", "inc", family=Gamma(link="log"), maxit=1000)
# glmgammalog_cagg_logo_results <- glmcv(df_glm_cagg, "logo", "cagg", family=Gamma(link="log"), maxit=1000)
# glmgammalog_cinc_logo_results <- glmcv(df_glm_cinc, "logo", "cinc", family=Gamma(link="log"), maxit=1000)
# saveRDS(glmgammalog_agg_logo_results, file="ch2 data transformations/outputdata/rds/glmgammalog_agg_logo_results.RDS")
# saveRDS(glmgammalog_inc_logo_results, file="ch2 data transformations/outputdata/rds/glmgammalog_inc_logo_results.RDS")
# saveRDS(glmgammalog_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glmgammalog_cagg_logo_results.RDS")
# saveRDS(glmgammalog_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glmgammalog_cinc_logo_results.RDS")

# glmgammainv_agg_logo_results <- glmcv(df_glm_agg, "logo", "agg", family=Gamma(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# glmgammainv_inc_logo_results <- glmcv(df_glm_inc, "logo", "inc", family=Gamma(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# glmgammainv_cagg_logo_results <- glmcv(df_glm_cagg, "logo", "cagg", family=Gamma(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# glmgammainv_cinc_logo_results <- glmcv(df_glm_cinc, "logo", "cinc", family=Gamma(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# saveRDS(glmgammainv_agg_logo_results, file="ch2 data transformations/outputdata/rds/glmgammainv_agg_logo_results.RDS")
# saveRDS(glmgammainv_inc_logo_results, file="ch2 data transformations/outputdata/rds/glmgammainv_inc_logo_results.RDS")
# saveRDS(glmgammainv_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glmgammainv_cagg_logo_results.RDS")
# saveRDS(glmgammainv_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glmgammainv_cinc_logo_results.RDS")

# glmgammai_agg_logo_results <- glmcv(df_glm_agg, "logo", "agg", family=Gamma(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# glmgammai_inc_logo_results <- glmcv(df_glm_inc, "logo", "inc", family=Gamma(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# glmgammai_cagg_logo_results <- glmcv(df_glm_cagg, "logo", "cagg", family=Gamma(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# glmgammai_cinc_logo_results <- glmcv(df_glm_cinc, "logo", "cinc", family=Gamma(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# saveRDS(glmgammai_agg_logo_results, file="ch2 data transformations/outputdata/rds/glmgammai_agg_logo_results.RDS")
# saveRDS(glmgammai_inc_logo_results, file="ch2 data transformations/outputdata/rds/glmgammai_inc_logo_results.RDS")
# saveRDS(glmgammai_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glmgammai_cagg_logo_results.RDS")
# saveRDS(glmgammai_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glmgammai_cinc_logo_results.RDS")

# inverse gaussian
# glminvnormsq_agg_logo_results <- glmcv(df_glm_agg, "logo", "agg", family=inverse.gaussian(link="1/mu^2"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormsq_inc_logo_results <- glmcv(df_glm_inc, "logo", "inc", family=inverse.gaussian(link="1/mu^2"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormsq_cagg_logo_results <- glmcv(df_glm_cagg, "logo", "cagg", family=inverse.gaussian(link="1/mu^2"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormsq_cinc_logo_results <- glmcv(df_glm_cinc, "logo", "cinc", family=inverse.gaussian(link="1/mu^2"), maxit=1000, start=c(0, rep(1, 25)))
# saveRDS(glminvnormsq_agg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormsq_agg_logo_results.RDS")
# saveRDS(glminvnormsq_inc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormsq_inc_logo_results.RDS")
# saveRDS(glminvnormsq_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormsq_cagg_logo_results.RDS")
# saveRDS(glminvnormsq_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormsq_cinc_logo_results.RDS")

# glminvnorminv_agg_logo_results <- glmcv(df_glm_agg, "logo", "agg", family=inverse.gaussian(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnorminv_inc_logo_results <- glmcv(df_glm_inc, "logo", "inc", family=inverse.gaussian(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnorminv_cagg_logo_results <- glmcv(df_glm_cagg, "logo", "cagg", family=inverse.gaussian(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnorminv_cinc_logo_results <- glmcv(df_glm_cinc, "logo", "cinc", family=inverse.gaussian(link="inverse"), maxit=1000, start=c(0, rep(1, 25)))
# saveRDS(glminvnorminv_agg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnorminv_agg_logo_results.RDS")
# saveRDS(glminvnorminv_inc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnorminv_inc_logo_results.RDS")
# saveRDS(glminvnorminv_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnorminv_cagg_logo_results.RDS")
# saveRDS(glminvnorminv_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnorminv_cinc_logo_results.RDS")

# glminvnormlog_agg_logo_results <- glmcv(df_glm_agg, "logo", "agg", family=inverse.gaussian(link="log"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormlog_inc_logo_results <- glmcv(df_glm_inc, "logo", "inc", family=inverse.gaussian(link="log"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormlog_cagg_logo_results <- glmcv(df_glm_cagg, "logo", "cagg", family=inverse.gaussian(link="log"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormlog_cinc_logo_results <- glmcv(df_glm_cinc, "logo", "cinc", family=inverse.gaussian(link="log"), maxit=1000, start=c(0, rep(1, 25)))
# saveRDS(glminvnormlog_agg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormlog_agg_logo_results.RDS")
# saveRDS(glminvnormlog_inc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormlog_inc_logo_results.RDS")
# saveRDS(glminvnormlog_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormlog_cagg_logo_results.RDS")
# saveRDS(glminvnormlog_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormlog_cinc_logo_results.RDS")

# glminvnormi_agg_logo_results <- glmcv(df_glm_agg, "logo", "agg", family=inverse.gaussian(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormi_inc_logo_results <- glmcv(df_glm_inc, "logo", "inc", family=inverse.gaussian(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormi_cagg_logo_results <- glmcv(df_glm_cagg, "logo", "cagg", family=inverse.gaussian(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# glminvnormi_cinc_logo_results <- glmcv(df_glm_cinc, "logo", "cinc", family=inverse.gaussian(link="identity"), maxit=1000, start=c(0, rep(1, 25)))
# saveRDS(glminvnormi_agg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormi_agg_logo_results.RDS")
# saveRDS(glminvnormi_inc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormi_inc_logo_results.RDS")
# saveRDS(glminvnormi_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormi_cagg_logo_results.RDS")
# saveRDS(glminvnormi_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glminvnormi_cinc_logo_results.RDS")

# Tweedie, this distribution can handle 0s. So use the lm dataset here
# var.power=0 is the Gaussian family, 1 is Poisson, 2 is Gamma, 3 is inverse Gaussian. Any value except (0,1) is acceptable since it is the power alpha on the exponential: var(y)=mu^alpha*phi. The link is specified in terms of Box-Cox transformation powers, so link.power=1 is the identity link and link.power=0 means log.

library(statmod)
# glmtwd_agg_logo_results <- glmcv(df_lm_agg, "logo", "agg", family=tweedie(var.power=1.1, link.power=0), maxit=1000)
# glmtwd_inc_logo_results <- glmcv(df_lm_inc, "logo", "inc", family=tweedie(var.power=1.1, link.power=0), maxit=1000)
# glmtwd_cagg_logo_results <- glmcv(df_lm_cagg, "logo", "cagg", family=tweedie(var.power=1.1, link.power=0), maxit=1000)
# glmtwd_cinc_logo_results <- glmcv(df_lm_cinc, "logo", "cinc", family=tweedie(var.power=1.1, link.power=0), maxit=1000)
# saveRDS(glmtwd_agg_logo_results, file="ch2 data transformations/outputdata/rds/glmtwd_agg_logo_results.RDS")
# saveRDS(glmtwd_inc_logo_results, file="ch2 data transformations/outputdata/rds/glmtwd_inc_logo_results.RDS")
# saveRDS(glmtwd_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glmtwd_cagg_logo_results.RDS")
# saveRDS(glmtwd_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glmtwd_cinc_logo_results.RDS")

# mean(unlist(glmtwd_cagg_logo_results[["gof"]]["bR2", ]))

glmlognormalcv <- function(data, groupingstyle, datatype){    
  # for resubstitution, where testing data and training data is the same
  if(groupingstyle=="resub"){
    linearmodel <- glm(log(FLOW)~. , family=gaussian(link="identity"), data=data[,c(15,18:ncol(data))], maxit=100)
    predictions <- predict(linearmodel, data, type='response')
    results <- cbind(obs=data$FLOW, pred=exp(predictions))
    modgof <- gof(as.data.frame(results)$pred, as.data.frame(results)$obs)
  }
  
  # for k-fold cross validation
  if(is.integer(groupingstyle)){
    group <- kfold(data, groupingstyle)
    linearmodel <- results <- modgof <- list()
    for (k in 1:groupingstyle) {
      trainset <- data[group != k, ]
      testset <- data[group == k, ]
      linearmodel[[k]] <- glm(log(FLOW)~. , family=gaussian(link="identity"), data=trainset[,c(15,18:ncol(trainset))], maxit=100)
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=exp(predictions))
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  # for leave one group (basin) out cross validation
  if(groupingstyle=="logo"){
    linearmodel <- results <- modgof <- list()
    for (k in 1:(length(unique(data$CDEC_ID)))){
      h <- unique(data$CDEC_ID)[k]
      testset <- data[data$CDEC_ID==h,]
      trainset <- data[data$CDEC_ID!=h,]
      linearmodel[[k]] <- glm(log(FLOW)~. , family=gaussian(link="identity"), data=trainset[,c(15,18:ncol(trainset))], maxit=1000)
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=exp(predictions))
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
    colnames(modgof) <- unique(data$CDEC_ID)
  }
  
  # for random 5-fold leave multiple groups out cross validation, meaning a random 1/5 of the basins will be left out of training
  if(groupingstyle=="lmgo"){
    nfolds <- 5
    group <- as.data.frame(unique(data$CDEC_ID))
    colnames(group) <- "CDEC_ID"
    group$kftrain <- kfold(nrow(group), nfolds)
    data <- merge(data, group, by="CDEC_ID")
    
    linearmodel <- results <- modgof <- list()
    for (k in 1:nfolds) {
      testset <- data[data$kftrain == k, ]
      trainset <- data[data$kftrain != k, ]
      linearmodel[[k]] <- glm(log(FLOW)~. , family=gaussian(link="identity"), data=trainset[,c(15,18:ncol(trainset))], maxit=100)
      predictions <- predict(linearmodel[[k]], testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=exp(predictions))
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  # # for leave hierarchies out cross validation
  # if(groupingstyle=="lho"){
  # }
  
  if(groupingstyle=="resub"){
    list(mod=linearmodel, results=results, gof=modgof)
    }
  else if(groupingstyle=="logo"){
    list(mod=linearmodel, results=results, gof=modgof)
    }
  else{
    list(mod=linearmodel, results=results, gof=modgof, kf=group)
    }
}

# glmlognormal_agg_logo_results <- glmgammacv(df_glm_agg, "logo", "agg")
# glmlognormal_inc_logo_results <- glmgammacv(df_glm_inc, "logo", "inc")
# glmlognormal_cagg_logo_results <- glmgammacv(df_glm_cagg, "logo", "agg")
# glmlognormal_cinc_logo_results <- glmgammacv(df_glm_cinc, "logo", "inc")
# saveRDS(glmlognormal_agg_logo_results, file="ch2 data transformations/outputdata/rds/glmlognormal_agg_logo_results.RDS")
# saveRDS(glmlognormal_inc_logo_results, file="ch2 data transformations/outputdata/rds/glmlognormal_inc_logo_results.RDS")
# saveRDS(glmlognormal_cagg_logo_results, file="ch2 data transformations/outputdata/rds/glmlognormal_cagg_logo_results.RDS")
# saveRDS(glmlognormal_cinc_logo_results, file="ch2 data transformations/outputdata/rds/glmlognormal_cinc_logo_results.RDS")

# pick which glm you're going to go with, I think the tweedie is doing mighty fine!!!
glm_agg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/glmtwd_agg_logo_results.RDS")
glm_inc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/glmtwd_inc_logo_results.RDS")
glm_cagg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/glmtwd_cagg_logo_results.RDS")
glm_cinc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/glmtwd_cinc_logo_results.RDS")
```

```{r rf_modelling_and_cv} 
# we are not saving the models because it takes too much memory. so rrfmodel is no longer specified as a list and took mod=rfmodel out of return list. 

library(randomForest)

# # let's first optimize the tuning parameter mtry
# trf <- tuneRF(df_lm_inc[,c(15,18:ncol(df_lm_inc))], df_lm_inc$FLOW, mtryStart=5, stepFactor=2)
# mt <- trf[which.min(trf[,2]), 1]
mt <- 20

rfcv <- function(data, groupingstyle, datatype){
  # for resubstitution, where testing data and training data is the same
  if(groupingstyle=="resub"){
    rfmodel <- randomForest(FLOW~. , data=data[,c(15,18:ncol(data))], mtry=mt)
    predictions <- predict(rfmodel, data, type='response')
    results <- cbind(obs=data$FLOW, pred=predictions)
    modgof <- gof(as.data.frame(results)$pred, as.data.frame(results)$obs)
  }
  
  # for k-fold cross validation
  if(is.integer(groupingstyle)){
    group <- kfold(data, groupingstyle)
    results <- modgof <- list()
    for (k in 1:groupingstyle) {
      trainset <- data[group != k, ]
      testset <- data[group == k, ]
      rfmodel <- randomForest(FLOW~. , data=trainset[,c(15,18:ncol(trainset))], mtry=mt)
      predictions <- predict(rfmodel, testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  # for leave one group (basin) out cross validation
  if(groupingstyle=="logo"){
    results <- modgof <- list()
    for (k in 1:(length(unique(data$CDEC_ID)))){
      h <- unique(data$CDEC_ID)[k]
      testset <- data[data$CDEC_ID==h,]
      trainset <- data[data$CDEC_ID!=h,]
      rfmodel <- randomForest(FLOW~. , data=trainset[,c(15,18:ncol(trainset))], mtry=mt)
      predictions <- predict(rfmodel, testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
    colnames(modgof) <- unique(data$CDEC_ID)
  }
  
  # for random 5-fold leave multiple groups out cross validation, meaning a random 1/5 of the basins will be left out of training
  if(groupingstyle=="lmgo"){
    nfolds <- 5
    group <- as.data.frame(unique(data$CDEC_ID))
    colnames(group) <- "CDEC_ID"
    group$kftrain <- kfold(nrow(group), nfolds)
    data <- merge(data, group, by="CDEC_ID")
    
    results <- modgof <- list()
    for (k in 1:nfolds) {
      testset <- data[data$kftrain == k, ]
      trainset <- data[data$kftrain != k, ]
      rfmodel <- randomForest(FLOW~. , data=trainset[,c(15,18:ncol(trainset))], mtry=mt)
      predictions <- predict(rfmodel, testset, type='response')
      results[[k]] <- cbind(obs=testset$FLOW, pred=predictions)
      modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
    }
    names_tbd <- rownames(modgof[[1]])
    modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
    rownames(modgof) <- names_tbd
  }
  
  if(groupingstyle=="resub"){
    list(results=results, gof=modgof)
  } else if(groupingstyle=="logo"){
    list(results=results, gof=modgof)
  } else{
    list(results=results, gof=modgof, kf=group)
  }
}

# rf_agg_resub_results <- rfcv(df_lm_agg, "resub", "agg")
# rf_agg_2fold_results <- rfcv(df_lm_agg, 2L, "agg")
# rf_agg_5fold_results <- rfcv(df_lm_agg, 5L, "agg")
# rf_agg_10fold_results <- rfcv(df_lm_agg, 10L, "agg")
# rf_agg_lmgo_results <- rfcv(df_lm_agg, "lmgo", "agg")
# 
# rf_inc_resub_results <- rfcv(df_lm_inc, "resub", "inc")
# rf_inc_2fold_results <- rfcv(df_lm_inc, 2L, "inc")
# rf_inc_5fold_results <- rfcv(df_lm_inc, 5L, "inc")
# rf_inc_10fold_results <- rfcv(df_lm_inc, 10L, "inc")
# rf_inc_lmgo_results <- rfcv(df_lm_inc, "lmgo", "inc")
# 
# rf_cagg_resub_results <- rfcv(df_lm_cagg, "resub", "agg")
# rf_cagg_2fold_results <- rfcv(df_lm_cagg, 2L, "agg")
# rf_cagg_5fold_results <- rfcv(df_lm_cagg, 5L, "agg")
# rf_cagg_10fold_results <- rfcv(df_lm_cagg, 10L, "agg")
# rf_cagg_lmgo_results <- rfcv(df_lm_cagg, "lmgo", "agg")
# 
# rf_cinc_resub_results <- rfcv(df_lm_cinc, "resub", "inc")
# rf_cinc_2fold_results <- rfcv(df_lm_cinc, 2L, "inc")
# rf_cinc_5fold_results <- rfcv(df_lm_cinc, 5L, "inc")
# rf_cinc_10fold_results <- rfcv(df_lm_cinc, 10L, "inc")
# rf_cinc_lmgo_results <- rfcv(df_lm_cinc, "lmgo", "inc")

# rf_agg_logo_results <- rfcv(df_lm_agg, "logo", "agg")
# rf_inc_logo_results <- rfcv(df_lm_inc, "logo", "inc")
# rf_cagg_logo_results <- rfcv(df_lm_cagg, "logo", "agg")
# rf_cinc_logo_results <- rfcv(df_lm_cinc, "logo", "inc")

# saveRDS(rf_agg_logo_results, file="ch2 data transformations/outputdata/rds/rf_agg_logo_results.RDS")
# saveRDS(rf_inc_logo_results, file="ch2 data transformations/outputdata/rds/rf_inc_logo_results.RDS")
# saveRDS(rf_cagg_logo_results, file="ch2 data transformations/outputdata/rds/rf_cagg_logo_results.RDS")
# saveRDS(rf_cinc_logo_results, file="ch2 data transformations/outputdata/rds/rf_cinc_logo_results.RDS")

rf_agg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/rf_agg_logo_results.RDS")
rf_inc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/rf_inc_logo_results.RDS")
rf_cagg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/rf_cagg_logo_results.RDS")
rf_cinc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/rf_cinc_logo_results.RDS")
```

```{r nn_modeling_and_cv}
# # install and set up our environment for deep learning
# # devtools::install_github("rstudio/keras")
library(keras)
# install_keras(method = "conda")
# 
# nncv <- function(data, groupingstyle, datatype){
#   # the model network includes two layers of fully-connected relu activated neurons, and an output layer with no transformation. units are the number of hidden nodes
#   trainingdim <- dim(data[,c(15,18:(ncol(data)-1))])
#   nnmodel <- keras_model_sequential() %>%
#   layer_dense(units=64, activation="relu", input_shape=trainingdim[[2]]) %>%
#   layer_dense(units=64, activation="relu") %>%
#   layer_dense(units=1) # number of outputs, here we just want one prediction
#     
#   nnmodel %>% # to compile the model, loss functions are defined here
#     compile(optimizer="rmsprop", loss=keras::loss_mean_squared_error, metrics=c("mae"))
#     
#   # for resubstitution, where testing data and training data is the same
#   if(groupingstyle=="resub"){
#     trainsetpvs <- as.matrix(data[,c(15,18:(ncol(data)-1))])
#     trainsetrv <- as.matrix(data$FLOW)
#     nnmodel %>%  # this is to fit the model coefficients
#       fit(trainsetpvs, trainsetrv, epochs=100, batch_size=25, verbose=1, validation_split=0.2)
#     predictions <- nnmodel %>% predict(trainsetpvs)
#     predictions <- predictions[ , 1] # because output layer was specified to be of unit=1
#     results <- cbind(obs=trainsetrv[ , 1], pred=predictions)
#     modgof <- gof(as.data.frame(results)$pred, as.data.frame(results)$obs)
#   }
#   
#   # for k-fold cross validation
#   if(is.integer(groupingstyle)){
#     group <- kfold(data, groupingstyle)
#     results <- modgof <- list()
#     for (k in 1:groupingstyle) {
#       trainset <- data[group != k, ]
#       testset <- data[group == k, ]
#       
#       # seperate into predictor variables and response variable
#       testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
#       trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
#       testsetrv <- as.matrix(testset$FLOW)
#       trainsetrv <- as.matrix(trainset$FLOW)
#       
#       nnmodel %>% 
#         fit(trainsetpvs, trainsetrv, epochs=100, batch_size=25, verbose=1, validation_split=0.2)
#       predictions <- nnmodel %>% predict(testsetpvs)
#       predictions <- predictions[ , 1] # because output layer was specified to be of unit=1
#       results[[k]] <- cbind(obs=testsetrv[ , 1], pred=predictions)
#       modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
#     }
#     names_tbd <- rownames(modgof[[1]])
#     modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
#     rownames(modgof) <- names_tbd
#   }
#   
#   # for leave one group (basin) out cross validation
#   if(groupingstyle=="logo"){
#     results <- modgof <- list()
#   
#     for (k in 1:(length(unique(data$CDEC_ID)))){
#       h <- unique(data$CDEC_ID)[k]
#       testset <- data[data$CDEC_ID==h,]
#       trainset <- data[data$CDEC_ID!=h,]
#       testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
#       trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
#       testsetrv <- as.matrix(testset$FLOW)
#       trainsetrv <- as.matrix(trainset$FLOW)
#       
#       nnmodel %>%  
#         fit(trainsetpvs, trainsetrv, epochs=100, batch_size=25, verbose=1, validation_split=0.2)
#       predictions <- nnmodel %>% predict(testsetpvs)
#       predictions <- predictions[ , 1] # because output layer was specified to be of unit=1
#       results[[k]] <- cbind(obs=testsetrv[ , 1], pred=predictions)
#       modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
#     }
#     names_tbd <- rownames(modgof[[1]])
#     modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
#     rownames(modgof) <- names_tbd
#     colnames(modgof) <- unique(data$CDEC_ID)
#   }
#   
#   # for random 5-fold leave multiple groups out cross validation, meaning a random 1/5 of the basins will be left out of training
#   if(groupingstyle=="lmgo"){
#     nfolds <- 5
#     group <- as.data.frame(unique(data$CDEC_ID))
#     colnames(group) <- "CDEC_ID"
#     group$kftrain <- kfold(nrow(group), nfolds)
#     data <- merge(data, group, by="CDEC_ID")
#     
#     results <- modgof <- list()
#     for (k in 1:nfolds) {
#       testset <- data[data$kftrain == k, ]
#       trainset <- data[data$kftrain != k, ]
#       testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
#       trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
#       testsetrv <- as.matrix(testset$FLOW)
#       trainsetrv <- as.matrix(trainset$FLOW)
#       
#       nnmodel %>% 
#         fit(trainsetpvs, trainsetrv, epochs=100, batch_size=25, verbose=1, validation_split=0.2)
#       predictions <- nnmodel %>% predict(testsetpvs)
#       predictions <- predictions[ , 1] # because output layer was specified to be of unit=1
#       results[[k]] <- cbind(obs=testsetrv[ , 1], pred=predictions)
#       modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
#     }
#     names_tbd <- rownames(modgof[[1]])
#     modgof <- data.frame(matrix(unlist(modgof), nrow=length(modgof[[1]]), byrow=FALSE))
#     rownames(modgof) <- names_tbd
#   }
#   
#   if(groupingstyle=="resub"){
#     list(results=results, gof=modgof)
#   } else if(groupingstyle=="logo"){
#     list(results=results, gof=modgof)
#   } else{
#     list(results=results, gof=modgof, kf=group)
#   }
# }
# 
# nn_agg_logo_results <- nncv(df_lm_agg, "logo", "agg")
# nn_inc_logo_results <- nncv(df_lm_inc, "logo", "inc")
# nn_cagg_logo_results <- nncv(df_lm_cagg, "logo", "agg")
# nn_cinc_logo_results <- nncv(df_lm_cinc, "logo", "inc")
# 
# saveRDS(nn_agg_logo_results, file="ch2 data transformations/outputdata/rds/nn_agg_logo_results.RDS")
# saveRDS(nn_inc_logo_results, file="ch2 data transformations/outputdata/rds/nn_inc_logo_results.RDS")
# saveRDS(nn_cagg_logo_results, file="ch2 data transformations/outputdata/rds/nn_cagg_logo_results.RDS")
# saveRDS(nn_cinc_logo_results, file="ch2 data transformations/outputdata/rds/nn_cinc_logo_results.RDS")

nn_agg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/nn_agg_logo_results.RDS")
nn_inc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/nn_inc_logo_results.RDS")
nn_cagg_logo_results <- readRDS("ch2 data transformations/outputdata/rds/nn_cagg_logo_results.RDS")
nn_cinc_logo_results <- readRDS("ch2 data transformations/outputdata/rds/nn_cinc_logo_results.RDS")
```

For saving results
```{r data_results_df} 
# make a copy of the original dataframes to add the results to later
results_lm_agg <- df_lm_agg
results_lm_inc <- df_lm_inc
results_lm_cagg <- df_lm_cagg
results_lm_cinc <- df_lm_cinc

# notice how the lm, not glm dataset was used for the Tweedie distribution
results_glm_agg <- df_lm_agg
results_glm_inc <- df_lm_inc
results_glm_cagg <- df_lm_cagg
results_glm_cinc <- df_lm_cinc

# use the same dataset as the lm for the rf and nn
results_nn_agg <- results_rf_agg <- df_lm_agg
results_nn_inc <- results_rf_inc <- df_lm_inc
results_nn_cagg <- results_rf_cagg <- df_lm_cagg
results_nn_cinc <- results_rf_cinc <- df_lm_cinc
```

# 5.0 LOGO Post Processing 

## 5.1 Aggregate basins
```{r results_dataframes}
# put the logo results in their respective dataframes, consider making this a function so you're not copy pasting
lm_agg_logo_results_unlisted <- as.data.frame(do.call("rbind", lm_agg_logo_results$results))
results_lm_agg <- cbind(results_lm_agg, LMLOGOFIT=lm_agg_logo_results_unlisted$pred)
results_lm_agg$LMLOGORES <- results_lm_agg$LMLOGOFIT-results_lm_agg$FLOW # this is pred - obs
  
lm_cagg_logo_results_unlisted <- as.data.frame(do.call("rbind", lm_cagg_logo_results$results))
results_lm_cagg <- cbind(results_lm_cagg, LMLOGOFIT=lm_cagg_logo_results_unlisted$pred)
results_lm_cagg$LMLOGORES <- results_lm_cagg$LMLOGOFIT-results_lm_cagg$FLOW 

glm_agg_logo_results_unlisted <- as.data.frame(do.call("rbind", glm_agg_logo_results$results))
results_glm_agg <- cbind(results_glm_agg, LMLOGOFIT=glm_agg_logo_results_unlisted$pred)
results_glm_agg$LMLOGORES <- results_glm_agg$LMLOGOFIT-results_glm_agg$FLOW 
  
glm_cagg_logo_results_unlisted <- as.data.frame(do.call("rbind", glm_cagg_logo_results$results))
results_glm_cagg <- cbind(results_glm_cagg, LMLOGOFIT=glm_cagg_logo_results_unlisted$pred)
results_glm_cagg$LMLOGORES <- results_glm_cagg$LMLOGOFIT-results_glm_cagg$FLOW 

rf_agg_logo_results_unlisted <- as.data.frame(do.call("rbind", rf_agg_logo_results$results))
results_rf_agg <- cbind(results_rf_agg, LMLOGOFIT=rf_agg_logo_results_unlisted$pred)
results_rf_agg$LMLOGORES <- results_rf_agg$LMLOGOFIT-results_rf_agg$FLOW 
  
rf_cagg_logo_results_unlisted <- as.data.frame(do.call("rbind", rf_cagg_logo_results$results))
results_rf_cagg <- cbind(results_rf_cagg, LMLOGOFIT=rf_cagg_logo_results_unlisted$pred)
results_rf_cagg$LMLOGORES <- results_rf_cagg$LMLOGOFIT-results_rf_cagg$FLOW 

nn_agg_logo_results_unlisted <- as.data.frame(do.call("rbind", nn_agg_logo_results$results))
results_nn_agg <- cbind(results_nn_agg, LMLOGOFIT=nn_agg_logo_results_unlisted$pred)
results_nn_agg$LMLOGORES <- results_nn_agg$LMLOGOFIT-results_nn_agg$FLOW 
  
nn_cagg_logo_results_unlisted <- as.data.frame(do.call("rbind", nn_cagg_logo_results$results))
results_nn_cagg <- cbind(results_nn_cagg, LMLOGOFIT=nn_cagg_logo_results_unlisted$pred)
results_nn_cagg$LMLOGORES <- results_nn_cagg$LMLOGOFIT-results_nn_cagg$FLOW
```

## 5.2 Incremental Basins
```{r post_processing_lm_logo_inc}
# add the observed data from basins above back in to the incremental predictions. This makes sense for "inc" dataframes and for LOGO CV and LHO CV results only!

# put the logo results in the original dataframe format
lm_inc_logo_results_unlisted <- as.data.frame(do.call("rbind", lm_inc_logo_results$results))
results_lm_inc <- cbind(results_lm_inc, LMLOGOFIT=lm_inc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_lm_inc_wide <- dcast(melt(results_lm_inc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_lm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_lm_inc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_lm_inc_wide$DATE), ]
max(results_lm_inc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_lm_inc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_lm_inc_agg_wide <- results_lm_inc_wide
i <- 1
for(n in colnames(results_lm_inc_wide)[2:length(colnames(results_lm_inc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_lm_inc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_lm_inc_wide[, n]}
  results_lm_inc_agg_wide <- cbind(results_lm_inc_agg_wide, b_ag)
  colnames(results_lm_inc_agg_wide)[dim(results_lm_inc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_lm_inc_agg_long <- melt(results_lm_inc_agg_wide, id.vars="DATE", measure.vars = colnames(results_lm_inc_agg_wide)[69:ncol(results_lm_inc_agg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_lm_inc_agg_long) == nrow(results_lm_agg)

# put in results, merge in so that it's joined correctly
results_lm_inc_agg_long$CDEC_ID_JOIN <- substr(results_lm_inc_agg_long$CDEC_ID, 1, 3)
results_lm_agg <- merge(results_lm_agg, results_lm_inc_agg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_lm_agg$LMLOGORES_AGG <- results_lm_agg$LMLOGOFIT_AGG-results_lm_agg$FLOW
```

```{r post_processing_glm_logo_inc}
# put the logo results in the original dataframe format
glm_inc_logo_results_unlisted <- as.data.frame(do.call("rbind", glm_inc_logo_results$results))
results_glm_inc <- cbind(results_glm_inc, LMLOGOFIT=glm_inc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_glm_inc_wide <- dcast(melt(results_glm_inc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_glm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_glm_inc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_glm_inc_wide$DATE), ]
max(results_glm_inc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_glm_inc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_glm_inc_agg_wide <- results_glm_inc_wide
i <- 1
for(n in colnames(results_glm_inc_wide)[2:length(colnames(results_glm_inc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_glm_inc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_glm_inc_wide[, n]}
  results_glm_inc_agg_wide <- cbind(results_glm_inc_agg_wide, b_ag)
  colnames(results_glm_inc_agg_wide)[dim(results_glm_inc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_glm_inc_agg_long <- melt(results_glm_inc_agg_wide, id.vars="DATE", measure.vars = colnames(results_glm_inc_agg_wide)[69:ncol(results_glm_inc_agg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_glm_inc_agg_long) == nrow(results_glm_agg)

# put in results, merge in so that it's joined correctly
results_glm_inc_agg_long$CDEC_ID_JOIN <- substr(results_glm_inc_agg_long$CDEC_ID, 1, 3)
results_glm_agg <- merge(results_glm_agg, results_glm_inc_agg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_glm_agg$LMLOGORES_AGG <- results_glm_agg$LMLOGOFIT_AGG-results_glm_agg$FLOW
```

```{r post_processing_rf_logo_inc}
# put the logo results in the original dataframe format
rf_inc_logo_results_unlisted <- as.data.frame(do.call("rbind", rf_inc_logo_results$results))
results_rf_inc <- cbind(results_rf_inc, LMLOGOFIT=rf_inc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_rf_inc_wide <- dcast(melt(results_rf_inc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_glm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_rf_inc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_rf_inc_wide$DATE), ]
max(results_rf_inc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_rf_inc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_rf_inc_agg_wide <- results_rf_inc_wide
i <- 1
for(n in colnames(results_rf_inc_wide)[2:length(colnames(results_rf_inc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_rf_inc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_rf_inc_wide[, n]}
  results_rf_inc_agg_wide <- cbind(results_rf_inc_agg_wide, b_ag)
  colnames(results_rf_inc_agg_wide)[dim(results_rf_inc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_rf_inc_agg_long <- melt(results_rf_inc_agg_wide, id.vars="DATE", measure.vars = colnames(results_rf_inc_agg_wide)[69:ncol(results_rf_inc_agg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_rf_inc_agg_long) == nrow(results_rf_agg)

# put in results, merge in so that it's joined correctly
results_rf_inc_agg_long$CDEC_ID_JOIN <- substr(results_rf_inc_agg_long$CDEC_ID, 1, 3)
results_rf_agg <- merge(results_rf_agg, results_rf_inc_agg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_rf_agg$LMLOGORES_AGG <- results_rf_agg$LMLOGOFIT_AGG-results_rf_agg$FLOW
```

```{r post_processing_nn_logo_inc}
# put the logo results in the original dataframe format
nn_inc_logo_results_unlisted <- as.data.frame(do.call("rbind", nn_inc_logo_results$results))
results_nn_inc <- cbind(results_nn_inc, LMLOGOFIT=nn_inc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_nn_inc_wide <- dcast(melt(results_nn_inc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_glm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_nn_inc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_nn_inc_wide$DATE), ]
max(results_nn_inc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_nn_inc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_nn_inc_agg_wide <- results_nn_inc_wide
i <- 1
for(n in colnames(results_nn_inc_wide)[2:length(colnames(results_nn_inc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_nn_inc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_nn_inc_wide[, n]}
  results_nn_inc_agg_wide <- cbind(results_nn_inc_agg_wide, b_ag)
  colnames(results_nn_inc_agg_wide)[dim(results_nn_inc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_nn_inc_agg_long <- melt(results_nn_inc_agg_wide, id.vars="DATE", measure.vars = colnames(results_nn_inc_agg_wide)[69:ncol(results_nn_inc_agg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_nn_inc_agg_long) == nrow(results_nn_agg)

# put in results, merge in so that it's joined correctly
results_nn_inc_agg_long$CDEC_ID_JOIN <- substr(results_nn_inc_agg_long$CDEC_ID, 1, 3)
results_nn_agg <- merge(results_nn_agg, results_nn_inc_agg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_nn_agg$LMLOGORES_AGG <- results_nn_agg$LMLOGOFIT_AGG-results_nn_agg$FLOW
```

```{r post_processing_lm_logo_cinc}
# put the logo results in the original dataframe format
lm_cinc_logo_results_unlisted <- as.data.frame(do.call("rbind", lm_cinc_logo_results$results))
results_lm_cinc <- cbind(results_lm_cinc, LMLOGOFIT=lm_cinc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_lm_cinc_wide <- dcast(melt(results_lm_cinc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_lm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_lm_cinc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_lm_cinc_wide$DATE), ]
max(results_lm_cinc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_lm_cinc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_lm_cinc_cagg_wide <- results_lm_cinc_wide
i <- 1
for(n in colnames(results_lm_cinc_wide)[2:length(colnames(results_lm_cinc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_lm_cinc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_lm_cinc_wide[, n]}
  results_lm_cinc_cagg_wide <- cbind(results_lm_cinc_cagg_wide, b_ag)
  colnames(results_lm_cinc_cagg_wide)[dim(results_lm_cinc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_lm_cinc_cagg_long <- melt(results_lm_cinc_cagg_wide, id.vars="DATE", measure.vars = colnames(results_lm_cinc_cagg_wide)[69:ncol(results_lm_cinc_cagg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_lm_cinc_cagg_long) == nrow(results_lm_agg)

# put in results, merge in so that it's joined correctly
results_lm_cinc_cagg_long$CDEC_ID_JOIN <- substr(results_lm_cinc_cagg_long$CDEC_ID, 1, 3)
results_lm_cagg <- merge(results_lm_cagg, results_lm_cinc_cagg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_lm_cagg$LMLOGORES_AGG <- results_lm_cagg$LMLOGOFIT_AGG-results_lm_cagg$FLOW
```

```{r post_processing_glm_logo_cinc}
# put the logo results in the original dataframe format
glm_cinc_logo_results_unlisted <- as.data.frame(do.call("rbind", glm_cinc_logo_results$results))
results_glm_cinc <- cbind(results_glm_cinc, LMLOGOFIT=glm_cinc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_glm_cinc_wide <- dcast(melt(results_glm_cinc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_glm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_glm_cinc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_glm_cinc_wide$DATE), ]
max(results_glm_cinc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_glm_cinc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_glm_cinc_cagg_wide <- results_glm_cinc_wide
i <- 1
for(n in colnames(results_glm_cinc_wide)[2:length(colnames(results_glm_cinc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_glm_cinc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_glm_cinc_wide[, n]}
  results_glm_cinc_cagg_wide <- cbind(results_glm_cinc_cagg_wide, b_ag)
  colnames(results_glm_cinc_cagg_wide)[dim(results_glm_cinc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_glm_cinc_cagg_long <- melt(results_glm_cinc_cagg_wide, id.vars="DATE", measure.vars = colnames(results_glm_cinc_cagg_wide)[69:ncol(results_glm_cinc_cagg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_glm_cinc_cagg_long) == nrow(results_glm_cagg)

# put in results, merge in so that it's joined correctly
results_glm_cinc_cagg_long$CDEC_ID_JOIN <- substr(results_glm_cinc_cagg_long$CDEC_ID, 1, 3)
results_glm_cagg <- merge(results_glm_cagg, results_glm_cinc_cagg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_glm_cagg$LMLOGORES_AGG <- results_glm_cagg$LMLOGOFIT_AGG-results_glm_cagg$FLOW
```

```{r post_processing_rf_logo_cinc}
# put the logo results in the original dataframe format
rf_cinc_logo_results_unlisted <- as.data.frame(do.call("rbind", rf_cinc_logo_results$results))
results_rf_cinc <- cbind(results_rf_cinc, LMLOGOFIT=rf_cinc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_rf_cinc_wide <- dcast(melt(results_rf_cinc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_glm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_rf_cinc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_rf_cinc_wide$DATE), ]
max(results_rf_cinc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_rf_cinc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_rf_cinc_cagg_wide <- results_rf_cinc_wide
i <- 1
for(n in colnames(results_rf_cinc_wide)[2:length(colnames(results_rf_cinc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_rf_cinc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_rf_cinc_wide[, n]}
  results_rf_cinc_cagg_wide <- cbind(results_rf_cinc_cagg_wide, b_ag)
  colnames(results_rf_cinc_cagg_wide)[dim(results_rf_cinc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_rf_cinc_cagg_long <- melt(results_rf_cinc_cagg_wide, id.vars="DATE", measure.vars = colnames(results_rf_cinc_cagg_wide)[69:ncol(results_rf_cinc_cagg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_rf_cinc_cagg_long) == nrow(results_rf_cagg)

# put in results, merge in so that it's joined correctly
results_rf_cinc_cagg_long$CDEC_ID_JOIN <- substr(results_rf_cinc_cagg_long$CDEC_ID, 1, 3)
results_rf_cagg <- merge(results_rf_cagg, results_rf_cinc_cagg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_rf_cagg$LMLOGORES_AGG <- results_rf_cagg$LMLOGOFIT_AGG-results_rf_cagg$FLOW
```

```{r post_processing_nn_logo_cinc}
# put the logo results in the original dataframe format
nn_cinc_logo_results_unlisted <- as.data.frame(do.call("rbind", nn_cinc_logo_results$results))
results_nn_cinc <- cbind(results_nn_cinc, LMLOGOFIT=nn_cinc_logo_results_unlisted$pred)

# put the results in wide format
library(reshape2)
results_nn_cinc_wide <- dcast(melt(results_nn_cinc[,c("DATE", "CDEC_ID", "LMLOGOFIT")], id.vars=c("DATE", "CDEC_ID")), DATE~CDEC_ID) # notice the LMLOGOFIT, that's the fitted values

# results_glm_inc_wide and cdec_fnf_wide should be in the right order and record length should be the same, check. since they don't match, trim cdec_fnf_wide so they do
cdec_fnf_wide <- cdec_fnf_wide[cdec_fnf_wide$DATE>=min(results_nn_cinc_wide$DATE) & cdec_fnf_wide$DATE<=max(results_nn_cinc_wide$DATE), ]
max(results_nn_cinc_wide$DATE) == max(cdec_fnf_wide$DATE)
min(results_nn_cinc_wide$DATE) == min(cdec_fnf_wide$DATE)

# make an empty dataframe
results_nn_cinc_cagg_wide <- results_nn_cinc_wide
i <- 1
for(n in colnames(results_nn_cinc_wide)[2:length(colnames(results_nn_cinc_wide))]){
  b <- substr(n, 1, 3)
  basinabove1 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE1"]
  basinabove2 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE2"]
  basinabove3 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE3"]
  basinabove4 <- basins@data[basins$CDEC_ID == b, "STATIONS_ABOVE4"]
  if(basinabove1!="none"){
    b_ag <- results_nn_cinc_wide[, n] + cdec_fnf_wide[, basinabove1]
    if(basinabove2!="none"){
      b_ag <- b_ag + cdec_fnf_wide[, basinabove2]
      if(basinabove3!="none"){
        b_ag <- b_ag + cdec_fnf_wide[, basinabove3]
        if(basinabove4!="none"){
            b_ag <- b_ag + cdec_fnf_wide[, basinabove4]
          } else{b_ag} 
       } else{b_ag}
    } else{b_ag}
  } else{b_ag <- results_nn_cinc_wide[, n]}
  results_nn_cinc_cagg_wide <- cbind(results_nn_cinc_cagg_wide, b_ag)
  colnames(results_nn_cinc_cagg_wide)[dim(results_nn_cinc_wide)[2]+i] <- paste0(b,"_INC_AGG")
  i <- i+1
}

# make this back into long format 
results_nn_cinc_cagg_long <- melt(results_nn_cinc_cagg_wide, id.vars="DATE", measure.vars = colnames(results_nn_cinc_cagg_wide)[69:ncol(results_nn_cinc_cagg_wide)], value.name = "LMLOGOFIT_AGG", variable.name = "CDEC_ID")

# make sure they go back into long format correctly, the dataframes should be the same length, they aren't but we can merge in by id and date
nrow(results_nn_cinc_cagg_long) == nrow(results_nn_cagg)

# put in results, merge in so that it's joined correctly
results_nn_cinc_cagg_long$CDEC_ID_JOIN <- substr(results_nn_cinc_cagg_long$CDEC_ID, 1, 3)
results_nn_cagg <- merge(results_nn_cagg, results_nn_cinc_cagg_long, by.x=c("DATE", "CDEC_ID"), by.y=c("DATE", "CDEC_ID_JOIN"))
results_nn_cagg$LMLOGORES_AGG <- results_nn_cagg$LMLOGOFIT_AGG-results_nn_cagg$FLOW
```

Now everything is in agg and cagg! so use results_lm_agg, results_lm_cagg, results_glm_agg, results_glm_cagg, results_rf_agg, results_rf_cagg, results_nn_agg, results_nn_cagg

## 5.3 Cumulative Basins
```{r post_processing_lm_logo_cagg}
# use WATERYEAR to subset and de-accumulate the vector

x <- y <- list() # for LMLOGOFIT non-accumulated vector
for (i in unique(results_lm_cagg$CDEC_ID)){
  subset <- results_lm_cagg[results_lm_cagg$CDEC_ID==i,]
  # in case it's not ordered, order subset by date
  subset <- subset[order(as.Date(subset$DATE, format="%Y-%m-%d")),]

  # make empty vectors for LMLOGOFIT and LMLOGOFIT_AGG for each wateryear
  lmlogofit_nonc_vect <- lmlogofit_agg_nonc_vect <- numeric()

  for (j in unique(subset$WATERYEAR)){
    subsubset <- subset[subset$WATERYEAR==j,]
    
    # for lmlogofit offset the vector then subtract
    subsubset2 <- c(0, subsubset$LMLOGOFIT)[1:length(subsubset$LMLOGOFIT)]
    lmlogofit_nonc <- subsubset$LMLOGOFIT - subsubset2
    lmlogofit_nonc_vect <- c(lmlogofit_nonc_vect, lmlogofit_nonc)
    
    # for lmlogofit_agg offset the vector then subtract
    subsubset3 <- c(0, subsubset$LMLOGOFIT_AGG)[1:length(subsubset$LMLOGOFIT_AGG)]
    lmlogofit_agg_nonc <- subsubset$LMLOGOFIT_AGG - subsubset3
    lmlogofit_agg_nonc_vect <- c(lmlogofit_agg_nonc_vect, lmlogofit_agg_nonc)
  }
  x[[i]] <- lmlogofit_nonc_vect
  y[[i]] <- lmlogofit_agg_nonc_vect
}

LMLOGOFIT_NONC <- unlist(x)
LMLOGOFIT_AGG_NONC <- unlist(y)

# make sure the dataframes are in the same length, and put it back
nrow(results_lm_cagg) == length(LMLOGOFIT_NONC)
results_lm_cagg$LMLOGOFIT_NONC <- LMLOGOFIT_NONC
results_lm_cagg$LMLOGOFIT_AGG_NONC <- LMLOGOFIT_AGG_NONC

# for residuals we have to put it back into agg dataframes
results_to_merge <- results_lm_cagg[ , c("DATE", "CDEC_ID", "LMLOGOFIT_NONC", "LMLOGOFIT_AGG_NONC")]
results_lm_agg <- merge(results_lm_agg, results_to_merge, by=c("DATE", "CDEC_ID"))
results_lm_agg$LMLOGORES_NONC <- results_lm_agg$LMLOGOFIT_NONC - results_lm_agg$FLOW
results_lm_agg$LMLOGORES_AGG_NONC <- results_lm_agg$LMLOGOFIT_AGG_NONC - results_lm_agg$FLOW
```

```{r post_processing_glm_logo_cagg}
x <- y <- list() # for LMLOGOFIT non-accumulated vector
for (i in unique(results_glm_cagg$CDEC_ID)){
  subset <- results_glm_cagg[results_glm_cagg$CDEC_ID==i,]
  # in case it's not ordered, order subset by date
  subset <- subset[order(as.Date(subset$DATE, format="%Y-%m-%d")),]

  # make empty vectors for LMLOGOFIT and LMLOGOFIT_AGG for each wateryear
  glmlogofit_nonc_vect <- glmlogofit_agg_nonc_vect <- numeric()

  for (j in unique(subset$WATERYEAR)){
    subsubset <- subset[subset$WATERYEAR==j,]
    
    # for lmlogofit offset the vector then subtract
    subsubset2 <- c(0, subsubset$LMLOGOFIT)[1:length(subsubset$LMLOGOFIT)]
    glmlogofit_nonc <- subsubset$LMLOGOFIT - subsubset2
    glmlogofit_nonc_vect <- c(glmlogofit_nonc_vect, glmlogofit_nonc)
    
    # for lmlogofit_agg offset the vector then subtract
    subsubset3 <- c(0, subsubset$LMLOGOFIT_AGG)[1:length(subsubset$LMLOGOFIT_AGG)]
    glmlogofit_agg_nonc <- subsubset$LMLOGOFIT_AGG - subsubset3
    glmlogofit_agg_nonc_vect <- c(glmlogofit_agg_nonc_vect, glmlogofit_agg_nonc)
  }
  x[[i]] <- glmlogofit_nonc_vect
  y[[i]] <- glmlogofit_agg_nonc_vect
}

LMLOGOFIT_NONC <- unlist(x)
LMLOGOFIT_AGG_NONC <- unlist(y)

# make sure the dataframes are in the same length, and put it back
nrow(results_glm_cagg) == length(LMLOGOFIT_NONC)
results_glm_cagg$LMLOGOFIT_NONC <- LMLOGOFIT_NONC
results_glm_cagg$LMLOGOFIT_AGG_NONC <- LMLOGOFIT_AGG_NONC

# for residuals we have to put it back into agg dataframes
results_to_merge <- results_glm_cagg[ , c("DATE", "CDEC_ID", "LMLOGOFIT_NONC", "LMLOGOFIT_AGG_NONC")]
results_glm_agg <- merge(results_glm_agg, results_to_merge, by=c("DATE", "CDEC_ID"))
results_glm_agg$LMLOGORES_NONC <- results_glm_agg$LMLOGOFIT_NONC - results_glm_agg$FLOW
results_glm_agg$LMLOGORES_AGG_NONC <- results_glm_agg$LMLOGOFIT_AGG_NONC - results_glm_agg$FLOW
```

```{r post_processing_rf_logo_cagg}
x <- y <- list() # for LMLOGOFIT non-accumulated vector
for (i in unique(results_rf_cagg$CDEC_ID)){
  subset <- results_rf_cagg[results_rf_cagg$CDEC_ID==i,]
  # in case it's not ordered, order subset by date
  subset <- subset[order(as.Date(subset$DATE, format="%Y-%m-%d")),]

  # make empty vectors for LMLOGOFIT and LMLOGOFIT_AGG for each wateryear
  rflogofit_nonc_vect <- rflogofit_agg_nonc_vect <- numeric()

  for (j in unique(subset$WATERYEAR)){
    subsubset <- subset[subset$WATERYEAR==j,]
    
    # for lmlogofit offset the vector then subtract
    subsubset2 <- c(0, subsubset$LMLOGOFIT)[1:length(subsubset$LMLOGOFIT)]
    rflogofit_nonc <- subsubset$LMLOGOFIT - subsubset2
    rflogofit_nonc_vect <- c(rflogofit_nonc_vect, rflogofit_nonc)
    
    # for lmlogofit_agg offset the vector then subtract
    subsubset3 <- c(0, subsubset$LMLOGOFIT_AGG)[1:length(subsubset$LMLOGOFIT_AGG)]
    rflogofit_agg_nonc <- subsubset$LMLOGOFIT_AGG - subsubset3
    rflogofit_agg_nonc_vect <- c(rflogofit_agg_nonc_vect, rflogofit_agg_nonc)
  }
  x[[i]] <- rflogofit_nonc_vect
  y[[i]] <- rflogofit_agg_nonc_vect
}

LMLOGOFIT_NONC <- unlist(x)
LMLOGOFIT_AGG_NONC <- unlist(y)

# make sure the dataframes are in the same length, and put it back
nrow(results_rf_cagg) == length(LMLOGOFIT_NONC)
results_rf_cagg$LMLOGOFIT_NONC <- LMLOGOFIT_NONC
results_rf_cagg$LMLOGOFIT_AGG_NONC <- LMLOGOFIT_AGG_NONC

# for residuals we have to put it back into agg dataframes
results_to_merge <- results_rf_cagg[ , c("DATE", "CDEC_ID", "LMLOGOFIT_NONC", "LMLOGOFIT_AGG_NONC")]
results_rf_agg <- merge(results_rf_agg, results_to_merge, by=c("DATE", "CDEC_ID"))
results_rf_agg$LMLOGORES_NONC <- results_rf_agg$LMLOGOFIT_NONC - results_rf_agg$FLOW
results_rf_agg$LMLOGORES_AGG_NONC <- results_rf_agg$LMLOGOFIT_AGG_NONC - results_rf_agg$FLOW
```

```{r post_processing_nn_logo_cagg}
x <- y <- list() # for LMLOGOFIT non-accumulated vector
for (i in unique(results_nn_cagg$CDEC_ID)){
  subset <- results_nn_cagg[results_nn_cagg$CDEC_ID==i,]
  # in case it's not ordered, order subset by date
  subset <- subset[order(as.Date(subset$DATE, format="%Y-%m-%d")),]

  # make empty vectors for LMLOGOFIT and LMLOGOFIT_AGG for each wateryear
  nnlogofit_nonc_vect <- nnlogofit_agg_nonc_vect <- numeric()

  for (j in unique(subset$WATERYEAR)){
    subsubset <- subset[subset$WATERYEAR==j,]
    
    # for lmlogofit offset the vector then subtract
    subsubset2 <- c(0, subsubset$LMLOGOFIT)[1:length(subsubset$LMLOGOFIT)]
    nnlogofit_nonc <- subsubset$LMLOGOFIT - subsubset2
    nnlogofit_nonc_vect <- c(nnlogofit_nonc_vect, nnlogofit_nonc)
    
    # for lmlogofit_agg offset the vector then subtract
    subsubset3 <- c(0, subsubset$LMLOGOFIT_AGG)[1:length(subsubset$LMLOGOFIT_AGG)]
    nnlogofit_agg_nonc <- subsubset$LMLOGOFIT_AGG - subsubset3
    nnlogofit_agg_nonc_vect <- c(nnlogofit_agg_nonc_vect, nnlogofit_agg_nonc)
  }
  x[[i]] <- nnlogofit_nonc_vect
  y[[i]] <- nnlogofit_agg_nonc_vect
}

LMLOGOFIT_NONC <- unlist(x)
LMLOGOFIT_AGG_NONC <- unlist(y)

# make sure the dataframes are in the same length, and put it back
nrow(results_nn_cagg) == length(LMLOGOFIT_NONC)
results_nn_cagg$LMLOGOFIT_NONC <- LMLOGOFIT_NONC
results_nn_cagg$LMLOGOFIT_AGG_NONC <- LMLOGOFIT_AGG_NONC

# for residuals we have to put it back into agg dataframes
results_to_merge <- results_nn_cagg[ , c("DATE", "CDEC_ID", "LMLOGOFIT_NONC", "LMLOGOFIT_AGG_NONC")]
results_nn_agg <- merge(results_nn_agg, results_to_merge, by=c("DATE", "CDEC_ID"))
results_nn_agg$LMLOGORES_NONC <- results_nn_agg$LMLOGOFIT_NONC - results_nn_agg$FLOW
results_nn_agg$LMLOGORES_AGG_NONC <- results_nn_agg$LMLOGOFIT_AGG_NONC - results_nn_agg$FLOW
```

```{r results_cleanup}
# no longer needed 
remove(n)
remove(i)
remove(j)
remove(b)
remove(b_ag)
remove(basinabove1)
remove(basinabove2)
remove(basinabove3)
remove(basinabove4)
remove(subset)
remove(subsubset)
remove(subsubset2)
remove(subsubset3)
remove(x)
remove(y)
remove(LMLOGOFIT_NONC)
remove(LMLOGOFIT_AGG_NONC)
remove(lmlogofit_nonc)
remove(lmlogofit_agg_nonc)
remove(lmlogofit_nonc_vect)
remove(lmlogofit_agg_nonc_vect)
remove(glmlogofit_nonc)
remove(glmlogofit_agg_nonc)
remove(glmlogofit_nonc_vect)
remove(glmlogofit_agg_nonc_vect)
remove(rflogofit_nonc)
remove(rflogofit_agg_nonc)
remove(rflogofit_nonc_vect)
remove(rflogofit_agg_nonc_vect)
remove(nnlogofit_nonc)
remove(nnlogofit_agg_nonc)
remove(nnlogofit_nonc_vect)
remove(nnlogofit_agg_nonc_vect)

# make new data frame with all results to use from here on!
results_lm <- results_lm_agg
results_glm <- results_glm_agg
results_rf <- results_rf_agg
results_nn <- results_nn_agg

# merge models in case needed for comparison plots 
colnames(results_glm_agg)[43:51] <- c("GLMLOGOFIT", "GLMLOGORES", "CDEC_ID.y", "GLMLOGOFIT_AGG", "GLMLOGORES_AGG", "GLMLOGOFIT_NONC", "GLMLOGOFIT_AGG_NONC", "GLMLOGORES_NONC", "GLMLOGORES_AGG_NONC")
colnames(results_rf_agg)[43:51] <- c("RFLOGOFIT", "RFLOGORES", "CDEC_ID.y", "RFLOGOFIT_AGG", "RFLOGORES_AGG", "RFLOGOFIT_NONC", "RFLOGOFIT_AGG_NONC", "RFLOGORES_NONC", "RFLOGORES_AGG_NONC")
colnames(results_nn_agg)[43:51] <- c("NNLOGOFIT", "NNLOGORES", "CDEC_ID.y", "NNLOGOFIT_AGG", "NNLOGORES_AGG", "NNLOGOFIT_NONC", "NNLOGOFIT_AGG_NONC", "NNLOGORES_NONC", "NNLOGORES_AGG_NONC")

results_all <- merge(results_lm, results_glm_agg[, c("DATE", "CDEC_ID", "GLMLOGOFIT", "GLMLOGORES", "GLMLOGOFIT_AGG", "GLMLOGORES_AGG", "GLMLOGOFIT_NONC", "GLMLOGOFIT_AGG_NONC", "GLMLOGORES_NONC", "GLMLOGORES_AGG_NONC" )], by=c("DATE", "CDEC_ID"))
results_all <- merge(results_all, results_rf_agg[, c("DATE", "CDEC_ID", "RFLOGOFIT", "RFLOGORES", "RFLOGOFIT_AGG", "RFLOGORES_AGG", "RFLOGOFIT_NONC", "RFLOGOFIT_AGG_NONC", "RFLOGORES_NONC", "RFLOGORES_AGG_NONC" )], by=c("DATE", "CDEC_ID"))
results_all <- merge(results_all, results_nn_agg[, c("DATE", "CDEC_ID", "NNLOGOFIT", "NNLOGORES", "NNLOGOFIT_AGG", "NNLOGORES_AGG", "NNLOGOFIT_NONC", "NNLOGOFIT_AGG_NONC", "NNLOGORES_NONC", "NNLOGORES_AGG_NONC" )], by=c("DATE", "CDEC_ID"))

# number of observations for each CDEC_ID in the two datasets
aggregate(FLOW ~ CDEC_ID, data = results_lm, FUN = length)
aggregate(FLOW ~ CDEC_ID, data = results_glm, FUN = length)
aggregate(FLOW ~ CDEC_ID, data = results_rf, FUN = length)
aggregate(FLOW ~ CDEC_ID, data = results_nn, FUN = length)

# quick look at the observed coefficient of variation by hierarchy (addressing Jay's comment)
length_byh <- aggregate(FLOW ~ HIERARCHY, data = results_nn, FUN = length)
sd_byh <- aggregate(FLOW ~ HIERARCHY, data = results_nn, FUN = sd)
mean_byh <- aggregate(FLOW ~ HIERARCHY, data = results_nn, FUN = mean)
coefofvar_byh <- sd_byh$FLOW/mean_byh$FLOW
stats_byh <- data.frame(cbind(HIERARCHY=length_byh$HIERARCHY, LENGTH=length_byh$FLOW, SD=sd_byh$FLOW, MEAN=mean_byh$FLOW, COEFVAR=coefofvar_byh))
stats_byh$HIERARCHY <- factor(stats_byh$HIERARCHY, levels=c("5", "4", "3", "2", "1"))

# ggplot(stats_byh)+
# geom_point(aes(x=COEFVAR, y=HIERARCHY))
```
Now everything is in results_all!

Note how we are not removing the epsilon (=1 AF) that we added to the FLOW for the glm modeling. It's just too small to worry about.  

# 6.0 Test & Analyze
There are four things we are looking for when analyzing residuals:
* The mean of the errors is zero (and the sum of the errors is zero)
* The distribution of the errors are normal.
* All of the errors are independent.
* Variance of errors is constant (Homoscedastic)

```{r lm_tests}
lmanalysistests <- function(lmmodel){
  library(fBasics)
  # residuals are normally distributed? test residuals for normality; null hypothesis: Skewness and Kurtosis are equal to zero
  jb <- jarqueberaTest(lmmodel$resid) 
  
  library(lmtest)
  # residuals are independent? dwtest; test for independence of residuals; null hypothesis: Errors are serially uncorrelated
  dw <- dwtest(lmmodel)
  
  # return both
  list(jb=jb, dw=dw)
}

# lapply(lm_agg_logo_results$mod, lmanalysistests)
# lapply(lm_agg_logo_results$mod, lmanalysistests)
# lapply(lm_inc_logo_results$mod, lmanalysistests)
# lapply(lm_cagg_logo_results$mod, lmanalysistests)
# lapply(lm_cinc_logo_results$mod, lmanalysistests)
# # seems like in all of them alternative hypothesis holds: non-normal residuals and true autocorrelation is greater than 0
```

```{r lm_analysis_plots}
# datatype can be: "agg", "inc", "cagg", "cinc"
# modeltype can be: "lm", "glm", "rf", "nn"

lmanalysisplots <- function(resultsdf, datatype, modeltype){
  # get the columns of interest
  if(datatype=="agg"){
    res_of_interest <- resultsdf$LMLOGORES
    fit_of_interest <- resultsdf$LMLOGOFIT
  } else if(datatype=="inc"){
    res_of_interest <- resultsdf$LMLOGORES_AGG
    fit_of_interest <- resultsdf$LMLOGOFIT_AGG    
  } else if(datatype=="cagg"){
    res_of_interest <- resultsdf$LMLOGORES_NONC
    fit_of_interest <- resultsdf$LMLOGOFIT_NONC    
  } else { # for datatype=="cinc" case
    res_of_interest <- resultsdf$LMLOGORES_AGG_NONC
    fit_of_interest <- resultsdf$LMLOGOFIT_AGG_NONC   
  }
  
  # 1st plot: residuals v response
  png(paste0('ch2 data transformations/outputdata/rplot21_', modeltype, 'logo_residvresp_', datatype, '.png'), width=6.5, height=3, units="in", pointsize=8, res=1200)
  
  plot(res_of_interest ~ resultsdf$FLOW, xlab="Unimpaired Flow (AF/m)", ylab="Residuals (AF/m)") # ylim=c(-1.5e7, 6e6), xlim=c(0, 2e7)
  abline(h=0,lty=2, col=cbpblack[6])
  dev.off()
  
  # 2nd plot: residuals over time
  png(paste0('ch2 data transformations/outputdata/rplot22_', modeltype, 'logo_residovertime_', datatype, '.png'), width=6.5, height=3, units="in", pointsize=8, res=1200)
  plot(resultsdf$DATE, res_of_interest, xlab="",ylab="Residuals (AF/m)", xaxt = "n") #, ylim=c(-1.5e7, 6e6)
  labDates <- seq(min(resultsdf$DATE), max(resultsdf$DATE), by = "12 months")
  axis.Date(side = 1, resultsdf$DATE, at = labDates, format = "%b %y", las = 2)
  abline(h=0,lty=2, col=cbpblack[6])
  dev.off()
  
  # 3rd plot: histogram of residuals
  png(paste0('ch2 data transformations/outputdata/rplot23_', modeltype, 'logo_histofresid_', datatype, '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  hist(res_of_interest, ylab="Frequency", xlab="Residuals (AF/m)", main="") #main="Histogram of Residuals" #, ylim=c(0,1e4)
  abline(v=0,lty=2, col=cbpblack[6])
  dev.off()
  
  # 4th plot: q-q plot
  png(paste0('ch2 data transformations/outputdata/rplot24_', modeltype, 'logo_qq_', datatype, '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  qqnorm(res_of_interest, main="") # main="Normal Q-Q Plot" #, ylim=c(-1.5e7, 6e6)
  qqline(res_of_interest, col=cbpblack[6], lty=2)
  dev.off()
  
  # # 5th plot: studentized residuals
  # png(paste0('outputdata/rplot25_', modeltype, 'logo_studentizedresiduals_', datatype, '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  # plot(fit_of_interest, rstudent(lmmodel), main="Studentized Residuals vs. Predictions", xlab="Predictions (acre-feet/month)", ylab="Studentized Residuals (-)", ylim=c(-25,25))
  # #xlim=c(-1e6, 5e6)
  # abline(h=0, lty=2, col=cbpblack[6])
  # dev.off()
}

lmanalysisplots(results_lm, "agg", "lm")
lmanalysisplots(results_lm, "cagg", "lm")
lmanalysisplots(results_lm, "inc", "lm")
lmanalysisplots(results_lm, "cinc", "lm")

lmanalysisplots(results_glm, "agg", "glm")
lmanalysisplots(results_glm, "cagg", "glm")
lmanalysisplots(results_glm, "inc", "glm")
lmanalysisplots(results_glm, "cinc", "glm")

lmanalysisplots(results_rf, "agg", "rf")
lmanalysisplots(results_rf, "cagg", "rf")
lmanalysisplots(results_rf, "inc", "rf")
lmanalysisplots(results_rf, "cinc", "rf")

lmanalysisplots(results_nn, "agg", "nn")
lmanalysisplots(results_nn, "cagg", "nn")
lmanalysisplots(results_nn, "inc", "nn")
lmanalysisplots(results_nn, "cinc", "nn")
```

# 7.0 Visual Fit
```{r timeseries_plots}
# datatype can be: "agg", "inc", "cagg", "cinc"
# modelform can be: "lm", "glm", "rf", "nn"

library(reshape2)
library(ggplot2)
tsresultsplots <- function(resultsdf, datatype, modelform){   
  for (r in 1:(length(unique(resultsdf$CDEC_ID)))){ 
    # plot time series by basin
    h <- unique(resultsdf$CDEC_ID)[r]
    resultsdf_sub <- resultsdf[resultsdf$CDEC_ID==h,]
    
    # convert the units. AREASQKM is in square kilometer, PPT is in mm/month, FLOW is in AF/month 
    watershedArea_sqft <- resultsdf_sub$AREASQM[1]*(1000*100/2.54/12)^2
    resultsdf_sub$precip_ft <- resultsdf_sub$PPT/10/2.54/12
    resultsdf_sub$precip_cuft <- resultsdf_sub$precip_ft * watershedArea_sqft
    resultsdf_sub$precip_cfs <- resultsdf_sub$precip_cuft/30.5/24/60/60
    resultsdf_sub$discharge_cfs <- resultsdf_sub$FLOW*0.01656433739228
    
    # get the columns of interest
    if(datatype=="agg"){
      res_of_interest <- resultsdf_sub$LMLOGORES
      fit_of_interest <- resultsdf_sub$LMLOGOFIT
    } else if(datatype=="inc"){
      res_of_interest <- resultsdf_sub$LMLOGORES_AGG
      fit_of_interest <- resultsdf_sub$LMLOGOFIT_AGG    
    } else if(datatype=="cagg"){
      res_of_interest <- resultsdf_sub$LMLOGORES_NONC
      fit_of_interest <- resultsdf_sub$LMLOGOFIT_NONC    
    } else { # for datatype=="cinc" case
      res_of_interest <- resultsdf_sub$LMLOGORES_AGG_NONC
      fit_of_interest <- resultsdf_sub$LMLOGOFIT_AGG_NONC   
    }
    
    # now convert the units
    resultsdf_sub$discharge_fit_cfs <- fit_of_interest*0.01656433739228
    
    # remove NAs here?
    resultsdf_sub <- na.omit(resultsdf_sub)
    
    # calculate the range needed to avoid having your hyetograph and hydrograph overlap 
    maxRange <- 1.1*(max(resultsdf_sub$precip_cfs) + max(max(resultsdf_sub$discharge_cfs), max(resultsdf_sub$discharge_fit_cfs, na.rm=TRUE)))
  
    # create a function to backtransform the axis labels for precipitation, for some reason multiplying it by -1 fixed the labels, kinda hacky but whatever
    precip_labels <- function(x) {round((-1*x / watershedArea_sqft) * 12 *30.5*24*60*60, 0)} # labels in inches/month
    
    # melt for ggplot dataframe
    results_sub_melted <- melt(resultsdf_sub[, c("DATE", "discharge_cfs", "discharge_fit_cfs" )], id.var='DATE')
    
    # make the plot
    hydrograph <- ggplot(data = results_sub_melted, 
                         aes(x = DATE, y=value, col=variable)) + 
      xlab("")  + 
      ggtitle(paste0('Basin CDEC ID: ', h)) +
      
      # use geom_tile to create the inverted hyetograph. geom_tile has a bug that displays a warning message for height and width, you can ignore it.
      geom_tile(data=resultsdf_sub, aes(y = -1*(precip_cfs/2-maxRange), # y = the center point of each bar
                height = precip_cfs,
                width = 2),
                fill = cbpblack[6],
                color = cbpblack[6]) +
    
      # plot your discharge data
      geom_line() +
      scale_colour_manual("legend:", values = cbpblack[c(1,3)], labels=c("observed", "predicted")) +
      # scale_linetype_manual("legend:", values = c("solid", "dashed")) +
      theme(legend.position="bottom", legend.title = element_blank()) +
    
      # create a second axis with sec_axis() and format the labels to display the original precipitation units
      scale_y_continuous(name = "Discharge (cfs)", sec.axis = sec_axis(trans = ~1*(.-maxRange), name = "Precipitation (in/m)", labels = precip_labels)) # labels are in inches/s
    
    png(paste0('ch2 data transformations/outputdata/timeseries_', modelform, "_", datatype, '/timeseries_', h, '.png'), width=12, height=3.5, units="in", pointsize=12, res=1200)
    par(mar=c(5,4,1,1)+0.1, ps=8, cex=1)
    print(hydrograph)
    dev.off()
  }
}

tsresultsplots(results_lm, "agg", "lm")
tsresultsplots(results_lm, "inc", "lm")
tsresultsplots(results_lm, "cagg", "lm")
tsresultsplots(results_lm, "cinc", "lm")

tsresultsplots(results_glm, "agg", "glm")
tsresultsplots(results_glm, "inc", "glm")
tsresultsplots(results_glm, "cagg", "glm")
tsresultsplots(results_glm, "cinc", "glm")

tsresultsplots(results_rf, "agg", "rf")
tsresultsplots(results_rf, "cagg", "rf")
tsresultsplots(results_rf, "inc", "rf")
tsresultsplots(results_rf, "cinc", "rf")

tsresultsplots(results_nn, "agg", "nn")
tsresultsplots(results_nn, "cagg", "nn")
tsresultsplots(results_nn, "inc", "nn")
tsresultsplots(results_nn, "cinc", "nn")
```

Need to modify these to accommodate the RF and NN
```{r tsplots_comp}
for (r in 1:(length(unique(results_all$CDEC_ID)))){ 
  # plot time series by basin
  h <- unique(results_all$CDEC_ID)[r]
  resultsdf_sub <- results_all[results_all$CDEC_ID==h,]
  
  # convert the units. AREASQKM is in square kilometer, PPT is in mm/month, FLOW is in AF/month 
  watershedArea_sqft <- resultsdf_sub$AREASQM[1]*(1000*100/2.54/12)^2
  resultsdf_sub$precip_ft <- resultsdf_sub$PPT/10/2.54/12
  resultsdf_sub$precip_cuft <- resultsdf_sub$precip_ft * watershedArea_sqft
  resultsdf_sub$precip_cfs <- resultsdf_sub$precip_cuft/30.5/24/60/60
  resultsdf_sub$discharge_cfs <- resultsdf_sub$FLOW*0.01656433739228
  
  resultsdf_sub$LMLOGOFIT_cfs <- resultsdf_sub$LMLOGOFIT*0.01656433739228
  resultsdf_sub$LMLOGOFIT_AGG_cfs <- resultsdf_sub$LMLOGOFIT_AGG*0.01656433739228
  resultsdf_sub$LMLOGOFIT_NONC_cfs <- resultsdf_sub$LMLOGOFIT_NONC*0.01656433739228
  resultsdf_sub$LMLOGOFIT_AGG_NONC_cfs <- resultsdf_sub$LMLOGOFIT_AGG_NONC*0.01656433739228
  resultsdf_sub$GLMLOGOFIT_cfs <- resultsdf_sub$GLMLOGOFIT*0.01656433739228
  resultsdf_sub$GLMLOGOFIT_AGG_cfs <- resultsdf_sub$GLMLOGOFIT_AGG*0.01656433739228
  resultsdf_sub$GLMLOGOFIT_NONC_cfs <- resultsdf_sub$GLMLOGOFIT_NONC*0.01656433739228
  resultsdf_sub$GLMLOGOFIT_AGG_NONC_cfs <- resultsdf_sub$GLMLOGOFIT_AGG_NONC*0.01656433739228
  resultsdf_sub$RFLOGOFIT_cfs <- resultsdf_sub$RFLOGOFIT*0.01656433739228
  resultsdf_sub$RFLOGOFIT_AGG_cfs <- resultsdf_sub$RFLOGOFIT_AGG*0.01656433739228
  resultsdf_sub$RFLOGOFIT_NONC_cfs <- resultsdf_sub$RFLOGOFIT_NONC*0.01656433739228
  resultsdf_sub$RFLOGOFIT_AGG_NONC_cfs <- resultsdf_sub$RFLOGOFIT_AGG_NONC*0.01656433739228

  # remove NAs here?
  resultsdf_sub <- na.omit(resultsdf_sub)
  
  # calculate the range needed to avoid having your hyetograph and hydrograph overlap 
  maxFlow <- max(max(resultsdf_sub$discharge_cfs), 
                 max(resultsdf_sub$LMLOGOFIT_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$LMLOGOFIT_AGG_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$LMLOGOFIT_NONC_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$LMLOGOFIT_AGG_NONC_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$GLMLOGOFIT_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$GLMLOGOFIT_AGG_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$GLMLOGOFIT_NONC_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$GLMLOGOFIT_AGG_NONC_cfs, na.rm=TRUE),
                 max(resultsdf_sub$RFLOGOFIT_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$RFLOGOFIT_AGG_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$RFLOGOFIT_NONC_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$RFLOGOFIT_AGG_NONC_cfs, na.rm=TRUE))
  maxRange <- 1.1*(max(resultsdf_sub$precip_cfs) + maxFlow)

  # create a function to backtransform the axis labels for precipitation, for some reason multiplying it by -1 fixed the labels, kinda hacky but whatever
  precip_labels <- function(x) {round((-1*x/watershedArea_sqft)*12*30.5*24*60*60, 0)} # labels in inches/month
  
  # melt for ggplot dataframe
  results_sub_melted <- melt(resultsdf_sub[, c("DATE", "discharge_cfs", "LMLOGOFIT_cfs", "LMLOGOFIT_AGG_cfs", "LMLOGOFIT_NONC_cfs", "LMLOGOFIT_AGG_NONC_cfs", "GLMLOGOFIT_cfs", "GLMLOGOFIT_AGG_cfs", "GLMLOGOFIT_NONC_cfs", "GLMLOGOFIT_AGG_NONC_cfs", "RFLOGOFIT_cfs", "RFLOGOFIT_AGG_cfs", "RFLOGOFIT_NONC_cfs", "RFLOGOFIT_AGG_NONC_cfs")], id.var='DATE')
  
  # make the plot
  hydrograph <- ggplot(data = results_sub_melted, 
                       aes(x = DATE, y=value, col=variable)) + 
    xlab("")  + 
    ggtitle(paste0('Basin CDEC ID: ', h)) +
    
    # use geom_tile to create the inverted hyetograph. geom_tile has a bug that displays a warning message for height and width, you can ignore it.
    geom_tile(data=resultsdf_sub, aes(y = -1*(precip_cfs/2-maxRange), # y = the center point of each bar
              height = precip_cfs,
              width = 2),
              fill = cbpblack[6],
              color = cbpblack[6]) +
  
    # plot your discharge data
    geom_line() +
    scale_colour_manual("legend:", values = c(cbpblack, cbpgrey[1], "red", "green", "blue", "goldenrod"), labels=c("Obs", "LM Agg", "LM Inc", "LM Cagg", "LM Cinc", "GLM Agg", "GLM Inc", "GLM Cagg", "GLM Cinc", "RF Agg", "RF Inc", "RF Cagg", "RF Cinc")) +
    theme(legend.position="bottom", legend.title = element_blank()) +
  
    # create a second axis with sec_axis() and format the labels to display the original precipitation units
    scale_y_continuous(name = "Discharge (cfs)", sec.axis = sec_axis(trans = ~1*(.-maxRange), name = "Precipitation (in/m)", labels = precip_labels)) # labels are in inches/s
  
  png(paste0('ch2 data transformations/outputdata/timeseries_all/timeseries_', h, '.png'), width=6.5, height=3.5, units="in", pointsize=12, res=1200)
  par(mar=c(5,4,1,1)+0.1, ps=8, cex=1)
  print(hydrograph)
  dev.off()
}
```

```{r tsplots_comp2}
for (r in 1:(length(unique(results_all$CDEC_ID)))){ 
  # plot time series by basin
  h <- unique(results_all$CDEC_ID)[r]
  resultsdf_sub <- results_all[results_all$CDEC_ID==h,]
  
  # convert the units. AREASQKM is in square kilometer, PPT is in mm/month, FLOW is in AF/month 
  watershedArea_sqft <- resultsdf_sub$AREASQM[1]*(1000*100/2.54/12)^2
  resultsdf_sub$precip_ft <- resultsdf_sub$PPT/10/2.54/12
  resultsdf_sub$precip_cuft <- resultsdf_sub$precip_ft * watershedArea_sqft
  resultsdf_sub$precip_cfs <- resultsdf_sub$precip_cuft/30.5/24/60/60
  resultsdf_sub$discharge_cfs <- resultsdf_sub$FLOW*0.01656433739228
  
  resultsdf_sub$LMLOGOFIT_cfs <- resultsdf_sub$LMLOGOFIT*0.01656433739228
  resultsdf_sub$LMLOGOFIT_AGG_cfs <- resultsdf_sub$LMLOGOFIT_AGG*0.01656433739228
  # resultsdf_sub$LMLOGOFIT_NONC_cfs <- resultsdf_sub$LMLOGOFIT_NONC*0.01656433739228
  # resultsdf_sub$LMLOGOFIT_AGG_NONC_cfs <- resultsdf_sub$LMLOGOFIT_AGG_NONC*0.01656433739228
  resultsdf_sub$GLMLOGOFIT_cfs <- resultsdf_sub$GLMLOGOFIT*0.01656433739228
  resultsdf_sub$GLMLOGOFIT_AGG_cfs <- resultsdf_sub$GLMLOGOFIT_AGG*0.01656433739228
  # resultsdf_sub$GLMLOGOFIT_NONC_cfs <- resultsdf_sub$GLMLOGOFIT_NONC*0.01656433739228
  # resultsdf_sub$GLMLOGOFIT_AGG_NONC_cfs <- resultsdf_sub$GLMLOGOFIT_AGG_NONC*0.01656433739228
  resultsdf_sub$RFLOGOFIT_cfs <- resultsdf_sub$RFLOGOFIT*0.01656433739228
  resultsdf_sub$RFLOGOFIT_AGG_cfs <- resultsdf_sub$RFLOGOFIT_AGG*0.01656433739228
  # resultsdf_sub$RFLOGOFIT_NONC_cfs <- resultsdf_sub$RFLOGOFIT_NONC*0.01656433739228
  # resultsdf_sub$RFLOGOFIT_AGG_NONC_cfs <- resultsdf_sub$RFLOGOFIT_AGG_NONC*0.01656433739228
  
  # remove NAs here?
  resultsdf_sub <- na.omit(resultsdf_sub)
  
  # calculate the range needed to avoid having your hyetograph and hydrograph overlap 
  maxFlow <- max(max(resultsdf_sub$discharge_cfs), 
                 max(resultsdf_sub$LMLOGOFIT_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$LMLOGOFIT_AGG_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$GLMLOGOFIT_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$GLMLOGOFIT_AGG_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$RFLOGOFIT_cfs, na.rm=TRUE), 
                 max(resultsdf_sub$RFLOGOFIT_AGG_cfs, na.rm=TRUE))
  maxRange <- 1.1*(max(resultsdf_sub$precip_cfs) + maxFlow)

  # create a function to backtransform the axis labels for precipitation, for some reason multiplying it by -1 fixed the labels, kinda hacky but whatever
  precip_labels <- function(x) {round((-1*x/watershedArea_sqft)*12*30.5*24*60*60, 0)} # labels in inches/month
  
  # melt for ggplot dataframe
  results_sub_melted <- melt(resultsdf_sub[, c("DATE", "discharge_cfs", "LMLOGOFIT_cfs", "LMLOGOFIT_AGG_cfs", "GLMLOGOFIT_cfs", "GLMLOGOFIT_AGG_cfs", "RFLOGOFIT_cfs", "RFLOGOFIT_AGG_cfs")], id.var='DATE')
  
  # make the plot
  hydrograph <- ggplot(data = results_sub_melted, 
                       aes(x = DATE, y=value, col=variable)) + 
    xlab("")  + 
    ggtitle(paste0('Basin CDEC ID: ', h)) +
    
    # use geom_tile to create the inverted hyetograph. geom_tile has a bug that displays a warning message for height and width, you can ignore it.
    geom_tile(data=resultsdf_sub, aes(y = -1*(precip_cfs/2-maxRange), # y = the center point of each bar
              height = precip_cfs,
              width = 2),
              fill = cbpblack[6],
              color = cbpblack[6]) +
  
    # plot your discharge data
    geom_line() +
    scale_colour_manual("legend:", values = c(cbpblack[1:7]), labels=c("Obs", "LM Agg", "LM Inc", "GLM Agg", "GLM Inc", "RF Agg", "RF Inc")) +
    theme(legend.position="bottom", legend.title = element_blank()) +
  
    # create a second axis with sec_axis() and format the labels to display the original precipitation units
    scale_y_continuous(name = "Discharge (cfs)", sec.axis = sec_axis(trans = ~1*(.-maxRange), name = "Precipitation (in/m)", labels = precip_labels)) # labels are in inches/s
  
  png(paste0('ch2 data transformations/outputdata/timeseries_some/timeseries_', h, '.png'), width=6.5, height=3.5, units="in", pointsize=12, res=1200)
  par(mar=c(5,4,1,1)+0.1, ps=8, cex=1)
  print(hydrograph)
  dev.off()
}
```

# 8.0 Goodness of Fit 
```{r mof_data} 
gof_lm_agg <- gof(results_lm$LMLOGOFIT, results_lm$FLOW, na.rm=TRUE)
gof_lm_inc <- gof(results_lm$LMLOGOFIT_AGG, results_lm$FLOW, na.rm=TRUE)
gof_lm_cagg <- gof(results_lm$LMLOGOFIT_NONC, results_lm$FLOW, na.rm=TRUE)
gof_lm_cinc <- gof(results_lm$LMLOGOFIT_AGG_NONC, results_lm$FLOW, na.rm=TRUE)

gof_glm_agg <- gof(results_glm$LMLOGOFIT, results_glm$FLOW, na.rm=TRUE)
gof_glm_inc <- gof(results_glm$LMLOGOFIT_AGG, results_glm$FLOW, na.rm=TRUE)
gof_glm_cagg <- gof(results_glm$LMLOGOFIT_NONC, results_glm$FLOW, na.rm=TRUE)
gof_glm_cinc <- gof(results_glm$LMLOGOFIT_AGG_NONC, results_glm$FLOW, na.rm=TRUE)

gof_rf_agg <- gof(results_rf$LMLOGOFIT, results_rf$FLOW, na.rm=TRUE)
gof_rf_inc <- gof(results_rf$LMLOGOFIT_AGG, results_rf$FLOW, na.rm=TRUE)
gof_rf_cagg <- gof(results_rf$LMLOGOFIT_NONC, results_rf$FLOW, na.rm=TRUE)
gof_rf_cinc <- gof(results_rf$LMLOGOFIT_AGG_NONC, results_rf$FLOW, na.rm=TRUE)

gof_nn_agg <- gof(results_nn$LMLOGOFIT, results_nn$FLOW, na.rm=TRUE)
gof_nn_inc <- gof(results_nn$LMLOGOFIT_AGG, results_nn$FLOW, na.rm=TRUE)
gof_nn_cagg <- gof(results_nn$LMLOGOFIT_NONC, results_nn$FLOW, na.rm=TRUE)
gof_nn_cinc <- gof(results_nn$LMLOGOFIT_AGG_NONC, results_nn$FLOW, na.rm=TRUE)

gof_lm <- cbind(gof_lm_agg, gof_lm_inc, gof_lm_cagg, gof_lm_cinc)
gof_glm <- cbind(gof_glm_agg, gof_glm_inc, gof_glm_cagg, gof_glm_cinc)
gof_rf <- cbind(gof_rf_agg, gof_rf_inc, gof_rf_cagg, gof_rf_cinc)
gof_nn <- cbind(gof_nn_agg, gof_nn_inc, gof_nn_cagg, gof_nn_cinc)

colnames(gof_lm) <- c("LM_AGG", "LM_INC", "LM_CAGG", "LM_CINC")
colnames(gof_glm) <- c("GLM_AGG", "GLM_INC", "GLM_CAGG", "GLM_CINC")
colnames(gof_rf) <- c("RF_AGG", "RF_INC", "RF_CAGG", "RF_CINC")
colnames(gof_nn) <- c("NN_AGG", "NN_INC", "NN_CAGG", "NN_CINC")

gof_all <- as.data.frame(cbind(gof_lm, gof_glm, gof_rf, gof_nn))

library(Hmisc)
var_labels <- c("LM Agg", "LM Inc", "LM Cumul Agg", "LM Cumul Inc", "GLM Agg", "GLM Inc", "GLM Cumul Agg", "GLM Cumul Inc", "RF Agg", "RF Inc", "RF Cumul Agg", "RF Cumul Inc", "NN Agg", "NN Inc", "NN Cumul Agg", "NN Cumul Inc") 
names(var_labels) <- colnames(gof_all)
Hmisc::label(gof_all) <- lapply(names(var_labels), function(x) Hmisc::label(gof_all[,x]) = var_labels[x])

# for latex documents, put this in appendix
library(xtable)
xtable(data.frame(gof_all))
```

```{r mof_bybasin}
# for plotting purposes, just do this for lm inc because it was the best model! did it for lm agg too, for purposes of comparison later. 

# for lm
gof_lm_agg <- gof_lm_inc <- gof_lm_cagg <- gof_lm_cinc <- list()
for (r in 1:(length(unique(results_lm$CDEC_ID)))){ 
  # plot time series by basin
  h <- unique(results_lm$CDEC_ID)[r]
  resultsdf_sub <- results_lm[results_lm$CDEC_ID==h,]
  gof_lm_agg[[r]] <- gof(resultsdf_sub$LMLOGOFIT, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_lm_inc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_lm_cagg[[r]] <- gof(resultsdf_sub$LMLOGOFIT_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_lm_cinc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
}

names_tbd <- rownames(gof_lm_agg[[1]])
gof_lm_agg_by_basins <- data.frame(matrix(unlist(gof_lm_agg), nrow=length(gof_lm_agg[[1]]), byrow=FALSE))
rownames(gof_lm_agg_by_basins) <- names_tbd
colnames(gof_lm_agg_by_basins) <- unique(results_lm$CDEC_ID)
remove(names_tbd)

names_tbd <- rownames(gof_lm_inc[[1]])
gof_lm_inc_by_basins <- data.frame(matrix(unlist(gof_lm_inc), nrow=length(gof_lm_inc[[1]]), byrow=FALSE))
rownames(gof_lm_inc_by_basins) <- names_tbd
colnames(gof_lm_inc_by_basins) <- unique(results_lm$CDEC_ID)
remove(names_tbd)

# for glm
gof_glm_agg <- gof_glm_inc <- gof_glm_cagg <- gof_glm_cinc <- list()
for (r in 1:(length(unique(results_glm$CDEC_ID)))){
  # plot time series by basin
  h <- unique(results_glm$CDEC_ID)[r]
  resultsdf_sub <- results_glm[results_glm$CDEC_ID==h,]
  gof_glm_agg[[r]] <- gof(resultsdf_sub$LMLOGOFIT, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_glm_inc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_glm_cagg[[r]] <- gof(resultsdf_sub$LMLOGOFIT_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_glm_cinc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
}

names_tbd <- rownames(gof_glm_agg[[1]])
gof_glm_agg_by_basins <- data.frame(matrix(unlist(gof_glm_agg), nrow=length(gof_glm_agg[[1]]), byrow=FALSE))
rownames(gof_glm_agg_by_basins) <- names_tbd
colnames(gof_glm_agg_by_basins) <- unique(results_glm$CDEC_ID)
remove(names_tbd)

names_tbd <- rownames(gof_glm_inc[[1]])
gof_glm_inc_by_basins <- data.frame(matrix(unlist(gof_glm_inc), nrow=length(gof_glm_inc[[1]]), byrow=FALSE))
rownames(gof_glm_inc_by_basins) <- names_tbd
colnames(gof_glm_inc_by_basins) <- unique(results_glm$CDEC_ID)
remove(names_tbd)

# for rf
gof_rf_agg <- gof_rf_inc <- gof_rf_cagg <- gof_rf_cinc <- list()
for (r in 1:(length(unique(results_rf$CDEC_ID)))){ 
  # plot time series by basin
  h <- unique(results_rf$CDEC_ID)[r]
  resultsdf_sub <- results_rf[results_rf$CDEC_ID==h,]
  gof_rf_agg[[r]] <- gof(resultsdf_sub$LMLOGOFIT, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_rf_inc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_rf_cagg[[r]] <- gof(resultsdf_sub$LMLOGOFIT_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_rf_cinc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
}

names_tbd <- rownames(gof_rf_agg[[1]])
gof_rf_agg_by_basins <- data.frame(matrix(unlist(gof_rf_agg), nrow=length(gof_rf_agg[[1]]), byrow=FALSE))
rownames(gof_rf_agg_by_basins) <- names_tbd
colnames(gof_rf_agg_by_basins) <- unique(results_rf$CDEC_ID)
remove(names_tbd)

names_tbd <- rownames(gof_rf_inc[[1]])
gof_rf_inc_by_basins <- data.frame(matrix(unlist(gof_rf_inc), nrow=length(gof_rf_inc[[1]]), byrow=FALSE))
rownames(gof_rf_inc_by_basins) <- names_tbd
colnames(gof_rf_inc_by_basins) <- unique(results_rf$CDEC_ID)
remove(names_tbd)

# for nn
gof_nn_agg <- gof_nn_inc <- gof_nn_cagg <- gof_nn_cinc <- list()
for (r in 1:(length(unique(results_nn$CDEC_ID)))){ 
  # plot time series by basin
  h <- unique(results_nn$CDEC_ID)[r]
  resultsdf_sub <- results_nn[results_nn$CDEC_ID==h,]
  gof_nn_agg[[r]] <- gof(resultsdf_sub$LMLOGOFIT, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_nn_inc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_nn_cagg[[r]] <- gof(resultsdf_sub$LMLOGOFIT_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
  gof_nn_cinc[[r]] <- gof(resultsdf_sub$LMLOGOFIT_AGG_NONC, resultsdf_sub$FLOW, na.rm=TRUE)
}

names_tbd <- rownames(gof_nn_agg[[1]])
gof_nn_agg_by_basins <- data.frame(matrix(unlist(gof_nn_agg), nrow=length(gof_nn_agg[[1]]), byrow=FALSE))
rownames(gof_nn_agg_by_basins) <- names_tbd
colnames(gof_nn_agg_by_basins) <- unique(results_nn$CDEC_ID)
remove(names_tbd)

names_tbd <- rownames(gof_nn_inc[[1]])
gof_nn_inc_by_basins <- data.frame(matrix(unlist(gof_nn_inc), nrow=length(gof_nn_inc[[1]]), byrow=FALSE))
rownames(gof_nn_inc_by_basins) <- names_tbd
colnames(gof_nn_inc_by_basins) <- unique(results_nn$CDEC_ID)
remove(names_tbd)
```

```{r mof_comp_plots}
# plot this table especially for the important errors: RMSE, bR2, NSE, KGE, VE 
# goftablet <- data.frame(t(gof_all))

# remove the cumulative ones, cause they are so bad
goftablet <- data.frame(t(gof_all[, c("LM_AGG", "LM_INC", "GLM_AGG", "GLM_INC", "RF_AGG", "RF_INC", "NN_AGG", "NN_INC")]))
goftablet$MODELTYPE <- sub("\\_.*", "", rownames(goftablet))  
goftablet$DT <- sub(".*_", "", rownames(goftablet))
goftablet$MODELTYPE <- factor(goftablet$MODELTYPE, levels=c("LM", "GLM", "RF", "NN"))
goftablet$DT <- factor(goftablet$DT, levels=c("AGG", "INC"))
goftablet$COLORS <- c(cbpblack[2], cbpblack[3], cbpblack[5], cbpblack[6])[goftablet$MODELTYPE]

DT.labs <- c("Aggregate (AGG)", "Incremental (INC)")
names(DT.labs) <- c("AGG", "INC")
MODELTYPE.labs <- c("Linear Model (LM)", "Generalized Linear Model (GLM)", "Random Forest (RF)", "Neural Network (NN)")
names(MODELTYPE.labs) <- c("LM", "GLM", "RF", "NN")

MOF_order <- c(rep(TRUE,7), rep(FALSE, 13))
MOF_lab <- c("Mean Error (AF)", "Mean Absolute Error (AF)", "Mean Squared Error (AF^2)", "Root Mean Squared Error (AF)", "Normalized Root Mean Squared Error (AF^2)", "Percent Bias (-)", "RMSE to Standard Deviation of Observations Ratio (-)", "Ratio of Standard Deviations (-)", "Nash-Sutcliffe Efficiency (-)", "Modified Nash-Sutcliffe Efficiency (-)", "Relative Nash-Sutcliffe Efficiency (-)", "Index of Agreement (-)", "Modified Index of Agreement (-)", "Relative Index of Agreement (-)", "Persistence Index (-)", "Pearson Correlation coefficient (-)", "Coefficient of Determination (-)", "Bias-Corrected Coefficient of Determination (-)", "Kling-Gupta Efficiency (-)", "Volumetric Efficiency (AF)")

# for (i in 1:20){
#   MOF <- colnames(goftablet)[i]
#   MOF_o <- MOF_order[i] # not working right now
#   MOF_l <- MOF_lab[i]
#   png(paste0('ch2 data transformations/outputdata/rplot26_gof_', MOF, '.png'), width=6.5, height=2, units="in", pointsize=8, res=1200)
#   plottoprint <- ggplot(goftablet)+
#     geom_point(aes_string(x = goftablet[,MOF], 
#                           y=reorder(rownames(goftablet), goftablet[,MOF]), 
#                           color=goftablet[, "MODELTYPE"], 
#                           shape=goftablet[, "DT"]))+
#     #scale_y_discrete(labels=var_labels[match(rownames(goftablet), names(var_labels))])+
#     theme_bw(base_size = 8) +
#     ylab("") +
#     xlab(MOF_l) +
#     xlim(min(goftablet[,MOF]), 1.05*max(goftablet[,MOF]))+
#     theme(legend.position = "none", axis.text.y = element_text(colour=goftablet[order(goftablet[ , MOF]),]$COLOR)) +
#     #legend.title = element_blank(), legend.text=element_text(size=10), text=element_text(size=10), legend.position = "right", legend.box = "vertical")+
#     scale_colour_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[5], cbpblack[6])) + 
#     scale_shape_manual(values=c(8, 16))+
#     guides(colour = guide_legend(ncol=1), shape = guide_legend(ncol=1))+
#     geom_text(aes(x = goftablet[,MOF], y = reorder(rownames(goftablet), goftablet[,MOF]), label=formatC(goftablet[ , MOF], format = "e", digits = 2)),hjust=-0.1, vjust=0, size = 2.5)
#   print(plottoprint)
# dev.off()
# }

# just for bR2 nd NSE
plottoprint <- ggplot(goftablet)+
  geom_point(aes_string(x = goftablet[,"bR2"], 
                        y=reorder(rownames(goftablet), goftablet[,"bR2"]), 
                        color=goftablet[, "MODELTYPE"], 
                        shape=goftablet[, "DT"]))+
  #scale_y_discrete(labels=var_labels[match(rownames(goftablet), names(var_labels))])+
  theme_bw(base_size = 8) +
  ylab("") +
  xlab("Bias Corrected Coefficient of Determination (-)") +
  xlim(0.2, 1)+
  theme(legend.position = "none", axis.text.y = element_text(colour=goftablet[order(goftablet[ , "bR2"]),]$COLOR)) +
  annotate("rect", xmin = 0.2, xmax = 0.5, ymin = 1, ymax = 8, fill= "grey55", alpha = 0.5) +
  annotate("rect", xmin = 0.5, xmax = 0.65, ymin = 1, ymax = 8, fill= "grey70", alpha = 0.5) +
  annotate("rect", xmin = 0.65, xmax = 0.75, ymin = 1, ymax = 8, fill= "grey85", alpha = 0.5) +
  annotate("rect", xmin = 0.75, xmax = 1.0, ymin = 1, ymax = 8, fill= "grey95", alpha = 0.5) +
  geom_text(aes(x= 0.35, y=8, label="Unsatisfactory"), size=3, hjust="center", fontface=3)+
  geom_text(aes(x= 0.575, y=8, label="Satisfactory"), size=3, hjust="center", fontface=3)+
  geom_text(aes(x= 0.7, y=8, label="Good"), size=3, hjust="center", fontface=3)+
  geom_text(aes(x= 0.875, y=1, label="Very Good"), size=3, hjust="center", fontface=3)+
  scale_colour_manual(aesthetics = c("colour"), values=c(cbpblack[2], cbpblack[3], cbpblack[5], cbpblack[6])) +
  scale_shape_manual(values=c(8, 16))+
  guides(colour = guide_legend(ncol=1), shape = guide_legend(ncol=1))+
  geom_text(aes(x = goftablet[,"bR2"], y = reorder(rownames(goftablet), goftablet[, "bR2"]), label=goftablet[, "bR2"]), nudge_x = 0.03, size=3) 

png(paste0('ch2 data transformations/outputdata/rplot26_gof_bR2.png'), width=6.5, height=2, units="in", pointsize=8, res=1200)
  print(plottoprint)
dev.off()

plottoprint <- ggplot(goftablet)+
  geom_point(aes_string(x = goftablet[,"NSE"], 
                        y=reorder(rownames(goftablet), goftablet[,"NSE"]), 
                        color=goftablet[, "MODELTYPE"], 
                        shape=goftablet[, "DT"]))+
  #scale_y_discrete(labels=var_labels[match(rownames(goftablet), names(var_labels))])+
  theme_bw(base_size = 8) +
  ylab("") +
  xlab("Nash-Sutcliffe Efficiency Factor (-)") +
  xlim(0.2, 1)+
  theme(legend.position = "none", axis.text.y = element_text(colour=goftablet[order(goftablet[ , "NSE"]),]$COLOR)) +
  annotate("rect", xmin = 0.2, xmax = 0.5, ymin = 1, ymax = 8, fill= "grey55", alpha = 0.5) +
  annotate("rect", xmin = 0.5, xmax = 0.65, ymin = 1, ymax = 8, fill= "grey70", alpha = 0.5) +
  annotate("rect", xmin = 0.65, xmax = 0.75, ymin = 1, ymax = 8, fill= "grey85", alpha = 0.5) +
  annotate("rect", xmin = 0.75, xmax = 1.0, ymin = 1, ymax = 8, fill= "grey95", alpha = 0.5) +
  geom_text(aes(x= 0.35, y=8, label="Unsatisfactory"), size=3, hjust="center", fontface=3)+
  geom_text(aes(x= 0.575, y=8, label="Satisfactory"), size=3, hjust="center", fontface=3)+
  geom_text(aes(x= 0.7, y=8, label="Good"), size=3, hjust="center", fontface=3)+
  geom_text(aes(x= 0.875, y=8, label="Very Good"), size=3, hjust="center", fontface=3)+
  scale_colour_manual(aesthetics = c("colour"), values=c(cbpblack[2], cbpblack[3], cbpblack[5], cbpblack[6])) +
  scale_shape_manual(values=c(8, 16))+
  guides(colour = guide_legend(ncol=1), shape = guide_legend(ncol=1))+
  geom_text(aes(x = goftablet[,"NSE"], y = reorder(rownames(goftablet), goftablet[, "NSE"]), label=goftablet[, "NSE"]), nudge_x = 0.03, size=3) 

png(paste0('ch2 data transformations/outputdata/rplot26_gof_NSE.png'), width=6.5, height=2, units="in", pointsize=8, res=1200)
  print(plottoprint)
dev.off()
```

```{r obsvpred_plots}
library(reshape2)
library(ggplot2)
master_dt <- results_all[,c("HIERARCHY", "FLOW", "LMLOGOFIT", "LMLOGOFIT_AGG", "GLMLOGOFIT", "GLMLOGOFIT_AGG", "RFLOGOFIT", "RFLOGOFIT_AGG", "NNLOGOFIT", "NNLOGOFIT_AGG")]
master_dt$HIERARCHY <- factor(master_dt$HIERARCHY, levels=c("1", "2", "3", "4", "5"))

master_dt_melted <- melt(master_dt, id.vars=c("HIERARCHY", "FLOW"), measure.vars=c("LMLOGOFIT", "LMLOGOFIT_AGG", "GLMLOGOFIT", "GLMLOGOFIT_AGG", "RFLOGOFIT", "RFLOGOFIT_AGG", "NNLOGOFIT", "NNLOGOFIT_AGG"), variable.name="MODELTYPEDT", value.name="PRED")
master_dt_melted$MODELTYPE <- sub("LOGO.*", "", master_dt_melted$MODELTYPEDT) 
master_dt_melted$MODELTYPE <- factor(master_dt_melted$MODELTYPE, levels=c("LM", "GLM", "RF", "NN"))
master_dt_melted$DT <- ifelse(sub(".*FIT", "", master_dt_melted$MODELTYPEDT)=="", "AGG", "INC")
master_dt_melted$DT <- factor(master_dt_melted$DT, levels=c("AGG", "INC"))

DT.labs <- c("Aggregate (AGG)", "Incremental (INC)")
names(DT.labs) <- c("AGG", "INC")
MODELTYPE.labs <- c("Linear Model (LM)", "Generalized Linear Model (GLM)", "Random Forest (RF)", "Neural Network (NN)")
names(MODELTYPE.labs) <- c("LM", "GLM", "RF", "NN")

library(ggpmisc)
png('ch2 data transformations/outputdata/rplot27_obsvspred_all.png', width=6.5, height=8, units="in", pointsize=8, res=1200)
  plottoprint <- ggplot(master_dt_melted, aes(x=FLOW, y=PRED)) +
    geom_point(aes(group=HIERARCHY, colour=HIERARCHY, shape=HIERARCHY)) +
    geom_smooth(method="lm", se=FALSE, color="black")+
    stat_poly_eq(formula = y ~ x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
    geom_abline(slope=1, intercept=0, color="black", linetype=3)+
    facet_grid(MODELTYPE~DT, labeller=labeller(DT=DT.labs, MODELTYPE=MODELTYPE.labs))+
    scale_discrete_manual(aesthetics="color", values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
    scale_discrete_manual(aesthetics= "shape", values=c(1, 16, 2, 0, 15), name="Hierarchy") +
    labs(x ="Observed Unimpaired Flow (AF/m)", y = "Predicted Unimpaired Flow (AF/m)", color = "")+
    theme(legend.text=element_text(size=10), text=element_text(size=10))+
    theme_bw(base_size = 8)
  print(plottoprint)
dev.off()
```

```{r error_density_plot_for_paper}
masterdt_lm <- results_all[,c("FLOW", "LMLOGOFIT", "LMLOGOFIT_AGG")]
masterdt_glm <- results_all[,c("FLOW", "GLMLOGOFIT", "GLMLOGOFIT_AGG")]
masterdt_rf <- results_all[,c("FLOW", "RFLOGOFIT", "RFLOGOFIT_AGG")]
masterdt_nn <- results_all[,c("FLOW", "NNLOGOFIT", "NNLOGOFIT_AGG")]

masterdt_lm$MODELTYPE <- "LM"
masterdt_glm$MODELTYPE <- "GLM"
masterdt_rf$MODELTYPE <- "RF"
masterdt_nn$MODELTYPE <- "NN"

colnames(masterdt_lm)[1:3] <- colnames(masterdt_glm)[1:3] <- colnames(masterdt_rf)[1:3] <- colnames(masterdt_nn)[1:3] <- c("OBS", "AGG", "INC")

master_dt <- rbind(masterdt_lm, masterdt_glm, masterdt_rf, masterdt_nn)
master_dt_melted <- melt(master_dt, measure.vars= c("AGG", "INC"), variable.name="DATASTYLE", value.name="FLOW")
master_dt_melted$MODELTYPE <- factor(master_dt_melted$MODELTYPE, levels=c("LM", "GLM", "RF", "NN"))
master_dt_melted$DATASTYLE <- factor(master_dt_melted$DATASTYLE, levels=c("AGG", "INC"))

MODELTYPE.labs <- c("Linear Model (LM)", "Generalized Linear Model (GLM)", "Random Forest (RF)", "Neural Network (NN)")
names(MODELTYPE.labs) <- c("LM", "GLM", "RF", "NN")

png('ch2 data transformations/outputdata/rplot216_density_all.png', width=3.25*2, height=2.85*2, units="in", pointsize=8, res=1200)
  plottoprint <- ggplot(master_dt_melted) +
    geom_density(aes(x=FLOW, group=DATASTYLE, colour=DATASTYLE, linetype=DATASTYLE), position=position_dodge(width=0.2)) +
    facet_wrap(~MODELTYPE, labeller=labeller(MODELTYPE=MODELTYPE.labs))+
    scale_color_manual(values=c(cbpblack[7], cbpblack[8]), name="Pred", breaks = c("AGG", "INC"), labels=c("AGG", "INC"))+ 
    scale_linetype_manual(values=c("dashed", "dotted"), labels=c("AGG", "INC"), name="Pred", breaks=c("AGG", "INC"))+
    geom_density(aes(x=OBS, fill=""), alpha=0.2) +
    scale_discrete_manual(aesthetics = "fill", values=cbpblack[1], name="Obs")+
    guides(fill = guide_legend(override.aes = list(alpha = 0.2)))+
    scale_x_continuous(trans="log10")+
    labs(x ="Unimpaired Flow (AF/m)", y = "Density or Frequency of Occurance (%)", color = "")+
    annotation_logticks(sides="b")+
    theme(legend.text=element_text(size=10), text=element_text(size=10))+
    theme_bw(base_size = 8)
  print(plottoprint)
dev.off()
```

```{r error_mapplots}
# modelform can be: "lm", "glm", "rf", "nn"
# datatype can be: "agg", "cagg", "inc", "cinc"
library(RColorBrewer)
library(lattice)
library(grid)

rmsemap <- function(gof_results, datatype, modelform){
  basinsc <- basins_points
  results <- data.frame(t(gof_results))
  results$CDEC_ID <- rownames(results)
  basinsc <- merge(basinsc, results, by="CDEC_ID", all=TRUE)
  counties <- list(first=TRUE, "sp.polygons", cacounties, fill="gray88", col="white")
  
  png(paste0('ch2 data transformations/outputdata/rplot28_rmsemap_', modelform, "_", datatype , '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  par(mar=c(0,0,0,0)+0.1, cex=1)
  mycolors <- colorRampPalette(c(cbpblack[2],cbpblack[4],cbpblack[6]))
  tbdspplot <- spplot(basinsc["RMSE"], cex=0.8, sp.layout=counties, col.regions = mycolors(100), 
                      colorkey = list(
                        right = list( # see ?levelplot in package trellis, argument colorkey:
                          fun = draw.colorkey, 
                          args = list(
                            key = list(
                              at = seq(0, 1, 1/100), # colour breaks
                              col = mycolors(100), # colours
                              labels = list(
                              at = seq(0, 1, 20/100),
                              labels =prettyNum(round(seq(min(basinsc$RMSE, na.rm=TRUE), 
max(basinsc$RMSE, na.rm=TRUE), 1e5), 0), big.mark = ",") 
                            )
                          )
                        )
                      )
                    )
                  )
  print(tbdspplot)
  grid.text("RMSE(AF)", 0.57, 0.88)
  dev.off()
}
rmsemap(gof_rf_inc_by_basins, "inc", "rf")
rmsemap(gof_rf_agg_by_basins, "agg", "rf")
rmsemap(gof_glm_inc_by_basins, "inc", "glm")
rmsemap(gof_glm_agg_by_basins, "agg", "glm")
rmsemap(gof_nn_inc_by_basins, "inc", "nn")
rmsemap(gof_nn_agg_by_basins, "agg", "nn")

br2map <- function(gof_results, datatype, modelform){  
  basinsc <- basins_points
  results <- data.frame(t(gof_results))
  results$CDEC_ID <- rownames(results)
  basinsc <- merge(basinsc, results, by="CDEC_ID", all=TRUE)
  counties <- list(first=TRUE, "sp.polygons", cacounties, fill="gray88", col="white")

  png(paste0('ch2 data transformations/outputdata/rplot28_br2map_', modelform, "_", datatype , '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  par(mar=c(0,0,0,0)+0.1, cex=1)
  mycolors <- colorRampPalette(c(cbpblack[2],cbpblack[4],cbpblack[6]))
  tbdspplot <- spplot(basinsc["bR2"], cex=0.8, sp.layout=counties, col.regions = mycolors(100), colorkey = list(right = list( # see ?levelplot in package trellis, argument colorkey:
                      fun = draw.colorkey, 
                      args = list(
                             key = list(
                                  at = seq(0, 1.0, 1/100), # colour breaks
                                  col = mycolors(100), # colours
                                  labels = list(
                                      at = seq(0, 1.0, 0.2),
                                      labels = seq(0, 1.0, 0.2)
                                      )
                                   )
                              )
                      )
          )
  )
  print(tbdspplot)
  grid.text("bR2(-)", 0.65, 0.88)
  dev.off()
}
br2map(gof_rf_inc_by_basins, "inc", "rf")
br2map(gof_rf_agg_by_basins, "agg", "rf")
br2map(gof_glm_inc_by_basins, "inc", "glm")
br2map(gof_glm_agg_by_basins, "agg", "glm")
br2map(gof_nn_inc_by_basins, "inc", "nn")
br2map(gof_nn_agg_by_basins, "agg", "nn")

nsemap <- function(gof_results, datatype, modelform){
  basinsc <- basins_points
  results <- data.frame(t(gof_results))
  results$CDEC_ID <- rownames(results)
  basinsc <- merge(basinsc, results, by="CDEC_ID", all=TRUE)
  counties <- list(first=TRUE, "sp.polygons", cacounties, fill="gray88", col="white")

  png(paste0('ch2 data transformations/outputdata/rplot28_nsemap_', modelform, "_", datatype , '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  par(mar=c(0,0,0,0)+0.1, cex=1)
  # breaksnse <- c(-6.2e3,-50,-10,seq(0,1,0.2))
  # basinsc@data$NSECUT <- cut(basinsc$NSE, breaks=breaksnse)
  mycolors <- colorRampPalette(c(cbpblack[2],cbpblack[4],cbpblack[6]))
  tbdspplot <- spplot(basinsc["NSE"], cex=0.8, sp.layout=counties, col.regions = mycolors(100), colorkey = list(right = list( # see ?levelplot in package trellis, argument colorkey:
                  fun = draw.colorkey,
                  args = list(
                      key = list(
                                  at = seq(0,1, 1/100), # colour breaks
                                  col = mycolors(100), # colours
                                  labels = list(
                                      at = seq(0, 1, 1/7),
                                      labels = c(round(min(gof_results[9, ]), 0),-10, seq(0,1,0.2))
                                      )
                                   )
                              )
                     )
          )
)
  print(tbdspplot)
  grid.text("NSE(-)", 0.60, 0.88)
  dev.off()
}
nsemap(gof_rf_inc_by_basins, "inc", "rf")
nsemap(gof_rf_agg_by_basins, "agg", "rf")
nsemap(gof_glm_inc_by_basins, "inc", "glm")
nsemap(gof_glm_agg_by_basins, "agg", "glm")
nsemap(gof_nn_inc_by_basins, "inc", "nn")
nsemap(gof_nn_agg_by_basins, "agg", "nn")

kgemap <- function(gof_results, datatype, modelform){
  basinsc <- basins_points
  results <- data.frame(t(gof_results))
  results$CDEC_ID <- rownames(results)
  basinsc <- merge(basinsc, results, by="CDEC_ID", all=TRUE)
  counties <- list(first=TRUE, "sp.polygons", cacounties, fill="gray88", col="white")

  png(paste0('ch2 data transformations/outputdata/rplot28_kgemap_', modelform, "_", datatype , '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  par(mar=c(0,0,0,0)+0.1, cex=1)
  mycolors <- colorRampPalette(c(cbpblack[2],cbpblack[4],cbpblack[6]))
  tbdspplot <- spplot(basinsc["KGE"], cex=0.8, sp.layout=counties, col.regions = mycolors(100), colorkey = list(right = list( # see ?levelplot in package trellis, argument colorkey:
                      fun = draw.colorkey,
                      args = list(
                             key = list(
                                  at = seq(0, 1, 1/100), # colour breaks
                                  col = mycolors(100), # colours
                                  labels = list(
                                      at = seq(0, 1, 1/7),
                                      labels = round(c(seq(min(gof_results[19,]), max(gof_results[19,]), 20), 0), 0)
                                      )
                                   )
                              )
                      )
          )
  )
  print(tbdspplot)
  grid.text("KGE(-)", 0.65, 0.88)
  dev.off()
}
kgemap(gof_rf_inc_by_basins, "inc", "rf")
kgemap(gof_rf_agg_by_basins, "agg", "rf")
kgemap(gof_glm_inc_by_basins, "inc", "glm")
kgemap(gof_glm_agg_by_basins, "agg", "glm")
kgemap(gof_nn_inc_by_basins, "inc", "nn")
kgemap(gof_nn_agg_by_basins, "agg", "nn")

vemap <- function(gof_results, datatype, modelform){
  basinsc <- basins_points
  results <- data.frame(t(gof_results))
  results$CDEC_ID <- rownames(results)
  basinsc <- merge(basinsc, results, by="CDEC_ID", all=TRUE)
  counties <- list(first=TRUE, "sp.polygons", cacounties, fill="gray88", col="white")

  png(paste0('ch2 data transformations/outputdata/rplot28_vemap_', modelform, "_", datatype , '.png'), width=3.25, height=3, units="in", pointsize=8, res=1200)
  par(mar=c(0,0,0,0)+0.1, cex=1)
  mycolors <- colorRampPalette(c(cbpblack[2],cbpblack[4],cbpblack[6]))
  tbdspplot <- spplot(basinsc["VE"], cex=0.8, sp.layout=counties, col.regions = mycolors(100), colorkey = list(right = list( # see ?levelplot in package trellis, argument colorkey:
                      fun = draw.colorkey,
                      args = list(
                             key = list(
                                  at = seq(0, 1, 1/100), # colour breaks
                                  col = mycolors(100), # colours
                                  labels = list(
                                      at = seq(0, 1, 1/6),
                                      labels = round(c(seq(min(gof_results[20,]), max(gof_results[20,]), 25), 1), 0)
                                      )
                                   )
                              )
                      )
          )
  )
  print(tbdspplot)
  grid.text("VE(AF)", 0.63, 0.88)
  dev.off()
}
vemap(gof_rf_inc_by_basins, "inc", "rf")
vemap(gof_rf_agg_by_basins, "agg", "rf")
vemap(gof_glm_inc_by_basins, "inc", "glm")
vemap(gof_glm_agg_by_basins, "agg", "glm")
vemap(gof_nn_inc_by_basins, "inc", "nn")
vemap(gof_nn_agg_by_basins, "agg", "nn")
```

```{r spatial_hierarchy_plot}
basinsc <- basins_points
basinsc$HIERARCHY <- (basinsc$STATIONS_ABOVE1!="none") + (basinsc$STATIONS_ABOVE2!="none") +  (basinsc$STATIONS_ABOVE3!="none") + (basinsc$STATIONS_ABOVE4!="none") + 1
counties <- list(first=TRUE, "sp.polygons", cacounties, fill="gray88", col="white")

png('ch2 data transformations/outputdata/rplot210_hierarchies.png', width=3.25, height=3, units="in", pointsize=8, res=1200)
  par(mar=c(0,0,0,0)+0.1, cex=1)
  spplot(basinsc["HIERARCHY"], cex=0.8, sp.layout=counties, col.regions = cbpblack[2:6],
         colorkey = list(
           right = list( # see ?levelplot in package trellis, argument colorkey:
             fun = draw.colorkey,
             args = list(
               key = list(
                 at = seq(0, 5, 1), # colour breaks
                 col = cbpblack[2:6], # colours
                 labels = list(
                   at = seq(0.5, 4.5, 1),
                   labels = seq(1, 5, 1)
                   )
                 )
               )
             )
           )
         )
  grid.text("Hierarchy", 0.63, 0.88)
dev.off()
```

```{r error_hierarchy_plots}
# plot errors by location in the hierarchy
# fitofinterest can be anything returned by the gof function

gofdotchart <- function(gof_results_agg, gof_results_inc, fitofinterest){
  tgof_results_agg <- data.frame(t(gof_results_agg))
  tgof_results_agg$CDEC_ID <- rownames(tgof_results_agg)
  basinsc <- basins_points@data
  basinsc <- merge(basinsc, tgof_results_agg, by="CDEC_ID", all=TRUE)
  basinsc$HIERARCHY <- (basinsc$STATIONS_ABOVE1!="none") + (basinsc$STATIONS_ABOVE2!="none") + (basinsc$STATIONS_ABOVE3!="none") + (basinsc$STATIONS_ABOVE4!="none") + 1
  basinsc$DT <- "AGG"
  
  tgof_results_inc <- data.frame(t(gof_results_inc))
  tgof_results_inc$CDEC_ID <- rownames(tgof_results_inc)
  basinsc2 <- basins_points@data
  basinsc2 <- merge(basinsc2, tgof_results_inc, by="CDEC_ID", all=TRUE)
  basinsc2$HIERARCHY <- (basinsc2$STATIONS_ABOVE1!="none") + (basinsc2$STATIONS_ABOVE2!="none") + (basinsc2$STATIONS_ABOVE3!="none") + (basinsc2$STATIONS_ABOVE4!="none") + 1
  basinsc2$DT <- "INC"

  basinscr <- melt(basinsc, id.vars=c("CDEC_ID", "DT", "HIERARCHY"), variable.name = "GOF", value.name="VALUE", measure.vars = fitofinterest)
  basinsc2r <- melt(basinsc2, id.vars=c("CDEC_ID", "DT", "HIERARCHY"), variable.name = "GOF", value.name="VALUE", measure.vars = fitofinterest)
  
  # order based on INC values decreasing
  orderrownums <- as.numeric(row.names(basinsc2r[order(basinsc2r$VALUE, decreasing=TRUE), ]))
  basinscr <- basinscr[orderrownums, ]
  basinsc2r <- basinsc2r[orderrownums, ]
  
  # bind aacross the different transformation styles
  basinscm <- rbind(basinscr, basinsc2r)
  basinscm$DT <- factor(basinscm$DT, levels = c("AGG", "INC"))
  basinscm$CDEC_ID <- factor(basinscm$CDEC_ID, levels=basinscm$CDEC_ID[1:67])
  
  if(fitofinterest=="ME"){
    fitofinterestlabel <- "Mean Error (AF)"
    maxxlim <- max(1.1*max(basinsm[, "ME.x"], na.rm=TRUE), 1.1*max(basinsm[, "ME.y"], na.rm=TRUE))
  } else if(fitofinterest=="MAE"){
    fitofinterestlabel <- "Mean Absolute Error (AF)"
    maxxlim <- max(1.1*max(basinsm[, "MAE.x"], na.rm=TRUE), 1.1*max(basinsm[, "MAE.y"], na.rm=TRUE))
  } else if(fitofinterest=="MSE"){
    fitofinterestlabel <- "Mean Squared Error (AF^2)"
    maxxlim <- max(1.1*max(basinsm[, "MSE.x"], na.rm=TRUE), 1.1*max(basinsm[, "MSE.y"], na.rm=TRUE))
  } else if(fitofinterest=="RMSE"){
    fitofinterestlabel <- "Root Mean Squared Error (AF)"
    maxxlim <- max(1.1*max(basinsm[, "RMSE.x"], na.rm=TRUE), 1.1*max(basinsm[, "RMSE.y"], na.rm=TRUE))
  } else if(fitofinterest=="NRMSE.."){
    fitofinterestlabel <- "Normalized Root Mean Squared Error (AF^2)"
    maxxlim <- max(1.1*max(basinsm[, "NRMSE...x"], na.rm=TRUE), 1.1*max(basinsm[, "NRMSE...y"], na.rm=TRUE))
  } else if(fitofinterest=="PBIAS.."){
    fitofinterestlabel <- "Percent Bias (-)"
    maxxlim <- max(1.4*max(basinsm[, "PBIAS...x"], na.rm=TRUE), 1.4*max(basinsm[, "PBIAS...y"], na.rm=TRUE))
  } else if(fitofinterest=="RSR"){
    fitofinterestlabel <- "RMSE to Standard Deviation of Observations Ratio (-)"
    maxxlim <- 67
  } else if(fitofinterest=="NSE"){
    fitofinterestlabel <- "Nash-Sutcliffe Efficiency (-)"
    maxxlim <- 10
    # minxlim <- 7*minxlim
  } else if(fitofinterest=="rSD"){
    fitofinterestlabel <- "Ratio of Standard Deviations (-)"
    maxxlim <- max(1.1*max(basinsm[, "rSD.x"], na.rm=TRUE), 1.1*max(basinsm[, "rSD.y"], na.rm=TRUE))
  } else if(fitofinterest=="mNSE"){
    fitofinterestlabel <- "Modified Nash-Sutcliffe Efficiency (-)"
    maxxlim <- 5
  } else if(fitofinterest=="rNSE"){
    fitofinterestlabel <- "Relative Nash-Sutcliffe Efficiency (-)"
    maxxlim <- 5e5
  } else if(fitofinterest=="d"){
    fitofinterestlabel <- "Index of Agreement (-)"
    maxxlim <- max(1.05*max(basinsm[, "d.x"], na.rm=TRUE), 1.05*max(basinsm[, "d.y"], na.rm=TRUE))
  } else if(fitofinterest=="md"){
    fitofinterestlabel <- "Modified Index of Agreement (-)"
    maxxlim <- max(1.1*max(basinsm[, "md.x"], na.rm=TRUE), 1.1*max(basinsm[, "md.y"], na.rm=TRUE))
  } else if(fitofinterest=="rd"){
    fitofinterestlabel <- "Relative Index of Agreement (-)"
    maxxlim <- 100
  } else if(fitofinterest=="cp"){
    fitofinterestlabel <- "Persistence Index (-)"
    maxxlim <- 200
  } else if(fitofinterest=="r"){
    fitofinterestlabel <- "Pearson Correlation coefficient (-)"
    maxxlim <- max(1.1*max(basinsm[, "r.x"], na.rm=TRUE), 1.1*max(basinsm[, "r.y"], na.rm=TRUE))
  } else if(fitofinterest=="R2"){
    fitofinterestlabel <- "Coefficient of Determination (-)"
    maxxlim <- 1.0
  } else if(fitofinterest=="bR2"){
    fitofinterestlabel <- "Bias-Corrected Coefficient of Determination (-)"
    maxxlim <- 1.0
    minxlim <- -0.05
  } else if(fitofinterest=="KGE"){
    fitofinterestlabel <- "Kling-Gupta Efficiency (-)"
    maxxlim <- 10
  } else if(fitofinterest=="VE"){
    fitofinterestlabel <- "Volumetric Efficiency (AF)"
    maxxlim <- 6
  } else{
    print("Input a measure of fit provided by the gof function in HydroGOF package!")
  }
  
  plottoprint <- ggplot(data=basinscm, aes(x=VALUE, y=CDEC_ID)) +
    geom_point(aes(shape=DT, color=DT), size=2)+
    facet_grid(HIERARCHY ~ ., scales = "free", space = "free") +
    scale_shape_manual(name="Type", breaks = c("AGG", "INC"), values=c(8, 16)) + 
    scale_colour_manual(name="Type", aesthetics = c("colour"), values=c(cbpblack[7], cbpblack[8]), breaks = c("AGG", "INC")) +
    labs(x=fitofinterestlabel, y="")+
    theme_bw() +
    theme(legend.position="right", legend.title = element_blank())+
    guides(color = guide_legend(nrow = 2), shape= guide_legend(nrow = 2))

  png(paste0('ch2 data transformations/outputdata/rplot211_', fitofinterest, 'dotchart_comp.png'), width=6.5, height=8, units="in", pointsize=8, res=1200)
    print(plottoprint)
  dev.off()
}

# gofdotchart(gof_lm_agg_by_basins, gof_lm_inc_by_basins, "NSE")
# gofdotchart(gof_lm_agg_by_basins, gof_lm_inc_by_basins, "bR2")
# gofdotchart(gof_glm_agg_by_basins, gof_glm_inc_by_basins, "NSE")
# gofdotchart(gof_glm_agg_by_basins, gof_glm_inc_by_basins, "bR2")
gofdotchart(gof_nn_agg_by_basins, gof_nn_inc_by_basins, "NSE")
gofdotchart(gof_nn_agg_by_basins, gof_nn_inc_by_basins, "bR2")
```

```{r boxplot}
gofboxplot <- function(gof_results_agg, gof_results_inc, fitofinterest){ 
  basinsc <- basins_points
  results <- data.frame(t(gof_results_agg))
  results$CDEC_ID <- rownames(results)
  
  results2 <- data.frame(t(gof_results_inc))
  results2$CDEC_ID <- rownames(results2)
  
  basinsc <- merge(basinsc, results, by="CDEC_ID", all=TRUE) # the .x s are the agg basins, the .y s are the inc
  basinsc <- merge(basinsc, results2, by="CDEC_ID", all=TRUE)
  
  basinsc <- basinsc@data[order(basinsc@data[, paste0(fitofinterest, ".y")], decreasing=TRUE), ]
  basinsc$HIERARCHY <- (basinsc$STATIONS_ABOVE1!="none") + (basinsc$STATIONS_ABOVE2!="none") + (basinsc$STATIONS_ABOVE3!="none") + (basinsc$STATIONS_ABOVE4!="none") + 1
  basinsc$GRPS <- as.factor(basinsc$HIERARCHY)
  basinsc <- basinsc[order(basinsc[, paste0(fitofinterest, ".y")], decreasing=TRUE), ]
  
  if(fitofinterest=="ME"){
    fitofinterestlabel <- "Mean Error (AF)"
    maxxlim <- 1.1*max(basinsc[, "ME"], na.rm=TRUE)
  } else if(fitofinterest=="MAE"){
    fitofinterestlabel <- "Mean Absolute Error (AF)"
    maxxlim <- 1.1*max(basinsc[, "MAE"], na.rm=TRUE)
  } else if(fitofinterest=="MSE"){
    fitofinterestlabel <- "Mean Squared Error (AF^2)"
    maxxlim <- 1.1*max(basinsc[, "MSE"], na.rm=TRUE)
  } else if(fitofinterest=="RMSE"){
    fitofinterestlabel <- "Root Mean Squared Error (AF)"
    maxxlim <- 1.1*max(basinsc[, "RMSE"], na.rm=TRUE)
  } else if(fitofinterest=="NRMSE.."){
    fitofinterestlabel <- "Normalized Root Mean Squared Error (AF^2)"
    maxxlim <- 1.1*max(basinsc[, "NRMSE.."], na.rm=TRUE)
  } else if(fitofinterest=="PBIAS.."){
    fitofinterestlabel <- "Percent Bias (-)"
    maxxlim <- 1.4*max(basinsc[, "PBIAS.."], na.rm=TRUE)
  } else if(fitofinterest=="RSR"){
    fitofinterestlabel <- "RMSE to Standard Deviation of Observations Ratio (-)"
    maxxlim <- 67
  } else if(fitofinterest=="NSE"){
    fitofinterestlabel <- "Nash-Sutcliffe Efficiency (-)"
    maxxlim <- 500
  } else if(fitofinterest=="rSD"){
    fitofinterestlabel <- "Ratio of Standard Deviations (-)"
    maxxlim <- 1.1*max(basinsc[, "rSD"], na.rm=TRUE)
  } else if(fitofinterest=="mNSE"){
    fitofinterestlabel <- "Modified Nash-Sutcliffe Efficiency (-)"
    maxxlim <- 5
  } else if(fitofinterest=="rNSE"){
    fitofinterestlabel <- "Relative Nash-Sutcliffe Efficiency (-)"
    maxxlim <- 5e5
  } else if(fitofinterest=="d"){
    fitofinterestlabel <- "Index of Agreement (-)"
    maxxlim <- 1.05*max(basinsc[, "d"], na.rm=TRUE)
  } else if(fitofinterest=="md"){
    fitofinterestlabel <- "Modified Index of Agreement (-)"
    maxxlim <- 1.1*max(basinsc[, "md"], na.rm=TRUE)
  } else if(fitofinterest=="rd"){
    fitofinterestlabel <- "Relative Index of Agreement (-)"
    maxxlim <- 100
  } else if(fitofinterest=="cp"){
    fitofinterestlabel <- "Persistence Index (-)"
    maxxlim <- 200
  } else if(fitofinterest=="r"){
    fitofinterestlabel <- "Pearson Correlation coefficient (-)"
    maxxlim <- 1.1*max(basinsc[, "r"], na.rm=TRUE)
  } else if(fitofinterest=="R2"){
    fitofinterestlabel <- "Coefficient of Determination (-)"
    maxxlim <- 1.0
  } else if(fitofinterest=="bR2"){
    fitofinterestlabel <- "Bias-Corrected Coefficient of Determination (-)"
    maxxlim <- 1.0
  } else if(fitofinterest=="KGE"){
    fitofinterestlabel <- "Kling-Gupta Efficiency (-)"
    maxxlim <- 10
  } else if(fitofinterest=="VE"){
    fitofinterestlabel <- "Volumetric Efficiency (AF)"
    maxxlim <- 6
  } else{
    print("Input a measure of fit provided by the gof function in HydroGOF package!")
  }
  
  basinsc2 <- melt(basinsc[,c("CDEC_ID", "GRPS", paste0(fitofinterest, ".x"), paste0(fitofinterest, ".y"))], id.vars = c("CDEC_ID", "GRPS"), measure.vars = c(paste0(fitofinterest, ".x"), paste0(fitofinterest, ".y")))
  
  plottoprint <- ggplot(basinsc2, aes(x=GRPS, y=value, fill=variable))+
      geom_boxplot(outlier.shape=NA, alpha=0.3, position=position_dodge(1), show.legend = FALSE) +
      geom_point(position=position_dodge(width=1), aes(group=variable, col=variable, shape=variable), size=2, alpha=0.7) +
      # geom_jitter(shape=16, position=position_jitter(0.1), aes(group=variable)) +
      coord_flip() +
      ylab(fitofinterestlabel) +
      xlab("Basin Hierarchy") +
      scale_x_discrete(limits = rev(levels(basinsc$GRPS))) +
      scale_color_manual(name="Type", labels=c("AGG", "INC"), values=cbpblack[7:8]) +
      scale_fill_discrete(name="Type", labels=c("AGG", "INC")) +
      scale_shape_manual(name="Type", labels=c("AGG", "INC"), values=c(8, 16)) +
      theme_bw() +
      theme(legend.title = element_blank(), legend.text=element_text(size=10), text=element_text(size=10)) 

  png(paste0('ch2 data transformations/outputdata/rplot212_', fitofinterest, "gofboxplot_comp.png"), width=6.5, height=4, units="in", pointsize=8, res=1200)
    par(mar=c(0,0,0,0)+0.1, cex=1)
    print(plottoprint)
  dev.off()
}

# gofboxplot(gof_glm_agg_by_basins, gof_glm_inc_by_basins, "bR2")
gofboxplot(gof_nn_agg_by_basins, gof_nn_inc_by_basins, "bR2")
```

```{r benchmarking_with_BCM}
bcm_results <- read.csv("Inputdata/bcm_validation_results.csv")
bcm_results <- bcm_results[, c("CDEC_ID", "BCM_NSE")]
colnames(bcm_results)[2] <- "BCM"
bcm_results <- na.omit(bcm_results)

nn_bench_results1 <- data.frame(t(gof_nn_agg_by_basins["NSE", ]))
nn_bench_results1$CDEC_ID <- rownames(nn_bench_results1)
colnames(nn_bench_results1)[1] <- "NN AGG"

nn_bench_results2 <- data.frame(t(gof_nn_inc_by_basins["NSE", ]))
nn_bench_results2$CDEC_ID <- rownames(nn_bench_results2)
colnames(nn_bench_results2)[1] <- "NN INC"

nn_bench_results <- merge(bcm_results, nn_bench_results1, by="CDEC_ID")
nn_bench_results <- merge(nn_bench_results, nn_bench_results2, by="CDEC_ID")

nn_bench_results <- melt(nn_bench_results, id.vars = "CDEC_ID", measure.vars = c("BCM", "NN AGG", "NN INC"), variable.name="TYPE", value.name = "NSE")

bench_h <- aggregate(HIERARCHY~CDEC_ID, data=results_all[ ,c("CDEC_ID", "HIERARCHY")], FUN=mean)
nn_bench_results <- merge(nn_bench_results, bench_h, by="CDEC_ID")

plottoprint <- ggplot(data=nn_bench_results, aes(x=NSE, y=CDEC_ID)) +
  geom_point(aes(shape=TYPE, color=TYPE), size=2)+
  facet_grid(HIERARCHY ~ ., scales = "free", space = "free") +
  scale_shape_manual(breaks = c("BCM", "NN AGG", "NN INC"), values=c(17, 8, 16)) + 
  scale_colour_manual(aesthetics = c("colour"), values=c(cbpblack[2], cbpblack[7], cbpblack[8]), breaks = c("BCM", "NN AGG", "NN INC")) +
  labs(x="Nash-Sutcliffe Efficiency Factor (-)", y="")+
  theme_bw()+
  theme(legend.position="right", legend.title = element_blank())+
  guides(color = guide_legend(nrow = 3), shape= guide_legend(nrow = 3))
    
png(paste0('ch2 data transformations/outputdata/rplot215_benchmarking.png'), width=6.5, height=3.2, units="in", pointsize=8, res=1200)
  print(plottoprint)
dev.off()

png(paste0('ch2 data transformations/outputdata/rplot215_benchmarking2.png'), width=6.5, height=3.2, units="in", pointsize=8, res=1200)
  plottoprint <- plottoprint + coord_cartesian(xlim=c(0, 1))
  print(plottoprint)
dev.off()
```

# 9.0 Variable Importance Plots 
```{r vip_prep}
# the models need to be saved, so run the modeling again

# # NN, best model with no preprocessing is NN LOGO AGG
trainingdim <- dim(df_lm_agg[,c(15,18:(ncol(df_lm_agg)-1))])
# nnmodel <- keras_model_sequential() %>%
#   layer_dense(units=64, activation="relu", input_shape=trainingdim[[2]]) %>%
#   layer_dense(units=64, activation="relu") %>%
#   layer_dense(units=1) # number of outputs, here we just want one prediction
# 
# nnmodel %>% # to compile the model, loss functions are defined here
#   compile(optimizer="rmsprop", loss=keras::loss_mean_squared_error, metrics=c("mae"))
# 
# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
#   trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
#   testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
#   trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
#   testsetrv <- as.matrix(testset$FLOW)
#   trainsetrv <- as.matrix(trainset$FLOW)
# 
#   nnmodel %>%
#     fit(trainsetpvs, trainsetrv, epochs=100, batch_size=25, verbose=1, validation_split=0.2)
#   predictions <- nnmodel %>% predict(testsetpvs)
#   predictions <- predictions[ , 1]
# 
#   nnmodel %>% save_model_hdf5(paste0("ch2 data transformations/outputdata/vi_saved_mods/nn_hdf5/nn_", h, ".h5"))
# }

# # LM
# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
#   trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
#   lmmodel <- lm(FLOW~., data=trainset[,c(15,18:ncol(trainset))])
#   saveRDS(lmmodel, paste0("ch2 data transformations/outputdata/vi_saved_mods/lm_rds/lm_", h, ".rds"))
# }

# # GLM
# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
#   trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
#   glmmodel <- glm(FLOW~., data=trainset[,c(15,18:ncol(trainset))], family=tweedie(var.power=1.1, link.power=0), maxit=1000)
#   saveRDS(glmmodel, paste0("ch2 data transformations/outputdata/vi_saved_mods/glm_rds/glm_", h, ".rds"))
# }

# # RF
# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
#   trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
#   rfmodel <- randomForest(FLOW~., data=trainset[,c(15,18:ncol(trainset))], mtry=20)
#   saveRDS(rfmodel, paste0("ch2 data transformations/outputdata/vi_saved_mods/rf_rds/rf_", h, ".rds"))
# }

# read back in
linearmodel <- glinearmodel <- rfmodel <- list()
for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
  linearmodel[[k]] <- readRDS(paste0("ch2 data transformations/outputdata/vi_saved_mods/lm_rds/lm_", h, ".rds"))
  glinearmodel[[k]] <- readRDS(paste0("ch2 data transformations/outputdata/vi_saved_mods/glm_rds/glm_", h, ".rds"))
  rfmodel[[k]] <- readRDS(paste0("ch2 data transformations/outputdata/vi_saved_mods/rf_rds/rf_", h, ".rds"))
}
```

```{r vip} 
library(vip)
library(ggplot2)

## NN
pred_wrapper <- function(object, newdata) {
  predict(object, x = as.matrix(newdata)) %>%
  as.vector()
}

nnvip <- list()
nnmodel <- list()
for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
  h <- unique(df_lm_agg$CDEC_ID)[k]
  testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
  trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
  testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
  trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
  testsetrv <- as.matrix(testset$FLOW)
  trainsetrv <- as.matrix(trainset$FLOW)
  
  modfilename <- paste0("ch2 data transformations/outputdata/vi_saved_mods/nn_hdf5/nn_", h, ".h5")
  nnmodel[[k]] <- load_model_hdf5(modfilename, compile=FALSE)

  nnvip[[k]] <- vip(
    object = nnmodel[[k]],                                     # fitted model
    method = "permute",                                        # permutation-based VI scores
    num_features = trainingdim[2],                             # default only plots top 10 features
    pred_wrapper = pred_wrapper(nnmodel[[k]], testsetpvs),     # user-defined prediction function
    train = as.data.frame(trainsetpvs),                        # training data
    target = trainsetrv,                                       # response values used for training
    metric = "rsquared",                                       # evaluation metric
    # progress = "text"                                        # request a text-based progress bar
    )
}

# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   png(paste0("ch2 data transformations/outputdata/vip/nn/vip_testset_", h, ".png"), width=6.5, height=8, units="in", pointsize=8, res=1200)
#     print(nnvip[[k]], bar=FALSE, shape=19, horizontal=TRUE) + theme_bw()
#   dev.off()
# }

# LM
lmvip <- list()
for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
  h <- unique(df_lm_agg$CDEC_ID)[k]
  testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
  trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
  testsetpvs <- testset[,c(15,18:(ncol(testset)-1))]
  trainsetpvs <- trainset[,c(15,18:(ncol(trainset)-1))]
  testsetrv <- testset$FLOW
  trainsetrv <- trainset$FLOW
  
  lmvip[[k]] <- vip(
    object = linearmodel[[k]],                      # fitted model
    method = "model",                    # model-based VI scores, vip recognizes some model types
    num_features = trainingdim[2],         # default only plots top 10 features
    pred_wrapper = pred_wrapper(linearmodel[[k]], testsetpvs),               # user-defined prediction function
    train = as.data.frame(trainsetpvs),    # training data
    target = trainsetrv,                   # response values used for training
    metric = "r2",                   # evaluation metric
    task = "regression"
    # progress = "text"                    # request a text-based progress bar
    )
}

# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   png(paste0("ch2 data transformations/outputdata/vip/lm/vip_testset_", h, ".png"), width=6.5, height=8, units="in", pointsize=8, res=1200)
#     print(lmvip[[k]], bar=FALSE, shape=19, horizontal=TRUE) + theme_bw()
#   dev.off()
# }

# GLM
glmvip <- list()
for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
  h <- unique(df_lm_agg$CDEC_ID)[k]
  testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
  trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
  testsetpvs <- testset[,c(15,18:(ncol(testset)-1))]
  trainsetpvs <- trainset[,c(15,18:(ncol(trainset)-1))]
  testsetrv <- testset$FLOW
  trainsetrv <- trainset$FLOW
  
  glmvip[[k]] <- vip(
    object = glinearmodel[[k]],                                     # fitted model
    method = "model",                                               # model-based VI scores, vip recognizes some model types
    num_features = trainingdim[2],                                  # default only plots top 10 features
    pred_wrapper = pred_wrapper(glinearmodel[[k]], testsetpvs),     # user-defined prediction function
    train = as.data.frame(trainsetpvs),                             # training data
    target = trainsetrv,                                            # response values used for training
    metric = "r2",                                                  # evaluation metric
    task = "regression"
    # progress = "text"                                             s# request a text-based progress bar
    )
}

# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   png(paste0("ch2 data transformations/outputdata/vip/glm/vip_testset_", h, ".png"), width=6.5, height=8, units="in", pointsize=8, res=1200)
#     print(glmvip[[k]], bar=FALSE, shape=19, horizontal=TRUE) + theme_bw()
#   dev.off()
# }

# RF 
rfvip <- list()
rfmodel <- list()
for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
  h <- unique(df_lm_agg$CDEC_ID)[k]
  testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
  trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
  testsetpvs <- testset[,c(15,18:(ncol(testset)-1))]
  trainsetpvs <- trainset[,c(15,18:(ncol(trainset)-1))]
  testsetrv <- testset$FLOW
  trainsetrv <- trainset$FLOW
  
  modfilename <- paste0("ch2 data transformations/outputdata/vi_saved_mods/rf_rds/rf_", h, ".rds")
  rfmodel[[k]] <- readRDS(modfilename)
  
  rfvip[[k]] <- vip(
    object = rfmodel[[k]],                                               # fitted model
    method = "model",                                                    # model-based VI scores
    num_features = trainingdim[2],                                       # default only plots top 10 features
    pred_wrapper = pred_wrapper(rfmodel[[k]], testsetpvs),               # user-defined prediction function
    train = as.data.frame(trainsetpvs),                                  # training data
    target = trainsetrv,                                                 # response values used for training
    metric = "r2",                                                       # evaluation metric
    task = "regression"
    # progress = "text"                                                  # request a text-based progress bar
    )
}

# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   png(paste0("ch2 data transformations/outputdata/vip/rf/vip_testset_", h, ".png"), width=6.5, height=8, units="in", pointsize=8, res=1200)
#     print(rfvip[[k]], bar=FALSE, shape=19, horizontal=TRUE) + theme_bw()
#   dev.off()
# }
```

```{r vip_averages} 
vimeans <- function(model, ...){
  vils <- list()
  for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
    h <- unique(df_lm_agg$CDEC_ID)[k]
    vils[[k]] <- data.frame(vi(model[[k]], var_fun="con", scale=TRUE, ...))
    vils[[k]][,"TESTSET"] <- h
  }
  vidf <- do.call("rbind", vils)
  vidf_mean <- aggregate(Importance~Variable, data=vidf, FUN=mean)
  vidf_mean <- vidf_mean[order(vidf_mean$Importance, decreasing=TRUE), ]
}

lmvi_mean <- vimeans(linearmodel, method="model")
lmvi_mean$MODELTYPE <- "LM"

glmvi_mean <- vimeans(glinearmodel, method="model")
glmvi_mean$MODELTYPE <- "GLM"

rfvi_mean <- vimeans(rfmodel, method="model")
rfvi_mean$MODELTYPE <- "RF"

# have to treat this specially
vils <- list()
for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
  h <- unique(df_lm_agg$CDEC_ID)[k]
  vils[[k]] <- data.frame(nnvip[[k]]$data)
  vils[[k]][,"TESTSET"] <- h
}
vidf <- do.call("rbind", vils)
nnvi_mean <- aggregate(Importance~Variable, data=vidf, FUN=mean)
nnvi_mean <- nnvi_mean[order(nnvi_mean$Importance, decreasing=TRUE), ]
nnvi_mean$MODELTYPE <- "NN"
nnvi_mean$Importance <- nnvi_mean$Importance*100 # all the others are scaled to 100

vi_means <- rbind(lmvi_mean, glmvi_mean, rfvi_mean, nnvi_mean)
vi_means$Variable <- factor(vi_means$Variable, levels = nnvi_mean$Variable[order(nnvi_mean$Importance, decreasing=FALSE)])
vi_means$MODELTYPE <- factor(vi_means$MODELTYPE, levels=c("LM", "GLM", "RF", "NN"))

MODELTYPE_labels <- c("LM", "GLM", "RF", "NN")
names(MODELTYPE_labels) <- c("LM", "GLM", "RF", "NN")
var_labels <- c("Date","Basin ID", "Basin Name", "River Basin", "County", "Operator", "Station Above #1", "Station Above #2", "Station Above #3", "Station Above #4", "Hierarchy", "Lon", "Lat", "Month", "Ordinal Month", "Season", "Year", "Water Year", "Temperature", "Tmp Lag 1m", "Tmp Lag 2m", "Tmp Lag 3m", "Precipitation", "Ppt Lag 1m", "Ppt Lag 2m", "Ppt Lag 3m", "Snow", "Drainage Area", "Shape", "Compactness", "Mean Elevation", "Relief Ratio", "Sat. Hyd. Conductivity", "% Silt", "% Sand", "% Clay", "Avail. Water Cont.", "Lambda Pore Size", "N Pore Size", "Depth to Restricted Layer", "Percent Vegetated", "Unimpaired Flow" )
names(var_labels) <- c("DATE", "CDEC_ID", "STATION_NAME", "RIVER_BASIN", "COUNTY", "OPERATOR", "STATIONS_ABOVE1",  "STATIONS_ABOVE2", "STATIONS_ABOVE3", "STATIONS_ABOVE4", "HIERARCHY", "LONGITUDE", "LATITUDE", "MONTH", "MONTH_ORDINAL", "SEASON", "YEAR", "WATERYEAR", "TMP", "TMPLAG1", "TMPLAG2", "TMPLAG3", "PPT", "PPTLAG1", "PPTLAG2", "PPTLAG3", "SNOW", "AREASQM", "SHAPE", "COMPACTNESS", "MEANELEV", "BASINRELIEFRATIO","KSAT", "SILT", "SAND", "CLAY", "AWC", "LAMBDA", "N", "RESDT", "VEGETATED", "FLOW")

png("ch2 data transformations/outputdata/rplot213_vip_means.png", width=6.5, height=4, units="in", pointsize=8, res=1200)
  ggplot(data=vi_means, aes(x=Importance, y=Variable, group=MODELTYPE)) +
    geom_point(aes(shape=MODELTYPE, color=MODELTYPE), size=2)+
    scale_color_manual(values=cbpblack[c(2, 3, 5, 6)], labels=MODELTYPE_labels)+
    scale_shape_manual(values=c(3, 17, 0, 16), labels=MODELTYPE_labels)+
    scale_y_discrete(labels=var_labels)+
    labs(x="Importance (scaled)", y="")+
    guides(shape = guide_legend(nrow = 1))+
    theme_bw(base_size = 8)+
    theme(legend.position="right", legend.title = element_blank()) 
dev.off()
```

# 10.0 Partial Dependence Plots
```{r pdp}
library(pdp)
pdp_AREASQM <- pdp_PPT <- list()
nnmodel <- list()
pdp_wrapper <- function(object, newdata) {
  predict(object, x = as.matrix(newdata)) %>%
    as.vector() %>%
    mean()  # aggregate ICE curves
}

pdp_AREASQM_PPT <- pdp_MONTH <- list()
for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
  h <- unique(df_lm_agg$CDEC_ID)[k]
  testset <- df_lm_agg[df_lm_agg$CDEC_ID==h,]
  trainset <- df_lm_agg[df_lm_agg$CDEC_ID!=h,]
  testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
  trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
  testsetrv <- as.matrix(testset$FLOW)
  trainsetrv <- as.matrix(trainset$FLOW)

  modfilename <- paste0("ch2 data transformations/outputdata/vi_saved_mods/nn_hdf5/nn_", h, ".h5")
  nnmodel[[k]] <- load_model_hdf5(modfilename, compile=FALSE)

  # pdp_AREASQM[[k]] <- partial(nnmodel[[k]], pred.var = "AREASQM", pred.fun = pred_wrapper, train = as.data.frame(trainsetpvs))
  # pdp_PPT[[k]] <- partial(nnmodel[[k]], pred.var = "PPT", pred.fun = pred_wrapper, train = as.data.frame(trainsetpvs))
  # pdp_AREASQM_PPT[[k]] <- partial(nnmodel[[k]], pred.var = c("AREASQM", "PPT"), chull = TRUE, pred.fun = pdp_wrapper, train = as.data.frame(trainsetpvs))
  # pdp_MONTH[[k]] <- partial(nnmodel[[k]], pred.var = "MONTH_ORDINAL", chull = TRUE, pred.fun = pdp_wrapper, train = as.data.frame(trainsetpvs))
}
# 
## took too long to run, especially the joint partial dependence so save and read back in
# saveRDS(pdp_AREASQM, "ch2 data transformations/outputdata/pd_saved/nn_pdp_AREASQM.RDS")
# saveRDS(pdp_PPT, "ch2 data transformations/outputdata/pd_saved/nn_pdp_PPT.RDS")
# saveRDS(pdp_AREASQM_PPT, "ch2 data transformations/outputdata/pd_saved/nn_pdp_AREASQM_PPT.RDS")
# saveRDS(pdp_MONTH, "ch2 data transformations/outputdata/pd_saved/nn_pdp_MONTH.RDS")

pdp_AREASQM <- readRDS("ch2 data transformations/outputdata/pd_saved/nn_pdp_AREASQM.RDS")
pdp_PPT <- readRDS("ch2 data transformations/outputdata/pd_saved/nn_pdp_PPT.RDS")
pdp_AREASQM_PPT <- readRDS("ch2 data transformations/outputdata/pd_saved/nn_pdp_AREASQM_PPT.RDS")
pdp_MONTH <- readRDS("ch2 data transformations/outputdata/pd_saved/nn_pdp_MONTH.RDS")

# # randomly sampled because it was taking too long to plot
# for(k in 1:(length(unique(df_lm_agg$CDEC_ID)))){
#   h <- unique(df_lm_agg$CDEC_ID)[k]
#   # p1 <- pdp_AREASQM[[k]][sample(nrow(pdp_AREASQM[[k]]), 50000),]  %>% autoplot(alpha = 0.1) + 
#   #   labs(x="Drainage Area (km^2)", y="Predicted Unimpaired Flow (AF)") +
#   #   theme_bw()
#   # p2 <- pdp_PPT[[k]][sample(nrow(pdp_PPT[[k]]), 50000),] %>% autoplot(alpha = 0.1) + 
#   #   labs(x="Precipitation (mm)", y="Predicted Unimpaired Flow (AF)") +
#   #   theme_bw()
#   # p3 <-  pdp_AREASQM_PPT[[k]] %>% autoplot() + 
#   #   labs(x="Drainage Area (km^2)", y="Precipitation (mm)") +
#   #   guides(fill=guide_legend(title="Predicted \nUnimpaired \nFlow (AF)"))
#   #   theme_bw()
#   p4 <-  ggplot(pdp_MONTH[[k]], aes(x=MONTH_ORDINAL, y=yhat))+
#       geom_point()+
#       labs(x="Ordinal Month (Distance From June)", y="Predicted Unimpaired Flow (AF/m)")+
#       theme_bw()
#   
#   # png(paste0("ch2 data transformations/outputdata/pdp/nn/pdp1_testset_",h, ".png"), width=6.5, height=3, units="in", pointsize=8, res=1200)
#   #   grid.arrange(p1, p2, ncol = 2)+
#   #     theme_bw()
#   # dev.off()
#   # 
#   # png(paste0("ch2 data transformations/outputdata/pdp/nn/pdp2_testset_",h, ".png"), width=6.5, height=3, units="in", pointsize=8, res=1200)
#   #   print(p3)
#   # dev.off()
#   #
#   png(paste0("ch2 data transformations/outputdata/pdp/nn/pdp3_testset_",h, ".png"), width=6.5, height=3, units="in", pointsize=8, res=1200)
#     print(p4)
#   dev.off()
# }

# # to customize 
# print(pdp_AREASQM[[1]][sample(nrow(pdp_AREASQM[[1]]), 5000),] 
#       %>% autoplot(alpha = 0.1)) +
#       labs(x="Drainage Area (SQM)", y="Predicted Unimpaired Flow (AF/m)")+
#       theme_bw()
# 
# print(pdp_PPT[[1]][sample(nrow(pdp_PPT[[1]]), 5000),] 
#       %>% autoplot(alpha = 0.1)) +
#       labs(x="Precipitation (mm)", y="Predicted Unimpaired Flow (AF/m)")+
#       theme_bw()
# 
# print(pdp_MONTH[[1]] 
#       %>% autoplot(alpha = 1)) +
#       labs(x="Ordinal Month (distance from June)", y="Predicted Unimpaired Flow (AF/m)")+
#       theme_bw()
# 
# ggplot(pdp_MONTH[[1]], aes(x=MONTH_ORDINAL, y=yhat))+
#   geom_point()+
#   labs(x="Ordinal Month (Distance From June)", y="Predicted Unimpaired Flow (AF/m)")+
#   theme_bw()

# for all predictor variables but for one basin, let's go with AMF (k=2)
testset <- df_lm_agg[df_lm_agg$CDEC_ID=="AMF",]
trainset <- df_lm_agg[df_lm_agg$CDEC_ID!="AMF",]
testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
testsetrv <- as.matrix(testset$FLOW)
trainsetrv <- as.matrix(trainset$FLOW)

p_vars <- colnames(trainset)[c(15,18:(ncol(trainset)-1))]
var_labels <- c("Date","Basin ID", "Basin Name", "River Basin", "County", "Operator", "Station Above #1", "Station Above #2", "Station Above #3", "Station Above #4", "Hierarchy", "Lon", "Lat", "Month", "Ordinal Month (Distance from June)", "Season", "Year", "Water Year", "Temperature (Deg C)", "Temperature Lag 1m (Deg C)", "Temperature Lag 2m (Deg C)", "Temperature Lag 3m (Deg C)", "Precipitation (mm)", "Precipitation Lag 1m (mm)", "Precipitation Lag 2m (mm)", "Precipitation Lag 3m (mm)", "Snow (mm)", "Drainage Area (SQM)", "Shape (m/m)", "Compactness (m^2/m^2)", "Mean Elevation (m)", "Relief Ratio (m/m)", "Sat. Hyd. Conductivity (cm/hr)", "% Silt (%)", "% Sand (%)", "% Clay (%)", "Available Water Content (m^3/m^3)", "Lambda, Pore Size Distribution Index", "N, Pore Size Distribution", "Depth to Restricted Layer (cm)", "Percent Vegetated (%)", "Unimpaired Flow (AF/m)" )
names(var_labels) <- c("DATE", "CDEC_ID", "STATION_NAME", "RIVER_BASIN", "COUNTY", "OPERATOR", "STATIONS_ABOVE1",  "STATIONS_ABOVE2", "STATIONS_ABOVE3", "STATIONS_ABOVE4", "HIERARCHY", "LONGITUDE", "LATITUDE", "MONTH", "MONTH_ORDINAL", "SEASON", "YEAR", "WATERYEAR", "TMP", "TMPLAG1", "TMPLAG2", "TMPLAG3", "PPT", "PPTLAG1", "PPTLAG2", "PPTLAG3", "SNOW", "AREASQM", "SHAPE", "COMPACTNESS", "MEANELEV", "BASINRELIEFRATIO","KSAT", "SILT", "SAND", "CLAY", "AWC", "LAMBDA", "N", "RESDT", "VEGETATED", "FLOW")

# # for AMF
# ice <- list()
# for (i in 1:length(p_vars)){
#   ice[[i]] <- partial(nnmodel[[2]], pred.var=p_vars[i], pred.fun=pred_wrapper, train=as.data.frame(trainsetpvs), ice=TRUE, nsim=100)
# }
# 
# for (i in 1:length(p_vars)){
#   plottoprint <- autoplot(ice[[i]], alpha = 0.05) + # ice[sample(nrow(ice), 50000), ]
#     labs(x=var_labels[which(names(var_labels)==p_vars[i])], y="Pred. Unimpaired Flow (AF/m)")+
#     theme_bw()
#   png(paste0("ch2 data transformations/outputdata/pdp/nn_AMF/pdp_", p_vars[i], ".png"), width=6.5, height=3, units="in", pointsize=8, res=1200)
#     print(plottoprint)
#   dev.off()
# }

# # for YRS
# ice <- list()
# for (i in 1:length(p_vars)){
#   ice[[i]] <- partial(nnmodel[[67]], pred.var=p_vars[i], pred.fun=pred_wrapper, train=as.data.frame(trainsetpvs), ice=TRUE, nsim=100)
# }
# 
# for (i in 1:length(p_vars)){
#   plottoprint <- autoplot(ice[[i]], alpha = 0.05) + # ice[sample(nrow(ice), 50000), ]
#     labs(x=var_labels[which(names(var_labels)==p_vars[i])], y="Predicted Unimpaired Flow (AF/m)")+
#     theme_bw()
#   png(paste0("ch2 data transformations/outputdata/pdp/nn_YRS/pdp_", p_vars[i], ".png"), width=6.5/2, height=2.25, units="in", pointsize=8, res=1200)
#     print(plottoprint)
#   dev.off()
# }

# plot for paper
# "AREASQM"   12
# "MEANELEV"  15
# "PPT"       7 
# "TMP"       3
# "SNOW"      11
# "SAND"      19

# make a long format data with the variables above
vars_of_interest <- c(12, 15, 7, 3, 11, 19)
for (i in vars_of_interest){
  ice[[i]]$VAR <- colnames(ice[[i]])[1]
  colnames(ice[[i]]) <- c("VALUE", "PRED", "ID", "VAR")
}

ice_YRS <- rbind(ice[[12]], ice[[15]], ice[[7]], ice[[3]], ice[[11]], ice[[19]])
ice_YRS$VAR <- factor(ice_YRS$VAR, levels=c("AREASQM", "PPT", "TMP", "SNOW", "MEANELEV", "SAND"))
pretty_facet_labels <- var_labels[c(28, 31, 23, 19, 27, 35)]

library(ggpmisc)
png('ch2 data transformations/outputdata/rplot214_pdp.png', width=6.5, height=8, units="in", pointsize=8, res=1200)
  plottoprint <- ggplot(ice_YRS, aes(x=VALUE, y=PRED)) +
    geom_line(aes(group=ice_YRS$ID), alpha = 0.05) +
    facet_wrap(~VAR, ncol=2, scales = "free_x", strip.position = "top", labeller=labeller(VAR=pretty_facet_labels))+
    labs(x="", y = "Predicted Unimpaired Flow (AF/m)", color = "")+
    theme(legend.text=element_text(size=10), text=element_text(size=10))+
    stat_summary(fun.y = mean, geom = "line", col=cbpblack[8])+
    theme_bw(base_size = 8)
  print(plottoprint)
dev.off()
```

Find out how different the PDP and the VIP plots are between nn that preforms well and the other models. Leo Brieman, in two cultures, argues that if a model isn't a good predictor, then it may produce erroneous conclusions about the underlying mechanism that produced the data. Let's see how different that really is. maybe compare across the 10 basins that overlap with the BCM so it doesn't become too hard to compare. 

# 11.0 Variable Interactions
```{r interactions}
vint(object = nnmodel[[1]], parallel = TRUE)


```
