---
title: "climatechange"
author: "Ellie White"
date: "March 22, 2019"
output: html_document
---

Record of "future" hydrology as predicted by the NN model and climate model projections. 

# Contents
1.0 Data Gathering  
2.0 Data Transformations  
3.0 Functions  
4.0 Loading the Model and Making Predictions
5.0 Analyze the Model (Weights and Biases) 
6.0 Plots  
  6.1 Time Series  
  6.2 Density  
  6.3 Monthly, Rolling Annual, Rolling 10 Year Runoff/UF  

```{r, include=FALSE}
library(knitr)
library(formatR)
opts_chunk$set(fig.width = 7.5, fig.height = 7.5, collapse = TRUE, tidy = FALSE)
```

# Citations
```{r citations} 
# cite R 
toBibtex(citation())

# cite packages
citethese <- c("zoo", "astsa", "ggplot2", "ggpmisc")
for(i in seq_along(citethese)){
  x <- citation(citethese[i])
  print(toBibtex(x))
}

sessionInfo()
```
 
# 1.0 Data Gathering
```{r data_gathering} 
CanESM2_85_df <- readRDS('inputdata/CanESM2_85_moddf.rds')
CNRMCM5_85_df <- readRDS('inputdata/CNRMCM5_85_moddf.rds')
HadGEM2ES_85_df <- readRDS('inputdata/HadGEM2ES_85_moddf.rds')
MIROC5_85_df <- readRDS('inputdata/MIROC5_85_moddf.rds')

CanESM2_45_df <- readRDS('inputdata/CanESM2_45_moddf.rds')
CNRMCM5_45_df <- readRDS('inputdata/CNRMCM5_45_moddf.rds')
HadGEM2ES_45_df <- readRDS('inputdata/HadGEM2ES_45_moddf.rds')
MIROC5_45_df <- readRDS('inputdata/MIROC5_45_moddf.rds')

preprocess_data <- function(df){
  # remove DOMGEOLOGY cause it's causing problems
  df <- df[ , !(colnames(df) %in% c("DOMGEOLOGY"))]
  
  # order by baisn name
  df <- df[order(df$CDEC_ID), ]
  row.names(df) <- 1:nrow(df)
  
  return(df)
  # # get rid of negative flows, as of now there are no flows in the dataset 
  # moddf <- df[df$FLOW>=0, ]
}

CanESM2_85_moddf <- preprocess_data(CanESM2_85_df)
CNRMCM5_85_moddf <- preprocess_data(CNRMCM5_85_df)
HadGEM2ES_85_moddf <- preprocess_data(HadGEM2ES_85_df)
MIROC5_85_moddf <- preprocess_data(MIROC5_85_df)

CanESM2_45_moddf <- preprocess_data(CanESM2_45_df)
CNRMCM5_45_moddf <- preprocess_data(CNRMCM5_45_df)
HadGEM2ES_45_moddf <- preprocess_data(HadGEM2ES_45_df)
MIROC5_45_moddf <- preprocess_data(MIROC5_45_df)

# # check if all the negatives are gone from moddf, as of now there are no flows
# tbd <- HadGEMES_85_moddf[HadGEMES_85_moddf$FLOW<0, "FLOW"]
# tbd <- na.omit(tbd)
# length(tbd) == 0
# remove(tbd)
```

```{r data_gathering_extra}
# some helpful dataframes, may come in handy later for post processing
basins_points <- read.csv("inputdata/cdec_fnf_stations_data_minus_sfj_otr_bhn_ftm_sfr_sjm_klo.csv", stringsAsFactors = FALSE)
coordinates(basins_points) <- ~LONGITUDE+LATITUDE
proj4string(basins_points) <- CRS("+proj=longlat +datum=WGS84")

basins <- readRDS("inputdata/basins.rds")
cacounties <- readRDS("inputdata/counties.rds")

ta <- CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +datum=NAD83 +units=km +ellps=GRS80")
basins_points <- spTransform(basins_points, ta)
basins <- spTransform(basins, ta)
cacounties <- spTransform(cacounties, ta)
```

```{r visuals} 
# colourblind palettes
# ordered:     black      pink        orange     yellow     green       blue      darkorange  lightblue
cbpgrey <-  c("#999999", "#CC79A7",  "#E69F00", "#F0E442", "#009E73", "#0072B2", "#D55E00", "#56B4E9")
cbpblack <- c("#000000", "#CC79A7",  "#E69F00", "#F0E442", "#009E73", "#0072B2", "#D55E00", "#56B4E9")
```

# 2.0 Data Tranformations
```{r data_transformation}
# split into two one original aggregate basins and one the incremental basins
split_agg <- function(moddf){
  name_inc <- substr(moddf$CDEC_ID, 5,7)
  name_has_inc <- ifelse(name_inc=="",0,1)
  df_inc <- moddf[which(name_has_inc==1),]
  df_agg <- moddf[which(name_has_inc==0),]
  
  # get rid of na values 
  df_agg <- na.omit(df_agg)
  df_inc <- na.omit(df_inc)
  
  # order 
  df_agg <- df_agg[order(df_agg[, "CDEC_ID"], df_agg[, "DATE"]), ]
  
  # just return the agg for now
  return(df_agg)
}

CanESM2_85_moddf <- split_agg(CanESM2_85_moddf)
CNRMCM5_85_moddf <- split_agg(CNRMCM5_85_moddf)
HadGEM2ES_85_moddf <- split_agg(HadGEM2ES_85_moddf)
MIROC5_85_moddf <- split_agg(MIROC5_85_moddf)

CanESM2_45_moddf <- split_agg(CanESM2_45_moddf)
CNRMCM5_45_moddf <- split_agg(CNRMCM5_45_moddf)
HadGEM2ES_45_moddf <- split_agg(HadGEM2ES_45_moddf)
MIROC5_45_moddf <- split_agg(MIROC5_45_moddf)
```

# 3.0 Functions
```{r funcstoimport}
# library(hydroGOF) # this is giving wrong functions, do not load it in make sure the search path is clear
goffuncs <- list.files("libraries/HydroGOFm/R")
for(i in 1:length(goffuncs)){
  source(paste0("libraries/HydroGOFm/R/", goffuncs[i]))
}
remove(goffuncs)

search()
```

# 4.0 Loading the Model Making Predictions
Use NN, AGG, MSE, LOGOCV 
```{r plot_the_problem} 
# load results already in obs pred
resultsls <- readRDS("ch4 resampling/outputdata/rds/nn_agg_logo_results.RDS")

# make a copy of original dataframe
df_agg <- readRDS("Inputdata/moddf.rds")
df_agg <- df_agg[which(ifelse(substr(df_agg$CDEC_ID, 5,7)=="",0,1)==0),]
df_agg <- df_agg[df_agg$FLOW>=0, ]
resultsdf <- df_agg <- na.omit(df_agg)

results_unlisted <- as.data.frame(do.call("rbind", resultsls$results))
resultsdf <- cbind(resultsdf, LOGOFIT=results_unlisted$pred)
resultsdf$LOGORES <- resultsdf$LOGOFIT-resultsdf$FLOW
resultsdf$KF <- as.numeric(resultsdf$CDEC_ID)
colnames(resultsdf)[ncol(resultsdf)] <- "LOGOKF"
resultsdf$HIERARCHY <- factor(resultsdf$HIERARCHY)

# standardize residuals by mean annual flow
resultsdf_meanflow <- aggregate(FLOW~CDEC_ID+WATERYEAR, resultsdf, FUN=mean)
colnames(resultsdf_meanflow)[ncol(resultsdf_meanflow)] <- "MEANFLOW"
resultsdf <- merge(resultsdf, resultsdf_meanflow, by=c("CDEC_ID", "WATERYEAR"))
resultsdf$STANDARDIZED_LOGORES <- resultsdf$LOGORES/resultsdf$MEANFLOW

# studentize residuals by sd annual flow
resultsdf_sdflow <- aggregate(FLOW~CDEC_ID+WATERYEAR, resultsdf, FUN=sd)
colnames(resultsdf_sdflow)[ncol(resultsdf_sdflow)] <- "SDFLOW"
resultsdf <- merge(resultsdf, resultsdf_sdflow, by=c("CDEC_ID", "WATERYEAR"))
resultsdf$STUDENTIZED_LOGORES <- resultsdf$LOGORES/resultsdf$SDFLOW

png('ch5 climate change/outputdata/rplot51_resovertime.png', width=6.5, height=3, units="in", pointsize=8, res=1200)
ggplot(resultsdf_infrm, aes(x=DATE, y=LOGORES, color=HIERARCHY, shape=HIERARCHY))+
  geom_point(alpha=1)+
  scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
  scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
  labs(x="" , y="Residuals in Uniumpaired Flow (AF/m)")+
  geom_abline(slope=0, intercept = c(0,0), col=cbpblack[1], linetype="dashed")+
  scale_y_continuous(labels = scales::comma) +
  theme_bw()
dev.off()

resultsdf_infrm <- resultsdf[!is.infinite(resultsdf$STANDARDIZED_LOGORES), ]
png('ch5 climate change/outputdata/rplot51_resovertime_standardized.png', width=6.5, height=3, units="in", pointsize=8, res=1200)
ggplot(resultsdf_infrm, aes(x=DATE, y=STANDARDIZED_LOGORES, color=HIERARCHY, shape=HIERARCHY))+
  geom_point(alpha=1)+
  scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
  scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
  labs(x="" , y="Standardized Residuals\nin Uniumpaired Flow (-)")+
  geom_abline(slope=0, intercept = c(0,0), col=cbpblack[1], linetype="dashed")+
  scale_y_continuous(labels = scales::comma) +
  theme_bw()
dev.off()

resultsdf_infrm <- resultsdf[!is.infinite(resultsdf$STUDENTIZED_LOGORES), ]
png('ch5 climate change/outputdata/rplot51_resovertime_studentized.png', width=6.5, height=3, units="in", pointsize=8, res=1200)
ggplot(resultsdf_infrm, aes(x=DATE, y=STUDENTIZED_LOGORES, color=HIERARCHY, shape=HIERARCHY))+
  geom_point(alpha=1)+
  scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
  scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
  labs(x="" , y="Studentized Residuals\nin Uniumpaired Flow (-)")+
  geom_abline(slope=0, intercept = c(0,0), col=cbpblack[1], linetype="dashed")+
  scale_y_continuous(labels = scales::comma) +
  theme_bw()
dev.off()

png('ch5 climate change/outputdata/rplot51_resvsflow.png', width=6.5, height=3, units="in", pointsize=8, res=1200)
ggplot(resultsdf, aes(x=FLOW, y=LOGORES, color=HIERARCHY, shape=HIERARCHY))+
  geom_point(alpha=1)+
  scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
  scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
  labs(x="Unimpaired Flow (AF/m)" , y="Residuals in Uniumpaired Flow (AF/m)")+
  geom_abline(slope=0, intercept = c(0,0), col=cbpblack[1], linetype="dashed")+
  scale_y_continuous(labels = scales::comma) +
  theme_bw()
dev.off()

png('ch5 climate change/outputdata/rplot51_resvsflow_standardized.png', width=6.5, height=3, units="in", pointsize=8, res=1200)
ggplot(resultsdf, aes(x=FLOW, y=STANDARDIZED_LOGORES, color=HIERARCHY, shape=HIERARCHY))+
  geom_point(alpha=1)+
  scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
  xlim(c(1, 5e6))+
  scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
  labs(x="Unimpaired Flow (AF/m)" , y="Standardized Residuals\nin Uniumpaired Flow (-)")+
  geom_abline(slope=0, intercept = c(0,0), col=cbpblack[1], linetype="dashed")+
  scale_y_continuous(labels = scales::comma, limits = c(-20, 20)) +
  theme_bw()
dev.off()

# not the problem, let's just make some predictions using the nnmodel with climate changed precip and temp. Will have to have another dataprep

# scientifically check if they are random
library(astsa) 

for(r in 1:length(unique(resultsdf$CDEC_ID))){
  h <- unique(resultsdf$CDEC_ID)[r]
  resultsdf_sub <- resultsdf[resultsdf$CDEC_ID==h,]
  png(paste0('ch5 climate change/outputdata/residual_lagplot/rplot51_reslag_', h, '.png'), width=6.5, height=6.5, units="in", pointsize=8, res=1200)
  lag1.plot(resultsdf_sub$LOGORES, 4)
dev.off()
}

# obtain the correlogram of the in-sample forecast errors for lags 1:max specified. Then plot this correlation to get the ACF plot: the autocovariance or autocorrelation function. PACF is used for the partial autocorrelations. 

for(r in 1:length(unique(resultsdf$CDEC_ID))){
  h <- unique(resultsdf$CDEC_ID)[r]
  resultsdf_sub <- resultsdf[resultsdf$CDEC_ID==h,]
  if(h=="MKW"){
    max_lag <- 5
  } else {
    max_lag <- 24
  }
  # the lines are a lowess fit and the sample acf is blue in the box.
  png(paste0('ch5 climate change/outputdata/residual_acf/rplot51_resacf_', h, '.png'), width=6.5, height=4, units="in", pointsize=8, res=1200)
    acf2(resultsdf_sub$LOGORES, max.lag = max_lag, main=h)
  dev.off()
}

# Box-Pierce test, or Ljung–Box test
bp_test <- lj_test <- c()
for(r in 1:length(unique(resultsdf$CDEC_ID))){
  h <- unique(resultsdf$CDEC_ID)[r]
  resultsdf_sub <- resultsdf[resultsdf$CDEC_ID==h, ]
  bp_test[r] <- Box.test(resultsdf_sub$LOGORES, lag=12, fitdf=0)$p.value
  lj_test[r] <- Box.test(resultsdf_sub$LOGORES, lag=12, fitdf=0, type="Lj")$p.value
}

bplj_testdf <- data.frame(bp_test, lj_test)
bplj_testdf$CDEC_ID <- unique(resultsdf$CDEC_ID)

bplj_testdf <- merge(bplj_testdf, basins@data, by="CDEC_ID")

library(reshape2)
bplj_testdf_long <- melt(bplj_testdf[ , c("CDEC_ID", "bp_test", "lj_test", "HIERARCHY")], id.vars=c("CDEC_ID", "HIERARCHY"), variable.name="BOXTEST", value.name="P_VALUE")
  
plottoprint <- ggplot(data=bplj_testdf_long, aes(x=P_VALUE, y=CDEC_ID)) +
    geom_point(aes(shape=BOXTEST, color=BOXTEST), size=2)+
    facet_grid(HIERARCHY ~ ., scales = "free", space = "free") +
    scale_shape_manual(name="Tests", breaks = c("bp_test", "lj_test"), labels=c("Box–Pierce", "Ljung–Box"), values=c(8, 16)) + 
    scale_colour_manual(name="Tests", aesthetics = c("colour"), values=c(cbpblack[7], cbpblack[8]), breaks = c("bp_test", "lj_test"), labels=c("Box–Pierce", "Ljung–Box")) +
    labs(x="P Value", y="")+
    theme_bw() +
    theme(legend.position="right", legend.title = element_blank())+
    guides(color = guide_legend(nrow = 2), shape= guide_legend(nrow = 2))
 
png('ch5 climate change/outputdata/rplot51_bpljtest.png', width=6.5, height=8, units="in", pointsize=8, res=1200)
  print(plottoprint)
dev.off()
```

```{r nn_mod_predictions_cc}
# load models that were saved in ch2 for vip plotting in case needed
library(keras)
nnmodel <- list()

for(k in 1:(length(unique(CanESM2_85_moddf$CDEC_ID)))){
  h <- unique(CanESM2_85_moddf$CDEC_ID[k])
  modfilename <- paste0("ch2 data transformations/outputdata/vi_saved_mods/nn_hdf5/nn_", h, ".h5")
  nnmodel[[k]] <- load_model_hdf5(modfilename, compile=FALSE)
}

cc_pred <- function(moddf_agg){ 
  results <- modgof <- list()
  for(k in 1:(length(unique(moddf_agg$CDEC_ID)))){
    h <- unique(moddf_agg$CDEC_ID)[k]
    testset <- moddf_agg[moddf_agg$CDEC_ID==h,]
    # trainset <- moddf_agg[moddf_agg$CDEC_ID!=h,] #there's no training happening here
    testsetpvs <- as.matrix(testset[,c(15,18:(ncol(testset)-1))])
    # trainsetpvs <- as.matrix(trainset[,c(15,18:(ncol(trainset)-1))])
    testsetrv <- as.matrix(testset$FLOW)
    # trainsetrv <- as.matrix(trainset$FLOW)
    
    predictions <- nnmodel[[k]] %>% predict(testsetpvs)
    predictions <- predictions[ , 1] # because output layer was specified to be of unit=1
    
    results[[k]] <- cbind(obs=testsetrv[ , 1], pred=predictions, nforstitch=as.numeric(rownames(testset)))
    modgof[[k]] <- gof(as.data.frame(results[[k]])$pred, as.data.frame(results[[k]])$obs)
  }
  list(results=results, gof=modgof)
}

CanESM2_85_resultsls <- cc_pred(CanESM2_85_moddf)
CNRMCM5_85_resultsls <- cc_pred(CNRMCM5_85_moddf)
HadGEM2ES_85_resultsls <- cc_pred(HadGEM2ES_85_moddf)
MIROC5_85_resultsls <- cc_pred(MIROC5_85_moddf)

CanESM2_45_resultsls <- cc_pred(CanESM2_45_moddf)
CNRMCM5_45_resultsls <- cc_pred(CNRMCM5_45_moddf)
HadGEM2ES_45_resultsls <- cc_pred(HadGEM2ES_45_moddf)
MIROC5_45_resultsls <- cc_pred(MIROC5_45_moddf)
```

```{r postprocess} 
# make a copy of the moddfs to store results in 
CanESM2_85_resultsdf <- CanESM2_85_moddf 
CNRMCM5_85_resultsdf <- CNRMCM5_85_moddf
HadGEM2ES_85_resultsdf <- HadGEM2ES_85_moddf  
MIROC5_85_resultsdf <- MIROC5_85_moddf 

CanESM2_45_resultsdf <- CanESM2_45_moddf 
CNRMCM5_45_resultsdf <- CNRMCM5_45_moddf
HadGEM2ES_45_resultsdf <- HadGEM2ES_45_moddf  
MIROC5_45_resultsdf <- MIROC5_45_moddf 

postprocess <- function(resultsdf, resultsls){ 
  results_unlisted <- as.data.frame(do.call("rbind", resultsls$results))
  resultsdf <- cbind(resultsdf, CCFIT=results_unlisted$pred)
  resultsdf$CCRES <- resultsdf$CCFIT-resultsdf$FLOW 
  
  # adding a KF column to make it consistent between groupingstyles
  resultsdf$KF <- as.numeric(resultsdf$CDEC_ID)
  colnames(resultsdf)[ncol(resultsdf)] <- "KF"
  return(resultsdf)
}

CanESM2_85_resultsdf <- postprocess(CanESM2_85_resultsdf, CanESM2_85_resultsls)
CNRMCM5_85_resultsdf <- postprocess(CNRMCM5_85_resultsdf, CNRMCM5_85_resultsls)
HadGEM2ES_85_resultsdf <- postprocess(HadGEM2ES_85_resultsdf, HadGEM2ES_85_resultsls)
MIROC5_85_resultsdf <- postprocess(MIROC5_85_resultsdf, MIROC5_85_resultsls)

CanESM2_45_resultsdf <- postprocess(CanESM2_45_resultsdf, CanESM2_45_resultsls)
CNRMCM5_45_resultsdf <- postprocess(CNRMCM5_45_resultsdf, CNRMCM5_45_resultsls)
HadGEM2ES_45_resultsdf <- postprocess(HadGEM2ES_45_resultsdf, HadGEM2ES_45_resultsls)
MIROC5_45_resultsdf <- postprocess(MIROC5_45_resultsdf, MIROC5_45_resultsls)
```

# 5.0 Analyze the Model (Weights and Biases)
```{r nn_mod_analysis}
nnmodel[[1]] %>% summary()

# # devtools::install_github("andrie/deepviz")
# library(deepviz)
# library(magrittr)
# nnmodel[[1]] %>% plot_model()
```

# 6.0 Plots

## 6.1 Time Series
```{r ts_plots}
CanESM2_85_resultsdf$CCMOD <- "CanESM2"
CNRMCM5_85_resultsdf$CCMOD <- "CNRMCM5"
HadGEM2ES_85_resultsdf$CCMOD <- "HadGEM2ES"
MIROC5_85_resultsdf$CCMOD <- "MIROC5"

CanESM2_45_resultsdf$CCMOD <- "CanESM2"
CNRMCM5_45_resultsdf$CCMOD <- "CNRMCM5"
HadGEM2ES_45_resultsdf$CCMOD <- "HadGEM2ES"
MIROC5_45_resultsdf$CCMOD <- "MIROC5"

CanESM2_85_resultsdf$RCP <- "RCP 8.5"
CNRMCM5_85_resultsdf$RCP <- "RCP 8.5"
HadGEM2ES_85_resultsdf$RCP <- "RCP 8.5"
MIROC5_85_resultsdf$RCP <- "RCP 8.5"

CanESM2_45_resultsdf$RCP <- "RCP 4.5"
CNRMCM5_45_resultsdf$RCP <- "RCP 4.5"
HadGEM2ES_45_resultsdf$RCP <- "RCP 4.5"
MIROC5_45_resultsdf$RCP <- "RCP 4.5"

cc_resultsdf <- rbind(CanESM2_85_resultsdf, CNRMCM5_85_resultsdf, HadGEM2ES_85_resultsdf, MIROC5_85_resultsdf, CanESM2_45_resultsdf, CNRMCM5_45_resultsdf, HadGEM2ES_45_resultsdf, MIROC5_45_resultsdf)

# just comparison of nn model projections with climate changed variables
library(ggplot2)
for (r in 1:(length(unique(cc_resultsdf$CDEC_ID)))){ 
  # plot time series by basin
  h <- unique(cc_resultsdf$CDEC_ID)[r]
  resultsdf_sub <- cc_resultsdf[cc_resultsdf$CDEC_ID==h,]
  
  # convert the units. AREASQKM is in square kilometer, PPT is in mm/month, FLOW is in AF/month 
  watershedArea_sqft <- resultsdf_sub$AREASQKM[1]*(1000*100/2.54/12)^2
  resultsdf_sub$precip_ft <- resultsdf_sub$PPT/10/2.54/12
  resultsdf_sub$precip_cuft <- resultsdf_sub$precip_ft * watershedArea_sqft
  resultsdf_sub$precip_cfs <- resultsdf_sub$precip_cuft/30.5/24/60/60
  resultsdf_sub$discharge_cfs <- resultsdf_sub$FLOW*0.01656433739228
  
  # now convert the units
  resultsdf_sub$discharge_fit_cfs <- resultsdf_sub$CCFIT*0.01656433739228
  
  # remove NAs here?
  resultsdf_sub <- na.omit(resultsdf_sub)
  
  # calculate the range needed to avoid having your hyetograph and hydrograph overlap 
  maxRange <- 1*(max(resultsdf_sub$precip_cfs) + max(max(resultsdf_sub$discharge_cfs), max(resultsdf_sub$discharge_fit_cfs)))

  # create a function to backtransform the axis labels for precipitation, for some reason multiplying it by -1 fixed the labels, kinda hacky but whatever
  precip_labels <- function(x) {round((-1*x / watershedArea_sqft) * 12 *30.5*24*60*60, 0)} # labels in inches/month
  
  # melt for ggplot dataframe
  # results_sub_melted <- melt(resultsdf_sub[, c("DATE", "discharge_cfs", "discharge_fit_cfs" )], id.var='DATE')
  results_sub_melted <- resultsdf_sub
                             
  # make the plot
  hydrograph <- ggplot(data = results_sub_melted, 
                       aes(x = DATE, y=discharge_fit_cfs, col=CCMOD, linetype=RCP)) + 
    xlab("")  + 
    ggtitle(paste0('Basin CDEC ID: ', h)) +
    
    # use geom_tile to create the inverted hyetograph. geom_tile has a bug that displays a warning message for height and width, you can ignore it.
    geom_tile(data=resultsdf_sub, aes(y = -1*(precip_cfs/2-maxRange), # y = the center point of each bar
              height = precip_cfs,
              width = 2),
              fill = cbpblack[6],
              color = cbpblack[6]) +
  
    # plot your discharge data
    geom_line() +
    scale_colour_manual(values = cbpblack[c(2:5)]) +
    scale_linetype_manual(values = c("dotted", "solid")) +
    theme_bw()+
    theme(legend.position="bottom", legend.title = element_blank()) +
 
    # create a second axis with sec_axis() and format the labels to display the original precipitation units
    scale_y_continuous(name = "Discharge (cfs)", sec.axis = sec_axis(trans = ~1*(.-maxRange), name = "Precipitation (in/m)", labels = precip_labels)) # labels are in inches/s
  
  png(paste0('ch5 climate change/outputdata/timeseries_nnmodpred/timeseries_', h, '.png'), width=6.5, height=8, units="in", pointsize=12, res=1200)
    par(mar=c(5,4,1,1)+0.1, ps=8, cex=1)
    print(hydrograph)
  dev.off()
}

library(reshape2)
# compare the fit with the NN model to the projections from the climate models
tsplot_nnmodvccmod <- function(resultsdf, ccmod, scenario){ 
  for (r in 1:(length(unique(resultsdf$CDEC_ID)))){ 
    # plot time series by basin
    h <- unique(resultsdf$CDEC_ID)[r]
    resultsdf_sub <- resultsdf[resultsdf$CDEC_ID==h,]
    
    # convert the units. AREASQKM is in square kilometer, PPT is in mm/month, FLOW is in AF/month 
    watershedArea_sqft <- resultsdf_sub$AREASQKM[1]*(1000*100/2.54/12)^2
    resultsdf_sub$precip_ft <- resultsdf_sub$PPT/10/2.54/12
    resultsdf_sub$precip_cuft <- resultsdf_sub$precip_ft * watershedArea_sqft
    resultsdf_sub$precip_cfs <- resultsdf_sub$precip_cuft/30.5/24/60/60
    resultsdf_sub$discharge_cfs <- resultsdf_sub$FLOW*0.01656433739228
    
    # now convert the units
    resultsdf_sub$discharge_fit_cfs <- resultsdf_sub$CCFIT*0.01656433739228
    
    # remove NAs here?
    resultsdf_sub <- na.omit(resultsdf_sub)
    
    # calculate the range needed to avoid having your hyetograph and hydrograph overlap 
    maxRange <- 1*(max(resultsdf_sub$precip_cfs) + max(max(resultsdf_sub$discharge_cfs), max(resultsdf_sub$discharge_fit_cfs)))
  
    # create a function to backtransform the axis labels for precipitation, for some reason multiplying it by -1 fixed the labels, kinda hacky but whatever
    precip_labels <- function(x) {round((-1*x / watershedArea_sqft) * 12 *30.5*24*60*60, 0)} # labels in inches/month
    
    # melt for ggplot dataframe
    results_sub_melted <- melt(resultsdf_sub[, c("DATE", "discharge_cfs", "discharge_fit_cfs" )], id.var='DATE')

    # make the plot
    hydrograph <- ggplot(data = results_sub_melted, 
                         aes(x = DATE, y=value, col=variable)) + 
      xlab("")  + 
      ggtitle(paste0('Basin CDEC ID: ', h)) +
      
      # use geom_tile to create the inverted hyetograph. geom_tile has a bug that displays a warning message for height and width, you can ignore it.
      geom_tile(data=resultsdf_sub, aes(y = -1*(precip_cfs/2-maxRange), # y = the center point of each bar
                height = precip_cfs,
                width = 2),
                fill = cbpblack[6],
                color = cbpblack[6]) +
    
      # plot your discharge data
      geom_line(aes(linetype=variable)) +
      scale_colour_manual("legend:", values = cbpblack[c(1, 4)], labels=c("Climate Model Projections", "NN Model Predictions")) +
      scale_linetype_manual("legend:", values = c("solid", "dashed"), labels=c("Climate Model Projections", "NN Model Predictions")) +
      theme_bw()+
      theme(legend.position="bottom", legend.title = element_blank()) +
   
      # create a second axis with sec_axis() and format the labels to display the original precipitation units
      scale_y_continuous(name = "Discharge (cfs)", sec.axis = sec_axis(trans = ~1*(.-maxRange), name = "Precipitation (in/m)", labels = precip_labels)) # labels are in inches/s
    
    png(paste0('ch5 climate change/outputdata/timeseries_ccmodpred/', ccmod, '_', scenario, '/timeseries_', h, '.png'), width=6.5, height=8, units="in", pointsize=12, res=1200)
      par(mar=c(5,4,1,1)+0.1, ps=8, cex=1)
      print(hydrograph)
    dev.off()
  }
}

tsplot_nnmodvccmod(CanESM2_85_resultsdf, "CanESM2", "85")
tsplot_nnmodvccmod(CNRMCM5_85_resultsdf, "CNRMCM5", "85")
tsplot_nnmodvccmod(HadGEM2ES_85_resultsdf, "HadGEM2ES", "85")
tsplot_nnmodvccmod(MIROC5_85_resultsdf, "MIROC5", "85")

tsplot_nnmodvccmod(CanESM2_45_resultsdf, "CanESM2", "45")
tsplot_nnmodvccmod(CNRMCM5_45_resultsdf, "CNRMCM5", "45")
tsplot_nnmodvccmod(HadGEM2ES_45_resultsdf, "HadGEM2ES", "45")
tsplot_nnmodvccmod(MIROC5_45_resultsdf, "MIROC5", "45")
```

```{r ccprojvsnnpred_plot} 
library(ggpmisc)
# plot to see agreement
cc_resultsdf$CCMODRCP <- factor(paste0(cc_resultsdf$CCMOD, " ", cc_resultsdf$RCP))

png('ch5 climate change/outputdata/rplot52_obsvspred.png', width=6.5, height=6.5, units="in", pointsize=8, res=1200)
  plottoprint <- ggplot(cc_resultsdf, aes(x=FLOW, y=CCFIT)) +
    geom_point(aes(group=HIERARCHY, colour=HIERARCHY, shape=HIERARCHY)) +
    geom_smooth(method="lm", se=FALSE, color="black")+
    stat_poly_eq(formula = y ~ x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
    geom_abline(slope=1, intercept=0, color="black", linetype=3)+
    facet_wrap(~CCMODRCP, ncol=2) +
    scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
    scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
    labs(x ="Global Climate Model Runoff Projections (AF/m)", y = "NN Model Unimpaired Flow Predictions (AF/m)", color = "")+
    theme(legend.text=element_text(size=10), text=element_text(size=10))+
    theme_bw(base_size = 8)
  print(plottoprint)
dev.off()
```

## 6.2 Density 
```{r density}
png('ch5 climate change/outputdata/rplot53_density.png', width=6.5, height=2.85, units="in", pointsize=8, res=1200)
  plottoprint <- ggplot(cc_resultsdf) +
    geom_density(aes(x=FLOW, group=CCMOD, colour=CCMOD)) +
    scale_color_manual(values=c(cbpblack[8], cbpblack[5], cbpblack[3], cbpblack[2]), name="GCM Projections")+
    geom_density(data=cc_resultsdf, aes(x=CCFIT, fill=CCMOD), alpha=0.2) +
    facet_wrap(~RCP, ncol=2)+
    scale_fill_manual(values=c(cbpblack[8], cbpblack[5], cbpblack[3], cbpblack[2]), name="NN Predictions")+
    guides(fill = guide_legend(override.aes = list(alpha = 0.2)))+
    scale_x_continuous(trans="log10")+
    labs(x ="Runoff or Unimpaired Flow (AF/m)", y = "Density or Frequency of Occurance (%)", color = "")+
    annotation_logticks(sides = "b")+
    theme_bw(base_size = 8) +
    theme(legend.text=element_text(size=10), text=element_text(size=10))
  print(plottoprint)
dev.off()

# check it in seperate plots
plottoprint1 <- ggplot(cc_resultsdf) +
  geom_density(aes(x=FLOW, colour=CCMOD), show.legend = FALSE) +
  scale_colour_manual(values=c(cbpblack[8], cbpblack[5], cbpblack[3], cbpblack[2]))+
  facet_wrap(~RCP, ncol=2)+
  scale_x_continuous(trans="log10")+
  labs(x ="GCM Routed Runoff Projections (AF/m)", y="")+
  annotation_logticks(sides = "b")+
  theme_bw(base_size = 8) +
  theme(legend.text=element_text(size=10), text=element_text(size=10))

plottoprint2 <- ggplot(cc_resultsdf) +
  geom_density(aes(x=CCFIT, colour=CCMOD), show.legend = FALSE) +
  scale_colour_manual(values=c(cbpblack[8], cbpblack[5], cbpblack[3], cbpblack[2]), name="GCM Projections")+
  facet_wrap(~RCP, ncol=2)+
  scale_x_continuous(trans="log10")+
  labs(x ="NN Model Unimpaired Flow Predictions (AF/m)", y="")+
  annotation_logticks(sides = "b")+
  theme_bw(base_size = 8) +
  theme(legend.text=element_text(size=10), text=element_text(size=10))

png('ch5 climate change/outputdata/rplot53_density2.png', width=6.5, height=2.85*2, units="in", pointsize=8, res=1200)
  ggarrange(plottoprint1, plottoprint2, ncol=1)
dev.off()

# boxplot
plottoprint1 <- ggplot(cc_resultsdf) +
  geom_boxplot(aes(x=FLOW, y=CCMOD, colour=CCMOD), show.legend = FALSE) +
  scale_colour_manual(values=c(cbpblack[8], cbpblack[5], cbpblack[3], cbpblack[2]))+
  facet_wrap(~RCP, ncol=2)+
  scale_x_continuous(trans="log10")+
  labs(x ="GCM Routed Runoff Projections (AF/m)", y="")+
  annotation_logticks(sides = "b")+
  theme_bw(base_size = 8) +
  theme(legend.text=element_text(size=10), text=element_text(size=10))

plottoprint2 <- ggplot(cc_resultsdf) +
  geom_boxplot(aes(x=CCFIT, y=CCMOD, colour=CCMOD), show.legend = FALSE) +
  scale_colour_manual(values=c(cbpblack[8], cbpblack[5], cbpblack[3], cbpblack[2]), name="GCM Projections")+
  facet_wrap(~RCP, ncol=2)+
  scale_x_continuous(trans="log10")+
  labs(x ="NN Model Unimpaired Flow Predictions (AF/m)", y="")+
  annotation_logticks(sides = "b")+
  theme_bw(base_size = 8) +
  theme(legend.text=element_text(size=10), text=element_text(size=10))

png('ch5 climate change/outputdata/rplot53_boxplot.png', width=6.5, height=2.85*2, units="in", pointsize=8, res=1200)
  ggarrange(plottoprint1, plottoprint2, ncol=1)
dev.off()
```

## 6.3 Monthly, Rolling Annual, Rolling 10 Year Runoff/UF
```{r rolling_runoff}
head(cc_resultsdf)
cc_resultsdf_rolling1 <- aggregate(FLOW~DATE+HIERARCHY+CCMOD+RCP, data=cc_resultsdf, FUN=mean)
cc_resultsdf_rolling2 <- aggregate(CCFIT~DATE+HIERARCHY+CCMOD+RCP, data=cc_resultsdf, FUN=mean)
cc_resultsdf_rolling <- merge(cc_resultsdf_rolling1, cc_resultsdf_rolling2, by=c("DATE", "HIERARCHY", "CCMOD", "RCP"))
cc_resultsdf_rolling_long <- melt(cc_resultsdf_rolling, id.vars=c("DATE", "HIERARCHY", "CCMOD", "RCP"), variable.name="FLOWTYPE", value.name="FLOW")

# for facet wrapped plotting
cc_resultsdf_rolling$CCMODRCP <- factor(paste0(cc_resultsdf_rolling$CCMOD, " ", cc_resultsdf_rolling$RCP))
cc_resultsdf_rolling_long$CCMODRCP <- factor(paste0(cc_resultsdf_rolling_long$CCMOD, " ", cc_resultsdf_rolling_long$RCP))

#######################################################################################################
# first do monthly averages across CA
plottoprint <- ggplot(cc_resultsdf_rolling_long, aes(x=DATE, y=FLOW, col=FLOWTYPE, linetype=FLOWTYPE))+
  geom_line()+
  xlab("")+
  ylab("Mean California Unimpaired Flow (AF/m)")+
  scale_colour_manual(name= "flowtype", values = cbpblack[c(1,8)], breaks=c("FLOW", "CCFIT"), labels=c("GCM Routed\nRunoff Projections", "NN LOGO MSE\nModel Prediction")) +
  scale_linetype_manual(name= "flowtype", values= c("solid", "dotted"), breaks=c("FLOW", "CCFIT"), labels=c("GCM Routed\nRunoff Projections", "NN LOGO MSE\nModel Prediction"))+
  scale_y_continuous(labels = scales::comma) +
  facet_wrap(~CCMODRCP, ncol=2)+
  theme_bw()+
  theme(legend.position="right", legend.title = element_blank())

png('ch5 climate change/outputdata/rplot58_camean_monthly_comp.png', width=6.5, height=8, units="in", pointsize=8, res=1200)  
  print(plottoprint)
dev.off()

plottoprint <- ggplot(cc_resultsdf_rolling, aes(x=FLOW, y=CCFIT)) +
    geom_point(aes(group=HIERARCHY, colour=HIERARCHY, shape=HIERARCHY)) +
    geom_smooth(method="lm", se=FALSE, color="black")+
    stat_poly_eq(formula = y ~ x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
    geom_abline(slope=1, intercept=0, color="black", linetype=3)+
    scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
    scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
    labs(x ="Mean Global Climate Model Runoff Projections (AF/m)", y = "Mean NN Model Unimpaired Flow Predictions (AF/m)", color = "")+
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(labels = scales::comma) +
    facet_wrap(~CCMODRCP, ncol=2)+
    theme(legend.text=element_text(size=10), text=element_text(size=10))+
    theme_bw(base_size = 8)

png('ch5 climate change/outputdata/rplot58_camean_monthly_comp2.png', width=6.5, height=8, units="in", pointsize=8, res=1200)  
  print(plottoprint)
dev.off() 

#######################################################################################################
# now do annual averages across CA 
library(zoo)
cc_resultsdf_rolling_wide_flow <- dcast(cc_resultsdf_rolling, DATE ~ CCMODRCP + HIERARCHY, value.var="FLOW")
cc_resultsdf_rolling_wide_ccfit <- dcast(cc_resultsdf_rolling, DATE ~ CCMODRCP + HIERARCHY, value.var="CCFIT")

# first, flow
tbd <- data.frame(rollapply(cc_resultsdf_rolling_wide_flow[ , 2:ncol(cc_resultsdf_rolling_wide_flow)], 12, by.column=TRUE, align="left", FUN=mean))
tbd <- cbind(DATE=cc_resultsdf_rolling_wide_flow$DATE[1:(nrow(cc_resultsdf_rolling_wide_flow)-11)], tbd)
tbd <- melt(tbd, id.vars=c("DATE"), variable.name="CCMODRCPH", value.name="FLOW_1YR")
tbd$CCMODRCP <- factor(substring(tbd$CCMODRCPH, 1, (nchar(as.character(tbd$CCMODRCPH))-2)))
tbd$HIERARCHY <- factor(substring(tbd$CCMODRCPH, nchar(as.character(tbd$CCMODRCPH))))
tbd$CCMODRCP <- sub("\\.", " ", sub("\\.", " ", tbd$CCMODRCP))

cc_resultsdf_rolling <- tbd

# now, ccfit
tbd <- data.frame(rollapply(cc_resultsdf_rolling_wide_ccfit[ , 2:ncol(cc_resultsdf_rolling_wide_ccfit)], 12, by.column=TRUE, align="left", FUN=mean))
tbd <- cbind(DATE=cc_resultsdf_rolling_wide_ccfit$DATE[1:(nrow(cc_resultsdf_rolling_wide_ccfit)-11)], tbd)
tbd <- melt(tbd, id.vars=c("DATE"), variable.name="CCMODRCPH", value.name="CCFIT_1YR")
tbd$CCMODRCP <- factor(substring(tbd$CCMODRCPH, 1, (nchar(as.character(tbd$CCMODRCPH))-2)))
tbd$HIERARCHY <- factor(substring(tbd$CCMODRCPH, nchar(as.character(tbd$CCMODRCPH))))
tbd$CCMODRCP <- sub("\\.", " ", sub("\\.", " ", tbd$CCMODRCP))

cc_resultsdf_rolling <- merge(cc_resultsdf_rolling, tbd, by=c("DATE", "CCMODRCP", "HIERARCHY"))
cc_resultsdf_rolling_long <- melt(cc_resultsdf_rolling[, c("DATE", "HIERARCHY", "FLOW_1YR", "CCFIT_1YR", "CCMODRCP")], id.vars=c("DATE", "HIERARCHY", "CCMODRCP"), variable.name="FLOWTYPE", value.name="FLOW")
cc_resultsdf_rolling_long$FLOWTYPE <- factor(cc_resultsdf_rolling_long$FLOWTYPE, levels=c("CCFIT_1YR", "FLOW_1YR"))
plottoprint <- ggplot(cc_resultsdf_rolling_long, aes(x=DATE, y=FLOW, col=FLOWTYPE, linetype=FLOWTYPE))+
  geom_line()+
  xlab("")+
  ylab("Mean California Unimpaired Flow 1 Year Moving Average (AF/m)")+
  scale_colour_manual("flowtype", values = cbpblack[c(1, 8)], breaks=c("FLOW_1YR", "CCFIT_1YR"), labels=c("GCM Routed\nRunoff Projections", "NN LOGO MSE\nModel Prediction")) +
  scale_linetype_manual("flowtype", values= c("solid", "dotted"), breaks=c("FLOW_1YR", "CCFIT_1YR"), labels=c("GCM Routed\nRunoff Projections", "NN LOGO MSE\nModel Prediction"))+
  scale_y_continuous(labels = scales::comma) +
  facet_wrap(~CCMODRCP, ncol=2)+
  theme_bw()+
  theme(legend.position="right", legend.title = element_blank())

png('ch5 climate change/outputdata/rplot58_camean_annualrolling_comp.png', width=6.5, height=8, units="in", pointsize=8, res=1200)  
  print(plottoprint)
dev.off()

plottoprint <- ggplot(cc_resultsdf_rolling, aes(x=FLOW_1YR, y=CCFIT_1YR)) +
    geom_point(aes(group=HIERARCHY, colour=HIERARCHY, shape=HIERARCHY)) +
    geom_smooth(method="lm", se=FALSE, color="black")+
    stat_poly_eq(formula = y ~ x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
    geom_abline(slope=1, intercept=0, color="black", linetype=3)+
    scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
    scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
    labs(x ="Mean Global Climate Model Runoff Projections 1 Year Moving Average (AF/m)", y = "Mean NN Model Unimpaired Flow Predictions 1 Year Moving Average (AF/m)", color = "")+
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(labels = scales::comma) +
    facet_wrap(~CCMODRCP, ncol=2)+
    theme(legend.text=element_text(size=10), text=element_text(size=10))+
    theme_bw(base_size = 8)

png('ch5 climate change/outputdata/rplot58_camean_annualrolling_comp2.png', width=6.5, height=8, units="in", pointsize=8, res=1200)  
  print(plottoprint)
dev.off() 

#######################################################################################################
# now do 10 year rolling averages across CA, only thing changed here is 120 instead of 12 months
# first, flow
tbd <- data.frame(rollapply(cc_resultsdf_rolling_wide_flow[ , 2:ncol(cc_resultsdf_rolling_wide_flow)], 120, by.column=TRUE, align="left", FUN=mean))
tbd <- cbind(DATE=cc_resultsdf_rolling_wide_flow$DATE[1:(nrow(cc_resultsdf_rolling_wide_flow)-119)], tbd)
tbd <- melt(tbd, id.vars=c("DATE"), variable.name="CCMODRCPH", value.name="FLOW_10YR")
tbd$CCMODRCP <- factor(substring(tbd$CCMODRCPH, 1, (nchar(as.character(tbd$CCMODRCPH))-2)))
tbd$HIERARCHY <- factor(substring(tbd$CCMODRCPH, nchar(as.character(tbd$CCMODRCPH))))
tbd$CCMODRCP <- sub("\\.", " ", sub("\\.", " ", tbd$CCMODRCP))

cc_resultsdf_rolling <- tbd

# now, ccfit
tbd <- data.frame(rollapply(cc_resultsdf_rolling_wide_ccfit[ , 2:ncol(cc_resultsdf_rolling_wide_ccfit)], 120, by.column=TRUE, align="left", FUN=mean))
tbd <- cbind(DATE=cc_resultsdf_rolling_wide_ccfit$DATE[1:(nrow(cc_resultsdf_rolling_wide_ccfit)-119)], tbd)
tbd <- melt(tbd, id.vars=c("DATE"), variable.name="CCMODRCPH", value.name="CCFIT_10YR")
tbd$CCMODRCP <- factor(substring(tbd$CCMODRCPH, 1, (nchar(as.character(tbd$CCMODRCPH))-2)))
tbd$HIERARCHY <- factor(substring(tbd$CCMODRCPH, nchar(as.character(tbd$CCMODRCPH))))
tbd$CCMODRCP <- sub("\\.", " ", sub("\\.", " ", tbd$CCMODRCP))

cc_resultsdf_rolling <- merge(cc_resultsdf_rolling, tbd, by=c("DATE", "CCMODRCP", "HIERARCHY"))
cc_resultsdf_rolling_long <- melt(cc_resultsdf_rolling[, c("DATE", "HIERARCHY", "FLOW_10YR", "CCFIT_10YR", "CCMODRCP")], id.vars=c("DATE", "HIERARCHY", "CCMODRCP"), variable.name="FLOWTYPE", value.name="FLOW")
cc_resultsdf_rolling_long$FLOWTYPE <- factor(cc_resultsdf_rolling_long$FLOWTYPE, levels=c("CCFIT_10YR", "FLOW_10YR"))

plottoprint <- ggplot(cc_resultsdf_rolling_long, aes(x=DATE, y=FLOW, col=FLOWTYPE, linetype=FLOWTYPE))+
  geom_line()+
  xlab("")+
  ylab("Mean California Unimpaired Flow 10 Year Moving Average (AF/m)")+
  scale_colour_manual("flowtype", values = cbpblack[c(1, 8)], breaks=c("FLOW_10YR", "CCFIT_10YR"), labels=c("GCM Routed\nRunoff Projections", "NN LOGO MSE\nModel Prediction")) +
  scale_linetype_manual("flowtype", values= c("solid", "dotted"), breaks=c("FLOW_10YR", "CCFIT_10YR"), labels=c("GCM Routed\nRunoff Projections", "NN LOGO MSE\nModel Prediction"))+
  scale_y_continuous(labels = scales::comma) +
  facet_wrap(~CCMODRCP, ncol=2)+
  theme_bw()+
  theme(legend.position="right", legend.title = element_blank())

png('ch5 climate change/outputdata/rplot58_camean_10yr_rolling_comp.png', width=6.5, height=8, units="in", pointsize=8, res=1200)  
  print(plottoprint)
dev.off()

plottoprint <- ggplot(cc_resultsdf_rolling, aes(x=FLOW_10YR, y=CCFIT_10YR)) +
    geom_point(aes(group=HIERARCHY, colour=HIERARCHY, shape=HIERARCHY)) +
    geom_smooth(method="lm", se=FALSE, color="black")+
    stat_poly_eq(formula = y ~ x, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE) +
    geom_abline(slope=1, intercept=0, color="black", linetype=3)+
    scale_color_manual(values=c(cbpblack[2], cbpblack[3], cbpblack[4], cbpblack[5], cbpblack[6]), name="Hierarchy")+
    scale_shape_manual(values=c(1, 16, 2, 0, 15), name="Hierarchy") +
    labs(x ="Mean Global Climate Model Runoff Projections 10 Year Moving Average (AF/m)", y = "Mean NN Model Unimpaired Flow Predictions 10 Year Moving Average (AF/m)", color = "")+
    scale_y_continuous(labels = scales::comma) +
    scale_x_continuous(labels = scales::comma) +
    facet_wrap(~CCMODRCP, ncol=2)+
    theme(legend.text=element_text(size=10), text=element_text(size=10))+
    theme_bw(base_size = 8)

png('ch5 climate change/outputdata/rplot58_camean_10yr_rolling_comp2.png', width=6.5, height=8, units="in", pointsize=8, res=1200)  
  print(plottoprint)
dev.off() 
```



