---
title: "modelling"
author: "Ellie White"
date: "March 22, 2019"
output: html_document
---

Record of builidng different rainfall-runoff models. 

# Contents   
1.0 Data Gathering  
2.0 Modelling 
 
# Libraries  
 

```{r, include=FALSE}
library(knitr)
library(formatR)
opts_chunk$set(
  fig.width  = 7.5,
  fig.height = 7.5,
  collapse   = TRUE,
  tidy       = FALSE
)
```

# Citations
```{r citations}
# cite R 
toBibtex(citation())

# cite packages
citethese <- c("raster", "rgdal", "rgeos", "dismo", "geosphere", "prism", "sharpshootR", "reshape2")
for(i in seq_along(citethese)){
  x <- citation(citethese[i])
  print(toBibtex(x))
}

sessionInfo()
```

# 1.0 Data Gathering
```{r data_gathering}
moddf <- readRDS('inputdata/moddf_inc.rds')

# order by baisn name
moddf <- moddf[order(moddf$CDEC_ID),]
row.names(moddf) <- 1:nrow(moddf)

# split into two one original aggregate basins and one the incremental basins
df_agg <- moddf[1:18504,]
df_inc <- moddf[18505:nrow(moddf),]

# get rid of the negative values
df_agg <- df_agg[df_agg$FLOW>0,]

results_agg <- df_agg
results_inc <- df_inc
```

```{r setseed}
set.seed(3222019)
```

# 2.0 Modelling

## 2.1 Linear Models
```{r lm}
lm_agg <- lm(FLOW~., data=df_agg[,17:ncol(df_agg)])
summary(lm_agg)

lm_inc <- lm(FLOW~., data=df_inc[,17:ncol(df_inc)])
summary(lm_inc)
```

## 2.2 Generalized Linear Models
```{r glm}
glmp_agg <- glm(FLOW~. , family=poisson, data=df_agg[,17:ncol(df_agg)])
summary(glmp_agg)

glmg_inc <- glm(FLOW~. , family=gaussian, data=df_inc[,17:ncol(df_inc)])
summary(glmg_inc)
```

## 2.3 Neural Networks
```{r neuralnets}
# library(nnet)
# nn_agg1 <- nnet(FLOW ~ ., data = df_agg[ ,c(1, 17:41)], size=10)
# 
# # look into these settings             
# #subset = samp, size = 2, rang = 0.1, decay = 5e-4, maxit = 200)
# #table(df_agg$FLOW[-samp], predict(ir.nn2, df_agg[-samp,]))
# 
# library(neuralnet)
# formula_numvars <- as.formula('FLOW ~ PPT + PPTLAG1 + PPTLAG2 + PPTLAG3 + SNOW + AREASQM + SHAPE + COMPACTNESS + MEANELEV + BASINRELIEFRATIO + KSAT + SILT + SAND + CLAY + AWC + LAMBDA + N + RESDT + VEGETATED')
# nn_agg2 <- neuralnet(formula_numvars, data = df_agg[ ,c(1, 17:41)], hidden=10)
#  
# library(RSNNS)
# nn_agg3 <- mlp(df_agg[c(1, 17:40)], df_agg$FLOW, size=10,linOut=TRUE)
# 
# library(caret)
# nn_agg4 <- train(FLOW~.,method='nnet',data=df_agg[ ,c(1, 17:41)],linout=TRUE)
# plot.nnet(nn_ag4, nid=TRUE)
```

Tensorflow is a numerical computing library with an interface in r. It's open-source and  hardware independent, and with it you can do modelling with huge datasets without having to put all of it in RAM.  

Tensors are multi-dimensional arrays: 0D is a scalar (vector or length one), 1D is a vecotr, 2D is a matrix, and 3D and up are arrays. Examples: Dataframe with just observations are 1D or 2D (data.matrix(iris), n=10). Time series data are 3D tensors, because you have a sequence grouping, the samples are the third dimension. Images are 4D tensors, video is 5D. 

Data "flows" through the graph, with nodes representing units of computation. 

The "deep" in deep learning referrs to having large number of layers that transform the inputs into outputs. 

Deep learning has not yet proven that it is good at analyzing data with complex spatial or sequence dependencies that are hard to model traditionally.  

It's good for prediction, not necessarily understanding. 
```{r tensorflow}
# let's build a recurrent neural network(rnn)
# install.packages("tensorflow")
# install.packages("keras", type = "source")

library(keras)
install_keras()

library(tensorflow)
install_tensorflow()

# check to see if all errors are resolved
sess <-  tf$Session()
hello <- tf$constant('Hello, TensorFlow!')
sess$run(hello)

# loading the keras inbuilt mnist dataset
data <- data.matrix(df_inc[,11:ncol(df_inc)])

# split dataset into training, validation, and tesitng
train_data <- data[1:2000,]
mean <- apply(train_data, 2, mean)
std <- apply(train_data, 2, sd)
data <- scale(data, center = mean, scale = std)

train_gen
val_gen
test_gen

# defining a keras sequential model
model <- keras_model_sequential()

# layer_flatten(input_shape = c(lookback / step, dim(data)[-1])) %>% 
#   layer_dense(units = 32, activation = "relu") %>% 
#   layer_dense(units = 1)

# note that models in keras is modified in place, objects are not by-value like it is conventional in r, they are by-reference. 
model %>% 
  layer_dense(units = 784, input_shape = 784) %>% 
  layer_dropout(rate=0.4)%>%
  layer_activation(activation = 'relu') %>% 
  layer_dense(units = 10) %>%  # Note the lack of activation function on the last dense layer, which is typical for a regression problem.

# compiling the defined model
model %>% compile(
  loss = 'mae',
  optimizer = 'optimizer_rmsprop()'
  )

# fitting the model on the training dataset, can use validation_split=0.2 inside fit too. 
history <- model %>% fit(train_data[,1:30], train_data[,31], epochs = 100, batch_size = 128)

plot(history)

# evaluating model on the cross validation dataset
# loss_and_metrics <- model %>% evaluate(test_x, test_y, batch_size = 128)

# layers in keras
# dense layers are fully connected neural networks
# convolutional layers try to find spatial features, mostly used in computer vision, they develop filters that find patterns
# recurrent layers have some memory or state, they can maintain states, used in sequenced applications
# embedding layers, in NLP vecotrizing text that recognizes semantic relationships

# lots of loss functions, can write your own
# lots of optimizers
```

```{r example_tensorflow}
dir.create("~/Downloads/tbd_climate", recursive = TRUE)
download.file(
  "https://s3.amazonaws.com/keras-datasets/jena_climate_2009_2016.csv.zip",
  "~/Downloads/tbd_climate/jena_climate_2009_2016.csv.zip"
)
unzip(
  "~/Downloads/tbd_climate/jena_climate_2009_2016.csv.zip",
  exdir = "~/Downloads/tbd_climate"
)

library(tibble)
library(readr)

data_dir <- "~/Downloads/tbd_climate"
fname <- file.path(data_dir, "jena_climate_2009_2016.csv")
data <- read_csv(fname)

glimpse(data)

library(ggplot2)
ggplot(data, aes(x = 1:nrow(data), y = `T (degC)`)) + geom_line()

ggplot(data[1:1440,], aes(x = 1:1440, y = `T (degC)`)) + geom_line()

lookback = 1440 #Observations will go back 10 days.
steps = 6 #Observations will be sampled at one data point per hour.
delay = 144 #Targets will be 24 hours in the future.

sequence_generator <- function(start) {
  value <- start - 1
  function() {
    value <<- value + 1
    value
  }
}

gen <- sequence_generator(10)
gen()

data <- data.matrix(data[,-1])

train_data <- data[1:200000,]
mean <- apply(train_data, 2, mean)
std <- apply(train_data, 2, sd)
data <- scale(data, center = mean, scale = std)

generator <- function(data, lookback, delay, min_index, max_index,
                      shuffle = FALSE, batch_size = 128, step = 6) {
  if (is.null(max_index))
    max_index <- nrow(data) - delay - 1
  i <- min_index + lookback
  function() {
    if (shuffle) {
      rows <- sample(c((min_index+lookback):max_index), size = batch_size)
    } else {
      if (i + batch_size >= max_index)
        i <<- min_index + lookback
      rows <- c(i:min(i+batch_size-1, max_index))
      i <<- i + length(rows)
    }

    samples <- array(0, dim = c(length(rows),
                                lookback / step,
                                dim(data)[[-1]]))
    targets <- array(0, dim = c(length(rows)))
                      
    for (j in 1:length(rows)) {
      indices <- seq(rows[[j]] - lookback, rows[[j]]-1,
                     length.out = dim(samples)[[2]])
      samples[j,,] <- data[indices,]
      targets[[j]] <- data[rows[[j]] + delay,2]
    }           
    list(samples, targets)
  }
}

lookback <- 1440
step <- 6
delay <- 144
batch_size <- 128

train_gen <- generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 1,
  max_index = 200000,
  shuffle = TRUE,
  step = step, 
  batch_size = batch_size
)

val_gen = generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 200001,
  max_index = 300000,
  step = step,
  batch_size = batch_size
)

test_gen <- generator(
  data,
  lookback = lookback,
  delay = delay,
  min_index = 300001,
  max_index = NULL,
  step = step,
  batch_size = batch_size
)

# How many steps to draw from val_gen in order to see the entire validation set
val_steps <- (300000 - 200001 - lookback) / batch_size

# How many steps to draw from test_gen in order to see the entire test set
test_steps <- (nrow(data) - 300001 - lookback) / batch_size


#Here’s the evaluation loop.

library(keras)
evaluate_naive_method <- function() {
  batch_maes <- c()
  for (step in 1:val_steps) {
    c(samples, targets) %<-% val_gen()
    preds <- samples[,dim(samples)[[2]],2]
    mae <- mean(abs(preds - targets))
    batch_maes <- c(batch_maes, mae)
  }
  print(mean(batch_maes))
}

evaluate_naive_method()
celsius_mae <- 0.29 * std[[2]]


model <- keras_model_sequential() %>% 
  layer_flatten(input_shape = c(lookback / step, dim(data)[-1])) %>% 
  layer_dense(units = 32, activation = "relu") %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit_generator(
  train_gen,
  steps_per_epoch = 500,
  epochs = 20,
  validation_data = val_gen,
  validation_steps = val_steps
)
plot(history)

# A first recurrent baseline
model <- keras_model_sequential() %>% 
  layer_gru(units = 32, input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit_generator(
  train_gen,
  steps_per_epoch = 500,
  epochs = 20,
  validation_data = val_gen,
  validation_steps = val_steps
)

# using recurrent dropout to fight over fitting
model <- keras_model_sequential() %>% 
  layer_gru(units = 32, dropout = 0.2, recurrent_dropout = 0.2,
            input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit_generator(
  train_gen,
  steps_per_epoch = 500,
  epochs = 40,
  validation_data = val_gen,
  validation_steps = val_steps
)

# stcking recurrent layers
model <- keras_model_sequential() %>% 
  layer_gru(units = 32, 
            dropout = 0.1, 
            recurrent_dropout = 0.5,
            return_sequences = TRUE,
            input_shape = list(NULL, dim(data)[[-1]])) %>% 
  layer_gru(units = 64, activation = "relu",
            dropout = 0.1,
            recurrent_dropout = 0.5) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit_generator(
  train_gen,
  steps_per_epoch = 500,
  epochs = 40,
  validation_data = val_gen,
  validation_steps = val_steps
)

# bi directional RNNs
library(keras)

# Number of words to consider as features
max_features <- 10000  

# Cuts off texts after this number of words
maxlen <- 500

imdb <- dataset_imdb(num_words = max_features)
c(c(x_train, y_train), c(x_test, y_test)) %<-% imdb

# Reverses sequences
x_train <- lapply(x_train, rev)
x_test <- lapply(x_test, rev) 

# Pads sequences
x_train <- pad_sequences(x_train, maxlen = maxlen)  <4>
x_test <- pad_sequences(x_test, maxlen = maxlen)

model <- keras_model_sequential() %>% 
  layer_embedding(input_dim = max_features, output_dim = 128) %>% 
  layer_lstm(units = 32) %>% 
  layer_dense(units = 1, activation = "sigmoid")

model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("acc")
)
  
history <- model %>% fit(
  x_train, y_train,
  epochs = 10,
  batch_size = 128,
  validation_split = 0.2
)



model <- keras_model_sequential() %>% 
  bidirectional(
    layer_gru(units = 32), input_shape = list(NULL, dim(data)[[-1]])
  ) %>% 
  layer_dense(units = 1)

model %>% compile(
  optimizer = optimizer_rmsprop(),
  loss = "mae"
)

history <- model %>% fit_generator(
  train_gen,
  steps_per_epoch = 500,
  epochs = 40,
  validation_data = val_gen,
  validation_steps = val_steps
)


```






# 4.0 Predict & Analyze
There are four things we are looking for when analyzing residuals:
* The mean of the errors is zero (and the sum of the errors is zero)
* The distribution of the errors are normal.
* All of the errors are independent.
* Variance of errors is constant (Homoscedastic)
```{r predict_lm_inc}
results_inc$LMFIT <- lm_inc$fitted.values
results_inc$LMRES <- lm_inc$residuals # this is obs-predstr
  
layout(matrix(c(1,1,2,3),2,2,byrow=T))
# response vs. residuals Plot
results_inc_ordered <- results_inc[order(results_inc$FLOW),]
plot(results_inc_ordered$LMRES ~ results_inc_ordered$FLOW, main="Unimpaired Flow vs. Residuals\nfor Multiple Linear Regression", xlab="Unimpaired Flow (AF)", ylab="Residuals")
abline(h=0,lty=2)

# histogram of residuals
hist(results_inc_ordered$LMRES, main="Histogram of Residuals", ylab="Residuals")

# q-q plot
qqnorm(results_inc_ordered$LMRES)
qqline(results_inc_ordered$LMRES)

# residuals are normally distributed? test residuals for normality; null hypothesis: Skewness and Kurtosis are equal to zero
library(fBasics)
jarqueberaTest(lm_inc$resid) 

# residuals are independent? dwtest; test for independence of residuals; null hypothesis: Errors are serially uncorrelated
library(lmtest) 
dwtest(lm_inc) 

layout(matrix(c(1,2,3,4),2,2,byrow=T))
plot(lm_inc$fitted, rstudent(lm_inc), main="Multi Fit Studentized Residuals", xlab="Predictions", ylab="Studentized Resid", ylim=c(-2.5,2.5))
abline(h=0, lty=2)
plot(results_inc$DATE, lm_inc$residuals, main="Residuals by Time", xlab="Time",ylab="Residuals")
abline(h=0,lty=2)
hist(lm_inc$residuals,main="Histogram of Residuals")
qqnorm(lm_inc$residuals)
qqline(lm_inc$residuals)
```

```{r predict_lm_agg}
results_agg$LMFIT <- lm_agg$fitted.values
results_agg$LMRES <- lm_agg$residuals

layout(matrix(c(1,1,2,3),2,2,byrow=T))
# response vs. residuals Plot
results_agg_ordered <- results_agg[order(results_agg$FLOW),]
plot(results_agg_ordered$LMRES ~ results_agg_ordered$FLOW, main="Unimpaired Flow vs. Residuals\nfor Multiple Linear Regression", xlab="Unimpaired Flow (AF)", ylab="Residuals")
abline(h=0,lty=2)

# histogram of residuals
hist(results_agg_ordered$LMRES, main="Histogram of Residuals", ylab="Residuals")

# q-q plot
qqnorm(results_agg_ordered$LMRES)
qqline(results_agg_ordered$LMRES)

# residuals are normally distributed? test residuals for normality; null hypothesis: Skewness and Kurtosis are equal to zero
library(fBasics)
jarqueberaTest(lm_agg$resid) 

# residuals are independent? dwtest; test for independence of residuals; null hypothesis: Errors are serially uncorrelated
library(lmtest) 
dwtest(lm_agg) 

layout(matrix(c(1,2,3,4),2,2,byrow=T))
plot(lm_agg$fitted, rstudent(lm_agg), main="Multi Fit Studentized Residuals", xlab="Predictions", ylab="Studentized Resid", ylim=c(-2.5,2.5))
abline(h=0, lty=2)
plot(results_agg$DATE, lm_agg$residuals, main="Residuals by Time", xlab="Time",ylab="Residuals")
abline(h=0,lty=2)
hist(lm_agg$residuals,main="Histogram of Residuals")
qqnorm(lm_agg$residuals)
qqline(lm_agg$residuals)
```

```{r predict_glm_inc}

```

```{r predict_glm_agg}

```

```{r predict_tf_inc}

```

```{r predict_tf_agg}

```




